

%\newcommand*{\ACM}{}%

\ifdefined\ACM

%\documentclass[sigplan,screen]{acmart}
  \documentclass[manuscript,screen,review]{acmart}

\else
  \documentclass{article}
  \input{./usepackage}
  \addbibresource{./sample.bib} 

\fi

\begin{document}

\input{newcommands}

\title{Why The Following Doesn't Give Log-Local, Constant Gap Hamiltonian?} 
\author{David Ponarovsky}
%\author{Noa Viner, David Ponarovsky}

\ifdefined\ACM
  \affiliation{%
    \institution{The Th{\o}rv{\"a}ld Group}
    \streetaddress{1 Th{\o}rv{\"a}ld Circle}
    \city{Hekla}
  \country{Iceland}}
  \email{larst@affiliation.org}
\else
  \maketitle
\fi
%\input{abstract}
\ifdefined\ACM
  \maketitle
\fi

\newcommand{\Hin}{H_{\text{init}}}
  \newcommand{\Hpr}{H_{\text{prop}}}
\newcommand{\Hen}{H_{\text{end}}}

\newcommand{\CLASS}{\textcolor{blue}{Class}}


\section{New Approach.}

Consider the following promise problem: 

\begin{definition}
  Given a constant $\alpha\in (0,1)$ and $k$-local Hamiltonian $H$ overt $n$ qubits it is promised that either for any quantum states $\braket{\psi|H|\psi} \ge b$ or:\begin{enumerate}
    \item There exists $\ket{\psi}$ such that $\braket{\psi|H|\psi} \le a$
    \item For any $w\subset [n]$, $|w| < \alpha n $ the state $\ket{\phi} = \ket{\psi}|_{w} = Tr_{w}\left( \ket{\psi} \right)$ has energy at most $\braket{\phi|H|\phi|} \le a + \frac{b-a}{2}$
  \end{enumerate}
  Notice that if $b-a \in 1/poly(n)$ then the deciding which of the case holds is a problem in $QMA$. We will call that class: \CLASS 
\end{definition}

\begin{claim}
  
\end{claim}






\section{Several Hamiltonians Constructions.}

\begin{definition} 
Let $C = U_{T}U_{T-1} \dots U_{0}$ be a quantum circuit. Denote by $Z(C)$ the random variable circuit that is obtained by the following random process: $Z(C)$ is the chain of $X_{S}X_{S-1} \dots X_{0}$ such that $X_{0}=U_{0}$, $X_{S}=U_{T}$ and $X_{i}$ is defined recursively. If $X_{i-1} = U_{j}$ for $j>0$, then $X_{i}$ is chosen uniformly from  $\{ U_{j+1}, U_{j}^{\dagger} \}$. We will call any circuit that can be a result of such a process a $C$-Zigzag.
\end{definition}

\begin{definition} 
Let $C = U_{T}U_{T-1}..U_{0}$ be a quantum circuit. We will name any Hamiltonian that can be obtained by the following random process as a $C$-hashed. First, we chain $C$ with itself $\Theta(T)$ times as follows:  
  \begin{equation*}
    \begin{split}
      \rightarrow CC^{\dagger}CC^{\dagger}CC^{\dagger}C .. C^{\dagger}CC^{\dagger}CC^{\dagger}C  
    \end{split}
  \end{equation*}
  Now, any local terms in the propagation Hamiltonian will be at the form of: 
  \begin{equation*}
    \begin{split}
      I - \frac{1}{\Delta}  \left(  U_{i}\ket{t + 1 + 2T\cdot m^{\prime}}\bra{ t + 2T\cdot m} + U^{\dagger}_{i+1}\ket{t + 1 + 2T\cdot m}\bra{ t +1 + 2T\cdot m^{\prime}} \right)
    \end{split}
  \end{equation*}
  where $\Delta$ is the degree of the vertex associated with $\ket{ t + 2T \cdot m }$ in the adjacency graph (where each time coordinate is associated with a vertex and two vertices are connected only if there is a check that verifies their consistency with each other). We choose the local terms such that the adjacency graph has uniform degree and $\Delta$ is a constant number.
\end{definition}

\begin{definition}
  The $C$-hashed-Zigzag Hamiltonian will be the mixed of the two technics above. Given circuit $C$ we first generate a $C$-Zigzag circuit from it, denote it by $C^{\prime}$ with length $T^{\prime}$ and then we applay the hash reduction, but this time we also allow connection at the form:
  \begin{equation*}
    \begin{split}
      U_{i}\ket{t + 1 + 2T^{\prime}\cdot m^{\prime}}\bra{ t^{\prime} + 2T^{\prime}\cdot m}
    \end{split}
  \end{equation*}
  where the $U_{t}..U_{0} = U_{t^\prime}..U_{0}$ in $C^{\prime}$ (basically, in time $t^{\prime}$ we have returned to the state at time $t$). 
\end{definition}

\begin{definition}
  We will say that the following Hamiltonian is a $C$-multilayers if it can be obtained by the follow process. For a given graph $G$, any local term in $\Hpr$ will have the following form:  
  \begin{equation*}
    \begin{split}
      I -  \frac{1}{\Delta} \left( U_{i}\ket{u,t + 1}\bra{v,t} +   U_{i+1}^{\dagger} \ket{v,t}\bra{u,t+1}\right)
    \end{split}
  \end{equation*}
  Where $v,u$ are connected vertices in $G$. In some sanse, any pair of adjoint layers (belongs to consective time step) are form 'expander graph' (Yet, the total expansion of the obtained graph is still low).
\end{definition}

\begin{definition}
  Let $C$ a qaumtum circuit, and let $P : \mathcal{C} \times s  \rightarrow \mathcal{C}$ be a function which given a quantum circuit $C$ and a seed $s$ maps the circuit into another circuits. We will think about $P$ as a mapping ideal circuits to those which might run in the end. We will say that $C_{f}$ is a $P$-fault tolerece verision of $C$ if for any state such that $C\ket{\psi}$ measure $1$ with high probability, it holds that $P(C_{f},s)\ket{\psi}$ measure string $\bar{1}$ (on which we think as logical $1$) with high probability.  
\end{definition}

\begin{claim}
  Let $C_{f} = U_{T}U_{T-1}..U_{0}$ be a $P$-fault tolereance circuit verision of circuit $C$. Than for any $t < T$ it holds that:    
  \begin{equation*}
    \begin{split}
      || P\left(U_{1}^{\dagger} U_{2}^{\dagger}.. U_{t}^{\dagger} ,s \right) P\left(U_{t}.. U_{2} U_{1}, s^{\prime}\right) - I  ||_{op} < 1/poly(T)
    \end{split}
  \end{equation*}
\end{claim}


\section{What we would like to have:}


%
%Consider the LPS expnader on $n$ veritces and denote $ t \sim l $ if $t$ is adjoint to $l$. Let $M_\Delta \in \mathbb{C}^{n \times n}$ be the matrix defined by the product:
%\begin{equation*}
%  \begin{split}
%    \bra{u}M_{\Delta}\ket{l}\bra{l+1}M_{\Delta}\ket{t-1} \bra{t} M_{\Delta}\ket{v} = \mathbf{1}_{ t \sim l } \mathbf{1}_{u = t} \mathbf{1}_{v = l } \ \  
%  \end{split}
%\end{equation*}
% Given the Hamiltonian $\Hin + m \cdot 2I - \Hpr + \Hen$, consider the Hamiltonian $\alpha \Hin + m \cdot 2I - \Hpr M_\Delta \Hpr + \beta \Hen$. Denote $\Hpr$ by $U_{1} \otimes \ket{2}\bra{1}  + U_{2}^{\dagger} \otimes \ket{1}\bra{2} + \cdots $.
% Now Let $\Lambda_{t,l}$ be defined such that:
% 
% \begin{equation*}
%   \begin{split}
%     \Lambda^{\dagger}_{l,t} U_{l}^{\dagger}U_{t} \Lambda_{t,l} = U_{l}U_{l-1}..U_{t+1}U_{t}
%   \end{split}
% \end{equation*}
% And codsider the diagonliztion $W^{\dagger}\Hpr M_{\Delta} \Hpr W$. Where:
%
%\begin{equation*}
%  \begin{split}
%    & W = \sum\Lambda_{t,l}U_{t-1}U_{t-2}..U_{1} \otimes \ket{t}\bra{t} M_{\Delta}\ket{l}\bra{t} \\ 
%    \Rightarrow & W^{\dagger} = \sum U_{1}^{\dagger}U_{2}^{\dagger} .. U_{t-1}^{\dagger} \Lambda_{t,l}^{\dagger} \otimes \ket{t}\bra{t} M_{\Delta}\ket{l}^{*}\bra{t} 
%  \end{split}
%\end{equation*}
%  Noitce that: 
%
%\begin{equation*}
%  \begin{split}
%    & W^{\dagger}U_{l}^{\dagger}U_{t}\ket{l}\bra{l+1}M_{\Delta}\ket{t+1}\bra{t}W = \\
%    & W^{\dagger}U_{l}U_{t}\ket{l+1}\bra{l}M_{\Delta}\ket{t}\bra{t}\ket{t}\bra{t}M_{\Delta}\ket{v}\bra{t}\Lambda_{t,v}U_{t-1}U_{t-2}..U_{1} = \\
%    & U_{1}^{\dagger}U_{2}^{\dagger}.. \Lambda_{l,u}^{\dagger}  U_{l-1}^{\dagger}U_{t}\Lambda_{t,l}U_{t-1}.. U_{1} \ket{l}\bra{l}M_{\Delta}\ket{u}^{*}\bra{l}\ket{l}\bra{l+1} M_{\Delta}\ket{t-1} \bra{t}\ket{t}\bra{t} M_{\Delta}\ket{v} \ket{l}\bra{t} \\
%    & U_{1}^{\dagger} .. U_{l}^{\dagger} \Lambda^{\dagger}_{l,t} U_{l}^{\dagger}U_{t} \Lambda_{t,l} U_{t-1} .. U_{1} \ket{l}\bra{t} = \ket{l}\bra{t} \\ 
%    &\Rightarrow  W^{\dagger}\Hpr W = \sum_{i\sim j}\ket{i}\bra{j}
%  \end{split}
%\end{equation*}
%
%And the history state will look like:
%
%\begin{equation*}
%  \begin{split}
%    \ket{\eta} =  \sum \Lambda_{t,l}U_{t-1}U_{t-2}..U_{1}  \ket{x_{0}} \otimes  \ket{t} 
%  \end{split}
%\end{equation*}

Consider the LPS expander on $n$ vertices and denote $t \sim l$ if $t$ is adjacent to $l$. Let $M_\Delta \in \mathbb{C}^{n \times n}$ be the matrix defined by the product: \ctt{Such $M_{\Delta}$ dosn't exists.} 
\begin{equation*}
  \begin{split}
    &\bra{u}M_{\Delta}\ket{l}^{*}\bra{l+1}M_{\Delta}\ket{t-1} \bra{t} M_{\Delta}\ket{v} = \mathbf{1}_{ t \sim l } \mathbf{1}_{u = t} \mathbf{1}_{v = l } 
  \end{split}
\end{equation*}
Given the Hamiltonian $\Hin + m \cdot 2I - \Hpr + \Hen$, consider the Hamiltonian $\alpha \Hin + m \cdot 22\Delta I - \Hpr M_\Delta \Hpr + \beta \Hen$. Denote $\Hpr$ by $U_{1} \otimes \ket{2}\bra{1}  + U_{2}^{\dagger} \otimes \ket{1}\bra{2} + \cdots $.
Now let $\Lambda_{t,l}$ be defined such that:
 
 \begin{equation*}
   \begin{split}
     \Lambda^{\dagger}_{l,t} U_{l}^{\dagger}U_{t} \Lambda_{t,l} = U_{l}U_{l-1}..U_{t+1}U_{t}
   \end{split}
 \end{equation*}
And consider the diagonalization $W^{\dagger}\Hpr M_{\Delta} \Hpr W$. Where:

\begin{equation*}
  \begin{split}
    & W = \sum\Lambda_{t,l}U_{t-1}U_{t-2}..U_{1} \otimes \ket{t}\bra{t} M_{\Delta}\ket{l}\bra{t} \\ 
    \Rightarrow & W^{\dagger} = \sum U_{1}^{\dagger}U_{2}^{\dagger} .. U_{t-1}^{\dagger} \Lambda_{t,l}^{\dagger} \otimes \ket{t}\bra{t} M_{\Delta}\ket{l}^{*}\bra{t} 
  \end{split}
\end{equation*}
Notice that: 

\begin{equation*}
  \begin{split}
    & W^{\dagger}U_{l}^{\dagger}U_{t}\ket{l}\bra{l+1}M_{\Delta}\ket{t-1}\bra{t}W = \\
    & W^{\dagger}U_{l}U_{t}\ket{l+1}\bra{l}M_{\Delta}\ket{t}\bra{t}\ket{t}\bra{t}M_{\Delta}\ket{v}\bra{t}\Lambda_{t,v}U_{t-1}U_{t-2}..U_{1} = \\
    & U_{1}^{\dagger}U_{2}^{\dagger}.. \Lambda_{l,u}^{\dagger}  U_{l-1}^{\dagger}U_{t}\Lambda_{t,l}U_{t-1}.. U_{1} \ket{l}\bra{l}M_{\Delta}\ket{u}^{*}\bra{l}\ket{l}\bra{l+1} M_{\Delta}\ket{t-1} \bra{t}\ket{t}\bra{t} M_{\Delta}\ket{v} \ket{l}\bra{t} \\
    & U_{1}^{\dagger} .. U_{l}^{\dagger} \Lambda^{\dagger}_{l,t} U_{l}^{\dagger}U_{t} \Lambda_{t,l} U_{t-1} .. U_{1} \ket{l}\bra{t} = \ket{l}\bra{t} \\ 
    &\Rightarrow  W^{\dagger}\Hpr M_{\Delta} \Hpr W = \sum_{i\sim j}\ket{i}\bra{j}
  \end{split}
\end{equation*}
And the history state will look like:

\begin{equation*}
  \begin{split}
    \ket{\eta} =  \sum \Lambda_{t,l}U_{t-1}U_{t-2}..U_{1}   \ket{x_{0}} \otimes  \ket{t} \bra{t} M_{\Delta} \ket{l}
  \end{split}
\end{equation*}


\section{Lets change it a little bit.}
Mabye we should define $\Lambda$ to be depands on a single paramter, namely $\Lambda_{t}$ and: 
\begin{equation*}
   \begin{split}
     \Lambda^{\dagger}_{l} U_{l}^{\dagger}U_{t} \Lambda_{t} = U_{l}U_{l-1}..U_{t+1}
   \end{split}
 \end{equation*}
 That wil allow us to group terms, and if 
\begin{equation*}
  \begin{split}
     \sum_{v,u}\bra{u}D\ket{l}^{*}\bra{l+1}M_{\Delta}\ket{t-1} \bra{t} D\ket{v} = \mathbf{1}_{ t \sim l } % \mathbf{1}_{u = t} \mathbf{1}_{v = l } 
  \end{split}
\end{equation*}
Then we win. So now we ask wheter there exsits such $D,M_{\Delta}$ and $\Lambda_{t}$'s. (Or approximation).   
\begin{claim}
  There are such $\Lambda$'s and they given by: 
  
  \begin{equation*}
    \begin{split}
      \Lambda_{l}^{\dagger} = U_{l}\Lambda_{l-1}^{\dagger}U_{l-1}^{\dagger}U_{l}
    \end{split}
  \end{equation*}
\end{claim}
\begin{proof}
  By induction, assume existness for any  $l,t \le l-1$, namely $\Lambda_{l-1}= U_{l-1}^{\dagger}U_{l-2}\Lambda_{l-2}U^{\dagger}_{l-1}$. Then:  
\begin{equation*}
    \begin{split} 
      \Lambda^{\dagger}_{l} U_{l}^{\dagger}U_{t} \Lambda_{t} = &   \Lambda^{\dagger}_{l} U_{l}^{\dagger}U_{l-1}U_{l-1}^{\dagger}U_{t} \Lambda_{t} \\ 
      & \Lambda^{\dagger}_{l} U_{l}^{\dagger}U_{l-1}\Lambda_{l-1}\Lambda^{\dagger}_{l-1}U_{l-1}^{\dagger}U_{t} \Lambda_{t} = \Lambda^{\dagger}_{l} U_{l}^{\dagger}U_{l-1}\Lambda_{l-1} \cdot \ U_{l-1}..U_{t+1}  = \\ 
      & U_{l}U_{l-1}..U_{t+1} = \\ 
      & \ \Rightarrow   \Lambda_{l}^{\dagger} = U_{l}\Lambda_{l-1}^{\dagger}U_{l-1}^{\dagger}U_{l}
    \end{split}
  \end{equation*}
\end{proof}

What about defining $\tilde{D} = \bra{t} \mathbf{1}_{t\sim l} \ket{l} $, $D = \tilde{D}/det(D)$ and $\bra{l+1} M_{\Delta} \ket{t-1}  =  \mathbf{1}_{t\sim l} 1/\Delta^{2}$ ?  

\section{Ideas.}
\begin{enumerate}
  \item $M_{\Delta}$ has to be unitar (and not just hermitan).  
  \item $\Hin$ and $\Hen$ are the critical terms and deserve more gentle treatment.
\end{enumerate}


\section{Constant Clock.}

We can encode the time by unarity encoding. namely $\ket{t} = \ket{1^{t}000..}$. Then the check $\ket{l}\bra{t}$ replaced by the check $\ket{1_{l}0}\bra{1_{t}0}$.  And we also add checks for the validity of the input $ \ket{*10*1}\bra{*10*1} $ that add a quaderic number of checks.  
% In addition we have to add panility for any non ilegal edge. So, if $t\not{\sim}l$ then we add panility at the form $ J \cdot \ket{1_{l}0}\bra{1_{t}0}$.

\section{Using the classical LTC as hmiltonian} 
The idea of looking for a quantum LTC code through a construction of CSS code just committed to failure as approximating the ground state of local commute Hamiltonian sets on the expanders is in NP. Yet that fact also gives hope that using the classical LTC codes, as non-commute Hamiltonian on expanders, as they are as quantum Hamiltonian might yield a Hamiltonian which approximates it is in $QMA$. Let $H_{X} = J_{0}I - \mathcal{T} ( V^{+}, C_{A}\otimes C_{B}) $$H_{Z} = J_{0}I -   \mathcal{T} ( V^{+}, C_{A}^{\perp}\otimes C_{B}^{\perp}) $. Here the notation $H_{X}$ is used to describe Hamiltona and not a parity check matrix.  Denote $H = H_{X} + H_{Z}$.

\begin{definition}
  Consider the Hamitonain above, over $\frac{1}{4}\Delta^{2}n$ qubits, the decion problem q-c-LTC$[a,b]$ is to answer wheter there exsits state $\ket{\psi}$ such that $\bra{\psi}H\ket{\psi} \le a $ or that for any state the $\bra{\psi}H\ket{\psi} \ge  b $. 
\end{definition}


\begin{claim}
 q-c-LTC$[a,b]$ in QMA. 
\end{claim}
\begin{proof}
  By definition the problem is Local Hamiltonain with polynomail gap.%  We have to show that the gap is $\sim 1/poly$
\end{proof}

\begin{claim} 
 q-c-LTC$[a,b]$ in quantum PCP.  
\end{claim}


   


%\frac{1}{\sqrt{2}}\left( \bra{ \varphi} + \bra{\psi} \right)
\begin{equation*}
  \begin{split}
    \bra{\psi} H_{X} + H_{Z} \ket{\psi} \ge \kappa d\left( \psi, C_{X} \right) + \kappa d\left( \psi, C_{Z} \right)
  \end{split}
\end{equation*}
%\frac{1}{\sqrt{2}}\left( \ket{ \varphi} + \ket{\psi} \right)
\begin{equation*}
  \begin{split}
    & \frac{1}{\sqrt{2}}\left( \bra{ \varphi} + \bra{\psi} \right) H \frac{1}{\sqrt{2}}\left( \ket{ \varphi} + \ket{\psi} \right) \\ 
    & \frac{1}{2} \bra{ \varphi}H_{X} \ket{\varphi} + \frac{1}{2}\bra{\psi}H_{Z} \ket{\psi} -   \frac{1}{2}\bra{\varphi}H_{X}\ket{\psi} - \frac{1}{2}\bra{\varphi}H_{Z}\ket{\psi} + \\
    & +  \frac{1}{2} \bra{ \psi}H_{X} \ket{\psi} + \frac{1}{2}\bra{\varphi}H_{Z} \ket{\varphi} \\
& = a +  \frac{1}{2}\bra{\varphi}H_{X}\ket{\psi} - \frac{1}{2}\bra{\varphi}H_{Z}\ket{\psi} \\
    & +  \frac{1}{2} \bra{ \psi}H_{X} \ket{\psi} + \frac{1}{2}\bra{\varphi}H_{Z} \ket{\varphi} \\
& \ge a +  \frac{1}{2}\bra{\varphi}H_{X}\ket{\psi} - \frac{1}{2}\bra{\varphi}H_{Z}\ket{\psi} \\
& +  \frac{1}{2}\kappa d\left( C_{X}, \psi \right) + \frac{1}{2}\kappa d\left( C_{Z}, \varphi \right) \\
& \ge a +  \frac{1}{2}\bra{\varphi}H_{X}\ket{\psi} - \frac{1}{2}\bra{\varphi}H_{Z}\ket{\psi} \\
& +  \frac{1}{2}\kappa d\left( C_{X}, \psi \right) + \frac{1}{2}\kappa d\left( C_{Z}, \varphi \right) 
  \end{split}
\end{equation*}


\begin{equation*}
  \begin{split}
    \prb{\braket{\psi|H|\psi} \ge b } \le \delta  
  \end{split}
\end{equation*}

Suppose that $\prb{\braket{\psi|H|\psi} \ge b } \le \delta $, So at most $\delta$ of the vertices has energy greater than $b$ and at least $1 - \delta$ ofthe vertices has energy less than $a$. We will say that good vertex is a negative vertex that sibiling only to one positive vertex which doesn't pass the test. We will say that a normal vertex is a  positive non-passing vertex that adjoint only to good vertices. What can we say about the normal vertices?  


\begin{claim}
  Let $x \in \mathbb{F}^{\Delta}_{2}$ and denote by $H_{x}$ the Hamiltonain which on the $i$th coordinate applay $X$ if $x_{i} = 1$ and identty otherwise.And let $c(x) \in [\Delta,\rho\Delta,\delta\Delta]$ be the codeword obtained by encoding $x$. Then $H_{x} \le H_{c(x)}$.  
\end{claim}

\begin{equation*}
  \begin{split}
    & \sum{ H_{x_{i}}} \rightarrow \sum_{|I|=m}{ \prod_{x^{i} \in I } H_{x_{i}}}\rightarrow\sum_{|I|=m}{  H_{ \sum_{x_{i}\in I} x_{i}}} \\
    & \rightarrow \sum_{|I|=m}{  H_{ c\left(\sum_{x_{i}\in I} x_{i}\right)} } \rightarrow \sum_{|I|=m}{  H_{ \sum_{z_{i}} z_{i}}}  
  \end{split}
\end{equation*}


%\begin{multicols*}{2}
% \input{preamble}
% \input{introduction}

\section{Exersices.}
\begin{exercise}[Beasd on Free Games] Consider the following protocol, First we measure $k$ arbitrary qubits in the Fourier base, then we take only the bits measrued zero.. \ctt{somthing here is wrong.} 
\end{exercise}

\begin{definition}
  BellQMA protocol is a QMA varition when the Arthur is restricted to perform only non adaptive and untangled measurments and classical computation. 
\end{definition}
\begin{claim}
  There is a BellQMA protocol which, given a 3-SAT instance with $m$ clauses, uses $\Theta\left( \sqrt{m} \right)$ Merlines, each of them sends $~Q(\log m)$ quabits. The protocol has a completeness $ 1 - exp(-\Omega(\sqrt{m})) $ and soundness $ 1 - \Omega(1)$. 
\end{claim}
Bottom line, They shown that the entangled measurment is not necessary.  

\newpage

\begin{definition}
  Given state $\ket{\psi}$ over $n$ qubits. Let $\ket{\psi^{(i)}}$ be one qubit state defined as $\ket{\psi^{(i)}} = \left( \braket{0|\psi} \right)  \ket{0} + \left( \braket{1|\psi} \right)  \ket{1}$. In addition, define the state $\ket{\psi}^{-i}$ to be the state over $n-1$ qubits, obtained by tracing out the $i$th qubit. We will abuse the notation and denote by $\ket{\psi^{-i}} \otimes \ket{\psi^{(i)}}$ the results by stacking in the qubit of $\ket{\psi^{(i)}}$ in the $i$th position. 
\end{definition}

\begin{claim} \label{claim:noisyproof}
  Denote by $H_{f}$ the $k$-local Hamiltonian obtained by applying Kitaev reduction on a fault tolerant circuit, with gap $b -a \ge 1/poly(n)$. And suppose there is a state $\ket{\psi}$ over $n$ qubits with energy lower than $a$. Then for any $i \in [n]$ it holds that 
  \begin{equation*}
    \begin{split}    
  \braket{\ket{\psi^{-i}} \otimes \ket{\psi^{(i)}}|H_{f}|\ket{\psi^{-i}} \otimes \ket{\psi^{(i)}}} < a
    \end{split}
  \end{equation*}
\end{claim}

\begin{definition} \label{definition:denseHam}
  Given $H_{f}$ Consider the Hamiltonian $H^{\prime}_{f}$ over $2n$ qubits defined by summing local terms $H_{j}$ such that either $H_{j}$ is a local term of $H_{f}$ or that there exist $H_{i}$ in $H_{f}$ such that $H_{i}$ equavilance to $H_{j}$ on $k-1$ nontrival coordinates, and in addition, let $l\in [n]$ be the $k$th nontrivial qubit been act by $H_{i}$ and denote the by $U$ the corresponding opereation applplied by it, namely $H_{i}^{(l)} = U$. Then $H_{j}^{(l + n)} = U$. 
\end{definition}

\begin{claim}
  If $H_{f}$ has $a,b$-gap, So is $H^{\prime}_{f}$. Furthmore $H^{\prime}_{f}$ has the same locality. 
\end{claim}
\begin{definition}
  Let $H$ be a local Hamiltonian and consider the a qunbit $q$. Denote by $H(q)$ the set of the local terms in $H$ act nontrivially on $q$. Now we will define the $q,\zeta$-majority-term relative to $H$, $M[H,q,\zeta]$, to be the $k^{2}$ Hamiltonian defined by: 
  \begin{equation*}
    \braket{\psi|M[H,q,\zeta]|\psi} = \begin{cases}
      \begin{split}
        & 1 & \prbm{ \braket{\psi|H_{i}|\psi} \ge 1 }{H_{i} \sim H(q)} \ge \zeta \\
        & 0 & \prbm{ \braket{\psi|H_{i}|\psi} \ge 1 }{H_{i} \sim H(q)} < \zeta 
    \end{split}
  \end{cases}
  \end{equation*}
\end{definition}

\begin{claim}
  There is a $f(k)$-time algorithm that compute $M[H,q,\zeta]$ where $f(k)$ is a function of $k$, namely doesn't depeand on $n$. 
\end{claim}

\begin{definition} \label{definition}  
  Let $H$ be a $k$-local, Denote by $M[H, \zeta]$ the $\zeta$-majority Hamiltonian relative to $H$ to be: 
  \begin{equation*}
    \begin{split}
      M[H,\zeta] = \frac{1}{n}\sum_{q\in[n]}{ M[H,q,\zeta]} 
    \end{split}
  \end{equation*}
\end{definition}

\begin{claim}
  There exist $\zeta$ such that $M[H,\zeta]$ is $k^{2}$ local Hamiltonian with $1\frac{1}{2}$ gap.   
\end{claim}

\begin{proof}
  Suppose that $H$ has a state $\ket{\psi}$ with energy below $a$. Then:  
  \begin{equation*}
    \begin{split}
      \braket{\psi|M[H,q,\zeta]|\psi} & =  \exppm{ \braket{\psi|M[H,q,\zeta]|\psi} }{\sim q} \\ 
      & \\
      & =\exppm{\prbm{ \braket{\psi|H_{i}|\psi} \ge 1 }{H_{i}\sim H(q)} \ge \zeta }{\sim q} \\
      & \\ 
      & \le  \frac{ \exppm{ \exppm{ \braket{\psi|H_{i}|\psi} | q }{ H_{i} \sim H(q)} }{ \sim q }  }{\zeta } \\
      & \\ 
      & \le  \frac{ \exppm{ \braket{\psi|H_{i}|\psi} }{ H_{i} \sim H }  }{\zeta } \le \frac{a}{\zeta}
    \end{split}
  \end{equation*}
  Frathmore consider the case in which for every state it holds that $\braket{\psi|H|\psi}\ge b$, and denote by $\alpha$ the portion of the qubits which see lass than $\zeta k$ energy around them, then: 

  \begin{equation*}
    \begin{split}
    \braket{\psi|H|\psi}  & =  \frac{1}{m}\sum_{H_{i} \in H} {\braket{\psi|H_{i}|\psi} }  \\
    & = \frac{1}{m\cdot k}\sum_{q \in [n]}\sum_{H_{i} \in H(q)} {\braket{\psi|H_{i}|\psi} }  \\
    & = \frac{1}{n \cdot k_{2}}\sum_{q \in [n]}\sum_{H_{i} \in H(q)} {\braket{\psi|H_{i}|\psi} }  \\
    & \le \frac{1}{n \cdot k_{2}} n \cdot k_{2}\left( \alpha \zeta + (1-\alpha) \right) \\
    & \Rightarrow \alpha  \le \frac{1  - b} { 1 -\zeta}
    \end{split}
  \end{equation*}

 \begin{equation*}
    \begin{split}
      \braket{\psi|M[H,q,\zeta]|\psi} & =  \exppm{ \braket{\psi|M[H,q,\zeta]|\psi} }{\sim q} \\ 
      & y
     \end{split}
  \end{equation*}
 

\end{proof}

\printbibliography


\end{document}





