\section{Draft.} 

\subsection{Claim 13.}

\begin{claim}
  \label{claim:Tdeg} $d_{T} = ? $ \ctt{complete that lemma}. 
\end{claim}

\begin{proof}
Denote By $S_{e}$ the exceptional vertices in $\Gamma^{+}_{\square}$ which their degree restricted to $x$ is more than $\Delta^{1 \frac{1}{2} + \varepsilon}$ and we will say that any vertex which is not exceptional is normal.  

Let $T \subset V^{-}$ be the negative vertices which are connected to at least one normal vertex through an heavy edge i.e an edge which adjoins to at least $\delta\Delta - \Delta^{\frac{1}{2}}$ squares. 


\begin{equation*}
  \begin{split}
    & |S_{e}|\Delta^{1 \frac{1}{2}+ \varepsilon} \le \Delta^{2}|S_{e}|\frac{|S|}{n} +  \lambda \sqrt{|S||S_{e}|} \\ 
    & \left(  \Delta^{1 \frac{1}{2}+ \varepsilon} - \Delta^{2} \frac{|S|}{n}\right)|S_{e}| \le  \lambda \sqrt{|S||S_{e}|}\\
    & |S_{e}| \le \frac{\lambda^{2}}{\left(  \Delta^{1 \frac{1}{2}+ \varepsilon} - \Delta^{2} \frac{|S|}{n} \right)^{2}} |S| \le \frac{3}{4} |S|
  \end{split}
\end{equation*}


\begin{equation*}
  \begin{split}
    & \delta\Delta|T|\left( 1 - \frac{1}{\sqrt{\Delta}} \right) \le \Delta |T| \frac{|S|}{n} + \lambda_{\cup} \sqrt{|S||T|}\\ 
    & |T| \le \frac{\lambda_{\cup}^{2}}{ \left( \delta \Delta \left( 1 - \frac{1}{\sqrt{\Delta}} \right) -  \Delta \frac{|S|}{n} \right)^{2} } |S| \le \frac{1}{\Delta}|S|
  \end{split}
\end{equation*}


\begin{equation*}
  \begin{split}
    d_{T} = \frac{E(S_{n}, T)}{|T|} \ge \frac{|S_{n|}}{|T|} \ge   \left( 1 -  \frac{1}{\Delta} \right) \delta\Delta
  \end{split}
\end{equation*}

\end{proof}

\begin{equation*}
  \begin{split}
    (1- \frac{1}{2}\delta)\Delta^{2} \le \frac{3}{4}\left( 1 - \frac{1}{\sqrt{\Delta}}  \right)\Delta^{2} 
  \end{split}
\end{equation*}

Suppose that we have vertex $v_{-}$ which any of his positive neighbors contribute a row (col) with of poly-code with a small amount of noise (lets say below $\sqrt{\Delta}$). What could we say about the existence of polynomial that close to that manifold. We could think about that a linear number of rows has at most $\frac{1}{3}$ of zeros.  $ f\left( x,y \right)= \prod{ \left( x - a_{i} \right) \left(  y - b_{j} \right) } $


\ctt{ Seems like if $d_{T} \ge \theta \Delta^{2}$ then there is a little number of cols which are zero. Therefore we can think about some $f\left( x,y  \right) = \prod{ \left( y - a_{i} \right)   } g(x,y) $ such the degree of the first product is not so heigh and in addition if we write $f= l\left( x,y \right)g\left( x,y \right)$ then $l$ grantee that $f$ will agree on most to the zeros.  Now as the distance of the polynomial is relative large, we have that any term in $g$ after fixing $y$ is a low degree polynomial at $x$. Hence, it looks like ewe can only improve by adding the suit polynomial.}

\ctt{Notice that the product of two polynomial codes can be though as the polynomial in $2D$ in which the degree of each term is less than $2d$.} 

\begin{claim}
  \label{claim:poldu}
  Let $C_{0}$ be the $[\Delta,d, \Delta-d]$ polynomial code. Then any code word in $\left( C_{0}^{\perp} \otimes C_{0}^{\perp} \right)^{\perp}$ is a polynomial in $F[x,y]$ at degree at most $\Delta + d$
\end{claim}
\begin{proof}
Consider base element $ C_{0} \otimes \mathbb{F} $, denote it by $c = g_{i} \otimes e_{j}$. And notice that $c$ has representation in $F[x,y]$ of $\prod_{y^{\prime} \neq j}{\left( y - y^{\prime} \right) }g_{i}\left( x \right)$. By the fact that $g_{i}\left( x \right) \in C_{0} $ we have that degree of $c$ is at most $\Delta + \delta$. Hence any element in the subspace of $C_{0} \otimes \mathbb{F}$ is a polynomial at degree at most $\Delta + d$.   
\end{proof}
\begin{claim}
  \label{claim:lim}
  Any codeword in $\left( C_{0}^{\perp} \otimes C_{0}^{\perp} \right)^{\perp}$ at weight at most $\Delta^{1 \frac{1}{2}}$ is supported on at most $\Delta^{\frac{1}{2}} $ rows and columns.
\end{claim}
\begin{proof}
  Let $c$ be a codeword of the dual tensor and let $R (C)$ be the number of elements base at form $g_{i}\otimes e_{j} (e_{i} \otimes g_{j})$ on which $c$ has nonzero weight. Denote by $\delta_{0}$ the distance of the $C_{0}$. Now, denote by $\gamma$ the fraction number of interfere points between summed up vectors, and observe that by ~\cref{claim:poldu}, each of those point is a zero of polynomial at degree at most $\Delta + d$ over a subset $S \subset \mathbb{F}^{\Delta\times \Delta} $ at size $RC$.     

  Hence by Schwartz-Zippel lemma \cite{Schwartz} we have that $\gamma RC \le \left( d + \Delta \right)$. On the other hand, the number of weight of $c$ is at least: 
\begin{equation*}
    \begin{split}
      |c| \ge \left( R + C  \right) \delta_{0}\Delta - 2RC \cdot \gamma  \ge \left( R + C \right)\delta_{0}\Delta -2 \left( d + \Delta  \right)
    \end{split}
  \end{equation*}
  Combine the fact that $|c| \le \Delta^{1 \frac{1}{2}}$ we obtain that: 
  \begin{equation*}
    \begin{split}
      R + C \le 2\frac{d + \Delta}{\delta_{0} \Delta} + \frac{\Delta^{\frac{1}{2}}}{\delta_{0}}
    \end{split}
  \end{equation*}
\end{proof}
  
\begin{claim}
  Let $v_{-} \in T$ be a vertex adjoins to more than $\left( 1 - \frac{1}{\Delta} \right)\delta\Delta$ normal vertices via heavy edges. Then there exists $c \in C_{0} \otimes C_{0}$ supported on the local view of $v_{-}$ such that $|x + c| < |x|$. 
\end{claim}

\begin{proof}
  Noitce that any prumutation on the coordinate yield an euavlance code. Therefore if      

\begin{tikzpicture}
  [every node/.style={draw=black}]
  \matrix [nodes={minimum size=5mm}]
  {
    \node {1}; & \node{1}; & \node {1}; \node {1}; & \node{1}; & \node {1};\node {1}; & \node{1}; & \node {1}; \node {1}; & \node{1}; & \node {0};\\
    \node {1}; & \node{1}; & \node {1}; \node {1}; & \node{1}; & \node {1};\node {1}; & \node{1}; & \node {1}; \node {1}; & \node{1}; & \node {0};\\
    \node {1}; & \node{1}; & \node {1}; \node {1}; & \node{1}; & \node {1};\node {1}; & \node{1}; & \node {1}; \node {1}; & \node{1}; & \node {0};\\
    \node {1}; & \node{1}; & \node {1}; \node {1}; & \node{1}; & \node {1};\node {1}; & \node{1}; & \node {1}; \node {1}; & \node{1}; & \node {0};\\
    \node {0}; & \node{0}; & \node {0}; \node {0}; & \node{0}; & \node {0};\node {0}; & \node{0}; & \node {0}; \node {0}; & \node{0}; & \node {0};\\
    \node {0}; & \node{0}; & \node {0}; \node {0}; & \node{0}; & \node {0};\node {0}; & \node{0}; & \node {0}; \node {0}; & \node{0}; & \node {0};\\
  };
\end{tikzpicture}

  %By \cref{claim:Tdeg} there exists at least one vertex $v_{-}$ 

\end{proof}

\subsection{Simplified Claim 13.} 
\newcommand{\Gtt}{\tilde{G}}
% \text{ if the row (col) } [uv] \text{ weight is } \Teta\left( \Delta \right) 
Denote by $\Gtt$ the graph obtained by $\Gtt  = \left\{ \left\{ u^{-}, v^{+} \right\}  \right\} $. By the assumption that $x$ is not a reducible we have that there exists $\gamma$ ( $ 1- \frac{1}{2}\delta$  )  such that the degree of any negative vertex in $\Gtt$ is less than $\gamma\Delta$. Denote by $S$ and $T$ the subsets of positive and the negative vertices on the support of $x$. By counting arguments we obtain that: 
\begin{equation*}
  \begin{split}
    |S| 2\Delta \ge E|_{\Gtt} \ge  |T| \Rightarrow \frac{|S|}{|T|} \ge \frac{\Delta}{2}
  \end{split}
\end{equation*}
We could also think on $S$ the normal vertices defined at \cite{leverrier2022quantum} (as been with positive degree in $\Gtt$ equivalence for been connected with heavy edge. On the other hand that quotient is also lower bound for the average degree of the negative vertices, Since $E_{\Gtt}(S,T)/|T| \ge |S|/|T| \ge \gamma/2$. For any random variable $X$ such that $X \le \Delta$ we have that: 

  \begin{equation*}
    \begin{split}
      & \prb{X\le x}x+\prb{X > x}\Delta\ge \expp{X}\Rightarrow \\ 
      & \prb{X \ge \frac{1}{2} \expp{X} } \ge \frac{\expp{X}}{2\Delta}
    \end{split}
  \end{equation*}

