

%\newcommand*{\ACM}{}%

\ifdefined\ACM

%\documentclass[sigplan,screen]{acmart}
\documentclass[manuscript,screen,review]{acmart}

\else
\documentclass{article}
\include{usepackage}
\addbibresource{sample.bib} %Import the bibliography file

\fi
\begin{document}

\newcommand{\commentt}[1]{\textcolor{blue}{ \textbf{[COMMENT]} #1}}
\newcommand{\ctt}[1]{\commentt{#1}}
\newcommand{\prb}[1]{ \mathbf{Pr} \left[ {#1} \right]}
\newcommand{\onotation}[1]{\(\mathcal{O} \left( {#1}  \right) \)}
\newcommand{\ona}[1]{\onotation{#1}}
%\newcommand{\PSI}{{\ket{\psi}}}
%\newcommand{\LESn}{\ket{\psi_n}}
%\newcommand{\LESa}{\ket{\phi_n}}
%\newcommand{\LESs}{\frac{1}{\sqrt{n}}\sum_{i}{\ket{\left(0^{i}10^{n-i}\right)^{n}}}}
%\newcommand{\Hn}{\mathcal{H}_{n}}
%\newcommand{\Ep}{\frac{1}{\sqrt{2^n}}\sum^{2^n}_{x}{ \ket{xx}}}
%\newcommand{\HON}{\ket{\psi_{\text{honest}}}}
%\newcommand{\Lemma}{\paragraph{Lemma.}}
\newcommand{\Cpa}{[n, \rho n, \delta n]}
%\setlength{\columnsep}{0.6cm}
\newcommand{\Jvv}{ \bar{J_{v}} } 
\newcommand{\Cvv}{ \tilde{C_{v}} } 

\newcommand{\Gz}{ G_{z}^{\delta} } 
\newcommand{ \Tann } {  \mathcal{T}\left( G, C_0 \right) }


\title{Removing The $w$-Robustness Assumptions.} 
\author{David Ponarovsky}

\ifdefined\ACM
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}
\else
\maketitle
\fi

\abstract{We propose an alternative simple construction of good LTC codes. } 

\ifdefined\ACM
\maketitle
\fi
%\begin{multicols*}{2}

  \section{Preambles}
  In this work, we propose a new construction for good LDPC codes, which also have a good testability parameter. In the sense that verfining a constant number of random checks, would be enough to detect any error with probability proportional to the error size. In contrast to previews, constructions made by \cite{Dinur}, \cite{leverrier2022quantum} and \cite{Pavel}, our construction doesn't require spicel properties of the small codes, such as $w$-robustness and $p$-resistance for puncturing. 
  
  Our proof also indirectly answers the following question. Why most of the good LDPC codes are known to be bad in terms of detecting errors? In other words, It seems that for most of them, there exist strings that are very far from being in the code and, meanwhile, fail to satisfy only a small number of restrictions.
  While the previous LDPC constructions focused on ensuring that the yielded code would have a good rate and distance parameters, our construction enforces the restrictions collection to have a nontrivial fraction of degeneration. That is, removing a single restriction will not change the code, as any restriction is linearly dependent on the others.

  \include{backgroud.tex}

 \subsection{Tanner testability.} This subsection will explain why testability is so hard to achieve. Let $C$ be a good Tanner expander code as defined above. And consider an arbitrary vertex $u \in V$ and arbitrary restriction of $C_{0}$, $h$. Now define $\tilde{C}$ as the code obtained by requiring all the restrictions of $C$ except $h$ on $u$. That it, $u$ is satisfied if his local view satisfies all the $C_{0}$ restrictions apart from $h$.
  Also, for convenience, denote the small code $u$ enforces on his local view by $C_{0}^{u}$. Let us assume that the distance of $C_{0}^{u}$ is at least $\delta\Delta$. 
  Then, by repeating almost exactly the steps above with caution, one could prove that $\tilde{C}$ also has a linear distance. 


  Assume that $\tilde{C} \neq C \Rightarrow$ there exists $x\in \tilde{C} / C$. By definition, for any $v\in V / \{u\}$ it holdes that $x|_{v} \in C_{0}$. Hence, the assumption that $ x \notin C$  implies $x|_{u} \notin C_{0}$ So, clearly, $x$ fails at a constant number of $C$'s checks. On the other hand, the closest codeword $y \in C$ to $x$ is also a codeword of $\tilde{C}$ as $y|_{v} \in C_{0}$ for every $v\in V$.  Hence:
  \begin{equation*}
    \begin{split}
      d\left( x,C \right) &= d\left( x,y \right) \ge d\left( \tilde{C} \right) =\Theta\left( n \right)
    \end{split}
  \end{equation*}
  Even if a linear number of bits needed to be flipped to correct $x$, only a single check observes that $x$ is indeed an error.
  \section{Construction}
  \subsection{ Almost LTC With Zero Rate}
  \paragraph{Definition. The Disagreement Code.} Given a Tanner code $C = \Tann$, define the code $C_{\oplus}$ to contain all the words equal to the formal summation $ \sum_{v \in V\left( G \right)} {c_{v} }$ when $c_{v}$ is an assignment of a codeword $ c_{v} \in C_0 $  on the edges of the vertex $ v \in V\left( G \right)$.
  We call to such code the \textit{disagreement code} of $C$, as edges are set to 1 only if their connected vertices contribute to the summation codewords that are different on the corresponding bit to that edge. In addition, we will call to any contribute $c_v$, the \textit{suggestion} of $v$. And notice that by linearity, each vertex suggests, at most, a single suggestion.   


  Finally, given a bits assessment $x \in \mathbb{F}_{2}^{E}$ over the edges of $G$, we will denote by $x^{\oplus} \in C_{\oplus} $ the codeword which obtained by summing up suggestions set such each vertex suggests the closet codeword to his local view. Namely, for each $v \in V$ define:   
  \begin{equation*}
    \begin{split}
      c_{v} & \leftarrow \arg_{ \tilde{c} \in C_{0}} \min{ d( x|_{v} , \tilde{c} ) } \ \ \forall v\in V   \\
      x^{\oplus} & \leftarrow \sum_{v \in V}{c_{v}} 
    \end{split}
  \end{equation*}
  We will think about $x^{\oplus}$ as the disagreement between the vertices over $x$. 


  \paragraph{Lemma. Linearity Of The Disagreement.} Consider the code $C = \Tann$. Let $ x \in \mathbb{F}_{2}^{E}$ then for any $ y \in C$ it holds that: 
  \begin{equation*}
    \begin{split}
      \left( x + y  \right)^{\oplus} = \left( x  \right)^{\oplus} 
    \end{split}
  \end{equation*}
  \paragraph{Proof.} Having that $y \in C$ followes $y|_v \in C_{0}$ and therefore $\arg_{ \tilde{c} \in C_{0}} \min{ d( z  , \tilde{c} ) } = y|_{v} + \arg_{ \tilde{c} \in C_{0}} \min{ d( z, \tilde{c} + y|_{v} ) } $, Hence the suggestion made by vertrx $v$ is: 
  \begin{equation*}
    \begin{split}
      c_{v}\leftarrow &  \arg_{ \tilde{c} \in C_{0}} \min{ d( (x+y)|_{v}  , \tilde{c} ) } \\
      \leftarrow &  y|_{v} +  \arg_{ \tilde{c} \in C_{0}} \min{ d( (x+y)|_{v}  , \tilde{c} + y|_{v} ) } \\
      \leftarrow &  y|_{v} +  \arg_{ \tilde{c} \in C_{0}} \min{ d( x|_{v} , \tilde{c} ) } 
    \end{split}
  \end{equation*}
  It follows that: 

  \begin{equation*}
    \begin{split}
      \left( x + y \right)^{\oplus} =& \sum_{v\in V}{c_{v}} = \sum_{v \in V}{y|_{v}} + \sum_{v\in V}{ \arg_{ \tilde{c} \in C_{0}} \min{ d( x|_{v} , \tilde{c} ) } } \\ 
      =& y^{\oplus} + x^{\oplus} = x^{\oplus}
    \end{split}
  \end{equation*}
  When the last transition follows immediately by the fact that $y \in C$ and therefore any pair of connected vertices contribute the same value for their associated edge $\square$

  \paragraph{Definition.} Let $C = \Tann$. We say that $x \in C_{\oplus}$ is \textit{reducable} if there exists a vertex $v$ and a small codeword $c_v$, for which, adding the assignment of $c_v$ over the $v$'s edges to $x$ decreases the weight. Namely, $|x + c_{v}| < |x|$. If $x \in C_{\oplus}$ is not a reducable codeword then we say that $x$ is \textit{ireducable}.   

  \paragraph{Theorem 1.} There exist a constant $\alpha > 0$ and an infinte family of Tanner Codes $C = \Tann$ such that any ireducable codeword $x$ of a coresponding disagreement code $x \in C_{\oplus}$ at length $n$, weight at least $\alpha n$.
  \paragraph{Proof.} By induction over the number of vertices $V^\prime \subset V$, which suggest a nontrivial codeword to $x$. Base, assume that a single vertex $v \in V$ suggests a nontrivial codeword $c_{v} \in C_{0}$. Then it's clear that $x = c_{v}$. And therefore, we have that $|x +c_{v}| = 0 < |x|$.

  Assume the correctness of the argument for every codeword defined by at most $m$ nontrivial suggestions made by $V^\prime \subset V$. And consider the graph $\left( V^\prime, E^\prime \right)$ induced by them. If the graph has more than a single connectivity component, then any of them is also a codeword of $C_{\oplus}$  but composed of at most $m-1$ nontrivial suggestions. Therefore, by the assumption, we could find a vertex $v$ and a proper small codeword $c_v \in C_0 $, such that the addition of the suggestion will decrease the weight of the codeword defined on that component and therefore decrease the total weight of $x$.

  So, we can assume that the vertices in $V^\prime$ compose a single connectivity component. Let be $x|_{v} \in \mathbb{F}_{2}^{\Delta}$ the bits of $x$ on the indices corresponding to $v$'s edges. If there is any $v$, with suggestion $c_{v}$, such that $ \frac{1}{2}w\left( c_{v}\right) < w\left( x|_{v} \right)$, then we could pick to turn on $c_{v}$ again and have that:
  \begin{equation*}
    \begin{split}
      |x+c_{v}| & = | x_{/v} + x_{v} + c_{v}| = |x_{/v}| + w\left( c_{v} \right) + w\left( x|_{v} \right) \\
      & < |x_{/v}| + \frac{1}{2}w\left( c_{v} \right) \le |x_{/v}| + w\left( x|_{v} \right) = |x|
    \end{split}
  \end{equation*}

  Hence it is left to consider the case that for any $v\in V^\prime$, it holds that $\frac{1}{2}w\left( c_{v}\right) >  w\left( x|_{v} \right)$ (Notice that if they equal, then by turn on $c_{v}$, we back again to codeword made by $m-1$ nontrivial suggestions). We will prove that this case is possible only for codewords with wight at least $\alpha|E|^{1-\varepsilon}$.

  For any $S \subset E$, define $w_{S}\left( x \right)$ as the weight that $x$ induces over $S$. And notice that any edge of $E$ connected only to a single vertex in $V^\prime$ equals the corresponding bit in the original suggestion made by $c_{v}$. Hence for every $v\in V^\prime$, it holds that $w_{E / E^\prime}\left(x|_{v}\right) = w_{E / E^\prime}\left(c_{v}\right)$. 

%\input{network2.tex}
  \paragraph{Claim.} For any $v \in V^\prime$ and corresponded suggestion $c_{v}$ it holds that: $w_{E^\prime}\left( c_{v} \right) \ge \frac{1}{2}\delta_{0}\Delta$. 
  \paragraph{Proof:}By using the previews insight we get: \begin{equation*}
    \begin{split}
      w_{E^\prime}\left( c_{v} \right) &= w\left( c_{v} \right) - w_{E / E^\prime}\left( c_{v} \right) =  w\left( c_{v} \right) - w_{E / E^\prime}\left( x|_{v} \right) \\ 
      & \ge  w\left( c_{v} \right) - w\left( x|_{v} \right) \ge \frac{1}{2}w\left( c_{v} \right) = \frac{1}{2}\delta_{0}\Delta 
    \end{split}
  \end{equation*}
  $\square$

  Consider an arbitrary vertex $r \in V^\prime$, and consider the DAG obtained by the BFS walk over the subgraph $\left(V^\prime, E^\prime \right)$ starting at $r$. Denote this directed tree by $T$.

%Let $g$ be the girth of the graph and consider a layer $U$ in $T$ at height $h\left( U \right)$ satisfies the inequality $ h\left( U \right) < \frac{1}{2}g + l$ for some integer $l$.
  %\begin{adjustbox}{width=150pt}%\columnwidth}
%\begin{figure*}[t]%{width=150pt} %0.3\textwidth}

%\end{figure*}
%\end{adjustbox} 
  \paragraph{Claim.} The size of $T$ is at least:
  \begin{equation*}
    \begin{split}
      |T| & \ge \left( \frac{1}{4}\delta_{0} - \frac{\lambda}{\Delta} \right)n 
    \end{split}
  \end{equation*}
  \paragraph{Proof:} By the fact that for any $v \in T$ the degree of $v$ is at least $\frac{1}{2}\delta_{0}\Delta$ we have that: $E\left( T,T \right) \ge \frac{1}{2}\cdot \frac{1}{2}\delta_{0}\Delta |T|$. Combine the Mixining Expander Lemma we obtain:
  \begin{equation*}
    \begin{split}
      \frac{1}{4}\delta_{0}\Delta |T| & \le \frac{\Delta}{n}|T|^2  + \lambda|T| \\ 
      \Rightarrow & \left( \frac{\Delta}{n}|T| + \lambda -  \frac{1}{4}\delta_{0}\Delta \right)|T| \ge 0 \\ 
      \Rightarrow & |T| \ge \left( \frac{1}{4}\delta_{0} - \frac{\lambda}{\Delta} \right)n 
    \end{split}
  \end{equation*}
  $\square$
 %
 %  \paragraph{Claim.} There is a constant $\gamma > 0 $ such for any  $S \subset T$ it holds that:  
 %  \begin{equation*}
 %    \begin{split}
 %      \frac{\lambda}{\Delta} \le \gamma\left( 1 - \frac{1}{2}\delta_{0} \right)\frac{|S|}{|T|}
 %    \end{split}
 %  \end{equation*}
 %
 %  \paragraph{Proof.} Recall that the second largest eigenvalue 
 %
 %  Denote by $x|_{U}$ the bits of $x\in C$ correspond to the edges connected to at least one vertex in $U$. And denote by $w_{E/E^{\prime}}\left( x|_{U} \right)$ the weight induced by the $x|_{U}$ over the edges in $E/E^\prime$.

  \paragraph{Claim.} Suppose that $G$ is an expander graph with a second eigenvalue $\lambda$, then For any layer $U$ there exist a layer $U^{\prime}$ such that:
  \begin{equation*}
    \begin{split}
      (1) & \ \ |U^{\prime}| \ge |U| \\
      (2) & \ \ w_{E/E^{\prime}}\left( x|_{U^{\prime}} \right)  \ge\Delta|U^{\prime}|\left( \delta_{0}-\frac{2}{3}-\frac{2\lambda}{\Delta} \right)
    \end{split}
  \end{equation*}
  \paragraph{Proof:} Consider layer $U$ and denote by $U_{-1}$ and $U_{+1}$ the preceding and the following layers to $U$ in $T$. It follows from the expander mixing lemma that:
  \begin{equation*}
    \begin{split}
      w_{E/E^{\prime}}\left( x|_{U} \right) & \ge \delta_{0}\Delta|U| -w\left( E(U_{-1} \bigcup U_{+1} ,U)  \right) \ge \\ 
      & \delta_{0}\Delta|U| -\left( E(U_{-1} \bigcup U_{+1} ,U)  \right) \\ 
      &  \delta_{0}\Delta|U| - \Delta\frac{|U||U_{-1}|}{n} - \Delta\frac{|U||U_{+1}|}{n} \\
      & -\lambda\sqrt{|U||U_{-1}|} - \lambda\sqrt{|U||U_{+1}|}
    \end{split}
  \end{equation*}

  \paragraph{Claim.} We can assume that $|U| \ge |U_{-1}|, |U_{+1}|$. 
  \paragraph{Proof:} Suppose that $|U_{+1}| > |U|$, so we could choose $U$ to be $U_{+1}$. Continuing stepping deeper till we have that $|U| > |U_{+1}|, |U_{-1}|$. Simiraly, if $|U| > |U_{+1}|$ but $|U_{-1}| > |U|$, the we could take steps upward by replacing $U_{-1}$ with $U$. At the end of the process, we will be left with $U$ at a size greater than the initial layer and $|U| > |U_{+1}|, |U_{-1}|$ $\square$

  Using the the claim, we have that $\left( |U_{+1}| + |U_{-1}| \right)/n <\frac{2}{3} $ and therefore:
  \begin{equation*}
    \begin{split}
      w_{E/E^{\prime}}\left( x|_{U} \right) & \ge \left( \delta_{0} - \frac{2}{3} - \frac{2\lambda}{\Delta} \right) \Delta |U| \ \  \square 
    \end{split}
  \end{equation*}

  That immediately yields the following: let $U_{\text{max}} = \text{arg} \max_{U \text{ layer in }  T } |U|  $  then: 
  \begin{equation*}
    \begin{split}
      |x| \ge  w_{E/E^{\prime}}\left( x|_{U_{\text{max}}} \right) \ge \left( \delta_{0} - \frac{2}{3} - \frac{2\lambda}{\Delta} \right)\Delta |U_{\text{max}}|
    \end{split}
  \end{equation*}
  \paragraph{Claim.} Consider again the maximal layer $U_{\max}$ then: 
  \begin{equation*}
    \begin{split}
      w_{E/E^{\prime}}\left( x \right) \ge \left( \delta_{0} - \frac{|U_{\max}|}{n} - \frac{\lambda}{\Delta} \right) \Delta|T| 
    \end{split}
  \end{equation*}
  \paragraph{Proof.} Similarly to above, now we will bound the weight that all the nodes in $T$ induce over $E/E^{\prime}$. Denote by $U_{0}, U_{1} .. U_{m}$ the layers of $T$ ordered corresponded to their height, thus we obtain: 
  \begin{equation*}
    \begin{split}
      w_{E/E^{\prime}}\left( x \right) & \ge \delta_{0}\Delta|T| - \sum_{i\in [m]}{ w \left( E\left( U_{i}, U_{i+1}  \right) \right)  } \\ 
      \ge & \delta_{0}\Delta|T|  - \sum_{i \in [m]}{ E\left( U_{i}, U_{i+1}  \right)  } \\ 
      \ge & \delta_{0}\Delta|T|  -  \sum_{i \in [m]}{ \frac{\Delta}{n}|U_{i}| |U_{i+1}| + \lambda \sqrt{ |U_{i}| |U_{i+1}|} }\\ 
      \ge & \delta_{0}\Delta|T|  -  \sum_{i \in [m]}{ \frac{\Delta}{n}|U_{i}| |U_{i+1}| + \lambda \frac{ |U_{i}|+ |U_{i+1}|}{2 } }\\ 
      \ge & \delta_{0}\Delta|T|  - \frac{\Delta}{n}|T||U_{\max}| -  \lambda |T| \\ 
      \ge & \left( \delta_{0} - \frac{|U_{\max}| }{n}-  \frac{\lambda}{\Delta} \right) \Delta|T| 
    \end{split}
  \end{equation*}
  $\square$
  \paragraph{Proof of Theorem 1.} Consider the size of the maxiaml layer $|U_{\max}$ and sepearte to the following two cases. First, consider the case that $|U_{\max}| \ge  \alpha n $ in that case it follows immedily that if $\delta_{0} > \frac{2}{3} - \frac{2\lambda}{\Delta}$ there exists $\alpha^{\prime} > 0 $ such that:  
  \begin{equation*}
    \begin{split}
      |x| \ge \left( \delta_{0} - \frac{2}{3} - \frac{2}{\lambda}\Delta \right)\Delta|U_{\max}| \ge  \alpha^{\prime} n 
    \end{split}
  \end{equation*}
  So, it is lefts to consider the second case in which $ |U_{\max}| < \alpha n $ in that case, we have from the second inequality that: 

  \begin{equation*}
    \begin{split}
      |x| & \ge  w_{E/E^{\prime}}\left( x \right)  \ge \left( \delta_{0} - \frac{|U_{\max}|}{n} - \frac{\lambda}{\Delta} \right) \Delta|T| \\ 
      & \ge \left( \delta_{0} - \alpha - \frac{\lambda}{\Delta} \right) \Delta|T| 
    \end{split}
  \end{equation*}
  Setting $\alpha \ge \frac{2}{3}$ we complete the proof $\square$

  Unfortunately, Singelton bound doesn't allow both $\delta_0 > \frac{2}{3}$ and $\rho_0 \ge \frac{1}{2}$, so in total, we prove the existence of code LDPC code which is good in terms of testability and distance yet has a zero rate. In the following subsection, we will prove (\ctt{sec 3.4, which currently is a failure}) that one can overcome this problem by requiring only half of the vertices to restrict their local view to be codewords of high relative distance. 
%\subsection{ Good LTC Which Is Almost LDPC. } 
%To overcome the vanishing rate issue, we are going to consider the graphs family in which the maximal layer of BFS scanning couldn't exceed a linear  

 %
 %  \begin{equation*}
 %    \begin{split}
 %      \left( 1 - \frac{1}{2}\delta_{0} \right)\Delta |T| \ge \left( \delta_{0} - \frac{|U_{\max}|}{n} - \frac{\lambda}{\Delta} \right) \Delta|T| 
 %    \end{split}
 %  \end{equation*}

  \subsection { Overcoming The Vanishing Rate. } 
  Consider the following code; instead of associating each edge with pair of checks, let's define the vertices to be the checks of small codes over $q \in [0,1]$ fraction of their edges. That is, now each vertex defines only $\left( 1 - \rho_{0} \right)q\Delta$ restrictions. Hence, the rate of the code is at least:   
  \begin{equation*}
    \begin{split}
      \rho\frac{1}{2}\Delta n & \ge \frac{1}{2}\Delta n - \left(1 - \rho_{0} \right)q\Delta n \\
      \Rightarrow \rho & \ge \left(  2\rho_{0} + \left( \frac{1}{q}  - 2  \right)  \right)q \\ 
      \rho_{0} & \ge  1 - \frac{1}{2q} 
    \end{split}
  \end{equation*} for example, if $q = 2/3$, then for having constant rate, it is enough to ensure that $ \rho_{0} \ge 1 - \frac{3}{4} = \frac{1}{4}$.

 \paragraph{Intuition For Testability.} Before expand the construction let's us justifiy why one should even expects that removing constrainsts preserves testability. Assume that is gurnted that the lower bound of the flux on the trivial vertices remains up to multiplication by the fraction factor $q$, or put it diffrently, one could just stick $q$ in every inequalitiy without lose correcntess, Then: 
  \begin{equation*}
    \begin{split}
      w_{E/E^{\prime}}\left( x|_{U} \right) & \ge  \delta_{0}q\Delta|U| -qw\left( E(U_{-1} \bigcup U_{+1} ,U)  \right) \\ 
      \Rightarrow |x| & \ge \left(  \delta_{0} - \frac{2}{3} - \frac{2\lambda}{\Delta} \right) q \Delta|U_{\max}|
    \end{split}
  \end{equation*}
  As you can see, ireducable words of the disagreement have a linear weight, dispite that the orignal code has non-vanish rate.     
  
  \paragraph{Theorem 1+.} There exist a constant $\alpha > 0 $ and infinite familiy of codes which satesfies Theroem 1 and also good.
  \paragraph{}

  Yet, We still require more to prove a linear distance. 
   By repeating on the \emph{Singleton Bound} proof it follows that the small code $\tilde{C_{0}}$ obtained by ignoring arbitrary $ \left( q - \frac{1}{2} \right) \Delta $ coordinates yield a code with distance: 
  \begin{equation*}
    \begin{split}
      \left( \delta_{0} - \left( q - \frac{1}{2} \right) \right)\Delta
    \end{split}
  \end{equation*}
  So assume that we could engineer an expander family such that the graphs obtained by removing $\frac{1}{2}$ of the edges connected for each vertex result also expanders, and in addition, regarding $\tilde{C_{0}}$ each edge is checked by both vertices on its support. Namely, a good Tanners Code could be defined on the restricted graphs; Then, any string that satisfies the original checks also has a linear weight. To achieve this property, we will restrict ourselves to a particular family of Cayley Graphs.  
  \paragraph{Definion. Testability-Tanner-Code.} Let $q > \frac{1}{2}$ and let $J$ be a geneator set for group $\Gamma$ such that $|J| = \Delta$, $q | \Delta $, $J$ closed for inverse, and there exist subset of $J$, denote it by, $J^{\prime}$ such that $J^{\prime}$ is a generator set of $\Gamma$ and $|J^{\prime}| = \frac{1}{2}\Delta$. Let $C_{0}$ be a code with parameters $C_{0} = q\Delta \left[1, \rho_{0}, \delta_{0}\right]$. For any vertex assoicate a subset $\Jvv \subset J/J^{\prime}$ at size: 

  \begin{equation*}
    \begin{split}
      |\Jvv| = \left( q - \frac{1}{2} \right)\Delta \Rightarrow |\Jvv \cup J^{\prime}| = q\Delta
    \end{split}
  \end{equation*}
  Define the code $\mathcal{T}\left(J, q , C_{0}\right)$ to be the subspace such that any vertex's local view over the edges defined by $\Jvv \cup J^{\prime}$ is a codeword of $C_{0}$. In addition, let's associate a code $\Cvv$ obtained for any vertex by ignoring the bits supported on the $\Jvv$ coordinates. Notice that code defined by requiring that the local view of any vertex $v$ of \emph{Cayley}$\left(\Gamma, J^{\prime} \right)$ is a codeword of $\Cvv$ is a TannerCode. Denote it by $ \tilde{\mathcal{T}}\left(J, q ,C_{0}\right)$.   

  \paragraph{Lemma.} Let $J$ be defined as above such that both \emph{Cayley}$\left( \Gamma, J \right)$, \emph{Cayley}$\left( \Gamma, J^{\prime} \right)$ are expanders with algebric expansion greater then $\lambda$ and $C_0$ with the parameters $\rho_{0} > 1 - \frac{1}{2q}$ and $ \delta_{0} - \left( q - \frac{1}{2} \right) > \lambda$. Then the code $\mathcal{T}\left(J, q ,C_{0}\right)$ is a good code. 
  \paragraph{Proof.} We have already proven that the code has a positive rate. Consider a codeword $x$ and denote by $x^{\prime}$ the restriction of $x$ to \emph{Cayley }$\left( \Gamma, J^{\prime}  \right)$ which is a codeword of $\tilde{C} = \tilde{\mathcal{T}}\left(J, q ,C_{0}\right)$. But $\tilde{C}$ is a Tanner Code such that any vertex sees at least $ \tilde{\delta_{0}} \Delta := \left(\delta_{0} - \left( q - \frac{1}{2}   \right) \right)\Delta $ nontrivial bits, Therefore as the expansion of the graph \emph{Cayley}$\left( \Gamma, J^{\prime} \right)$ is lower than $\tilde{\delta}\Delta$ than any subset $S$ of $V$ at the size at most $|S|/|V| < \tilde{\delta_{0}} - \lambda / \Delta $  must contain at least one vertex that sees less than  $\tilde{\delta}\Delta$ nontrivial bits, In contradiction for the fact that $x^{\prime} \in \tilde{C}$. $\square$ 

  \paragraph{Claim. Existence of such \emph{Cayley's}.} Let $S$ be a generator set such that \emph{Cayley}$\left( \Gamma , S \right)$ has a second largest eigenvalue greater then $\lambda$, And consider an arbitray group element $g \in \Gamma$ such that $gSg^{-1}$ disjointness to $S$ \ctt{ remove the disjointness requirment}. Denote by $S_{g}$ the set $gSg^{-1}$. Then the second eigenvalue of the graph obtained by $\left( \Gamma, S \right) \cup \left( \Gamma, S \right)$ is at most $2\lambda$. 
  \paragraph{Proof.} Denote by $G,G^{\prime}$ the \emph{Cayley} graphs coressponding to $S$, $S_{g}$, for conviniet we will use the notation of $\sum_{v\sim_{G} u}$ to denote a summation over all the neighboors of $v$ in the graph $G$. Let $A_{G^{\prime}}$ be the adjacency matrix of $G^{\prime}$. Recall that $G^{\prime}$ is a  $\Delta$ regular graph, and therefore the uniform distribution $\mathbf{1}$ is the eigenstate with the maximal eigenvalue, and the second eigenvalue is given by the min-max principle: 
  \begin{equation*}
    \begin{split}
      & \max_{f \perp \mathbf{1}} { \frac{f^{\top}A_{G^{\prime}} f  }{ f^{\top}f}} = \max_{f \perp \mathbf{1}} { \sum_{v}  \sum_{u\sim_{G^{\prime}} v}\frac{f\left( u \right) f \left( v \right)  }{ f^{\top}f}} \\
      =  & \max_{f \perp \mathbf{1}} { \sum_{v}\sum_{\tau \in S} \frac{f\left( g\tau g^{-1} v \right) f \left( v \right)  }{ f^{\top}f}} \\ = & \max_{f \perp \mathbf{1}} { \sum_{gv} \sum_{\tau \in S}\frac{f\left( g\tau g^{-1} gv \right) f \left( gv \right)  }{ f^{\top}f}} \\  
      = & \max_{f \perp \mathbf{1}} { \sum_{gv}\sum_{\tau \in S}\frac{f\left( g \tau v \right) f \left( g v \right)  }{ f^{\top}f}} \\  = & \max_{f \perp \mathbf{1}} { \sum_{gv}\sum_{ u\sim_{G} v }\frac{f\left( gu \right) f \left( gv \right)  }{ f^{\top}f}} \\
         \end{split}
  \end{equation*}
  As for any function $f : V \rightarrow \mathbb{R} $ one could define a function $f^{\prime} : E \rightarrow \mathbb{R} $ such that $f^{\prime}\left( v \right) = f\left( v \right) $ and $f^{\prime}$ preservs the norm:    
  \begin{equation*}
    \begin{split}
     &  f^{\prime \top}f^{\prime}   = \sum_{v \in V}f^{\prime}\left( v \right)f^{\prime}\left( v \right)   =   \sum_{v \in V } f^{\top}\left( vg \right)f\left( vg \right) = f^{\top}f \\
     \Rightarrow  &  \max_{f \perp \mathbf{1}} { \frac{f^{\top}A_{G^{\prime}} f  }{ f^{\top}f}} =\max_{f \perp \mathbf{1}} { \sum_{gv}\sum_{ u\sim_{G} v }\frac{f\left( gu \right) f \left( vg \right)  }{ f^{\top}f}} 
    \end{split}
  \end{equation*}
  By the Interlacing Theorem, \cite{HAEMERS1995593} the second eigenvalue of any subgraph of $G^{\prime}$ is less than the $\lambda^{\prime}$, In particular, the eigenvalue of the graph obtained by taking the edges that are associated with elements of the $ S_{g} / S $, denote that subgraph by $G^{\prime}_{ / S}$. Because $S_{g} / S \cap S = \emptyset $, we have that the edges sets of $G, G^{\prime}$ are disjointness sets. Hence the adjacency matrix of the graphs union equals the sum of their adjacency matrices. So in total, we obtain that:  
    \begin{equation*}
    \begin{split}
      \lambda^{\prime} &= \max_{f \perp \mathbf{1}} { \frac{f^{\top} \left( A_{G} + A_{G^{\prime}_{/S}} \right) f  }{ f^{\top}f}} \\
      & \le  \max_{f \perp \mathbf{1}} { \frac{f^{\top}A_{G} f  }{ f^{\top}f}} +  \max_{f \perp \mathbf{1}} { \frac{f^{\top}A_{G^{\prime}_{/S}} f  }{ f^{\top}f}} \\
      & \le \lambda + \lambda = 2\lambda
    \end{split}
  \end{equation*} 
  $\square$ 
  \paragraph{Claim.} If $\Delta$ is a constant greater than two, and $G$ is a $\lambda$-algebric expander with girth at length $\Omega\left( \log n \right)$, then it there exists a $g \in \Gamma$ such that $S_{g}\cap S = \emptyset$.  
  \paragraph{Proof.} As $\Delta > 2 $ there must be at least two different elements $s_{1},s_{2} \in S$  such that $s_{1} \neq s_{2}, s_{2}^{-1}$. Pick $g = s_{1}s_{2}$. Now assume through contradiction that there also exists $s,t \in S$ such that $gsg^{-1} = r \Rightarrow gs = rg$ and notice that the fact that $s_{1}\neq s_{2}^{-1}$ guarantees that both terms are a product of $3$ element group. Therefore either that there is a $6$-length cycle in the graph, Or that there is element-wise equivalence, namely $s_{1} = r, s_{2} = s_{1}, s=s_{2}$. The first case contradict the lower bound on the expander girth, which is at least $\Omega \left( \log_{\Delta}(n) \right)$, while the other stand in contradiction to the fact that $s_{1} \neq s_{2}$ $\square$  
  \paragraph{Remark. Regarding Quantum Codes.} Notice that any complex designed to hold CSS qLDPC codes must have constant length cycles. Otherwise, the distance of $C_{x}$ will not be constant, and therefore the condition $H_{x}H_{z}^{\top} =0$ could be satisfied only if $H_{z}$ is not a constant row-weight matrix, Put differently $C_{z}$ is not an LDPC code. Consequently, any trial to generalize the construction for obtaining quantum codes must not rely on that claim.    

  \paragraph{Remark. Note On Random Construction.} One might wondring if using \emph{Cayley} is necssery. We conjecure that there is a constant $c > 0$ such that sampling pair of  $\left( 1 + c \right)\frac{1}{2}\Delta$ regulr random graphs, and than take the anti-symatry union of them might also obtain a good expander such that each of the reseuide part also has good expansion with heigh probability.  
  \paragraph{Lemma.} \ctt{Rewrite}. Consider the graph $G$ as defind above (direct subset of \emph{Cayley} graph) and let $S$, $T$ be subsets of the vertices. Then the flux of $S$ over $T$ is at most: 
  \begin{equation*}
    \begin{split}
      E_{G^{\prime}}(S,T) \le \frac{1}{2} \Delta\frac{|S||T|}{n} + \lambda\sqrt{|S||T|} 
    \end{split}
  \end{equation*} 

  \paragraph{Proof.} The only edges that can interferce are the edge defined by $J^{\prime}$. Therefore it's enough to use the mixing expander lemme on the $\frac{1}{2}\Delta$-regular graph. $\square$


  \paragraph{Proof of Theorem 1+.} Noitce that $\frac{1}{2} < \frac{2}{3} = q$, Thus reapting exactly over proof above obtains that: 
  \begin{equation*}
    \begin{split}
      w_{E/E^{\prime}}\left( x|_{U_{\text{max}}} \right) \ge \left( \delta_{0} - \frac{2}{3} - \frac{1}{q}\frac{2\lambda}{\Delta} \right)q\Delta |U_{\text{max}}|
    \end{split}
  \end{equation*}
  Choseing $J$ such that \emph{Cayley}$\left( \Gamma, J \right)$ is ramnujan provid that $ \frac{2\lambda}{\Delta q}$ sacle as $\Theta\left( \frac{1}{\sqrt{\Delta}} \right)$. That close the case in which there is a linear size layer of nontrival suggestions. In other case, in which any such layer is at size less than $\alpha^{\prime}n$ ( $\alpha^{\prime} = \left( \delta_{0} - \left( q - \frac{1}{2} \right) \right)$ ? ) then we obtain the testbility for free $\square$
      \section{Good Quantum Codes, logaritmic-check-weight.} 
In the following section we will construct a family of complexes on which we will define a pairs of Tanner Codes, evently, they will used to compose a CSS pairs of good quantum codes.  
  \paragraph{Inifinte Family Of Tanner Quantum Codes.} 
  Let $p$ be a prime and $\delta \in \left( 0,1 \right)$. Consider the Cayly graphs obtained by taking uniformly a $c\left( \delta \right)\log n$ generators of the cyclic group at order $p$, denote that set by $S$. It was shown by N.Alon \ctt{cite Noga} that with high probability that process yield a Graph with $\delta$-algebric expansion. Now, consider the double cover of that graph and denote it by $G = \left( V = V^{+} \cup V^{-},E \right)$. And define the folowing graph denoted by $\Gamma^{\pm} = \left(V^{\pm}, E^{\prime}\right)$:
  \begin{equation*}
    \begin{split}
      \left( \left(u , \pm  \right), \left( v, \pm \right) \right) \in  E^{\prime} \Leftrightarrow \exists a\neq b \in S \ s.t \ abu = v     
    \end{split}
  \end{equation*}
     

  \section{Decodeing and Testing}
  For completeness, we show exactly how Theorem 1 implies testability. The following section repeats Leiverar's and Zemor's proof \cite{leverrier2022quantum}. Consider a binary string $x$ that is not a codeword. The main idea is the observation that the number of bits filliped by (any) decoder, while decoding $x$, bounds the distance $d\left( x, C \right)$ from above. In addition, the number of positive checks in the first iteration is exactly the number of violated restrictions.
%\begin{figure*}[h]
%\begin{adjustbox}{width=\textwidth}
  \paragraph{Definition.}Let $L = \{L_{i}\}^{2|E|}_{0}$  be a series of $2|E|$. Such that for each vertex $ v \in V$ $\sum_{ e = \{u,v\} }{ L_{e_v} } \in C_{0}$. We will call $L$ a \textit{Potential list} and refer to the $e_{v}$'the element of $L$ as a suggestion made by the vertex $v \in V$ for the edge $e \in E$. Sometimes we will use the notation $L_{v}$ to denote all the $L$'s coordinates of the form $ L_{e_{v}} \forall e \in \text{Support} \left( v \right) $. Define the \textit{Force} of $L$ to be the following sum $  F\left( L \right) = \sum_{e = \{v,u\} \in E }{ \left(L_{e_v} + L_{e_u}\right) }$ and notice that $ F\left( L \right) \in C_{\oplus}$. And define the \textit{state} $S(L) \subset \mathbb{F}^{|E|}_{2}$ of $L$ as the vector obtained by choosing an arbitrary value from $ \{ L_{e_v}, L_{e_u} \}$ for each edge $e \in E$.  
  \paragraph{Claim.} Let $L$ be the Potential list. If $F(L)=0$ then $S(L)\in C$.
  \paragraph{Proof.} Denote by $\phi\left( e \right) \subset \{ L_{e_v}, L_{e_u} \}$ the value which was chosen to $e = \{v,u\} \in E$. By $F\left(L\right) = 0$ , it follows that $ L_{e_v} + L_{e_u} = 0 \Rightarrow L_{e_v} = L_{e_u} = \phi\left( e \right) $ for any $e \in E$. Hence for every $v\in V$ we have that $ S\left( L \right)|_{v} = \sum_{u \sim v}{ \phi\left( \{v,u\} \right) } =  \sum_{u \sim v}{ L_{e_v }} \in C_{0}$ $ \Rightarrow S\left( L \right) \in C \square$   

  The decoding goes as follows. First, each vertex suggests the closet $C_{0}$'s codeword to his local view. Those suggestions define a Potential list, denote it by $L$, then if $F\left( L \right) <\tau$, by Theorem 1, one could find a suggestion of vertex $v$ and a codeword $c_v$ such that updating the value of $L_{v} \leftarrow L_{v} + c_{v}$ yields a Potential list with lower force. Therefore repeating the process till the force vanishes, obtain a Potential list in which its state is a codeword. 
  \paragraph{Definition.} Let $\tau > 0, f : \mathbb{N} \rightarrow \mathbb{R^{+}}$, and consider a Tanner Code $C = \mathcal{T}\left( G, C_{0} \right)$. Let us Define the following decoder and denote it by $\mathcal{D}$.  
  \paragraph{}
  \begin{algorithm}[H]
    \caption{Decoding}
    \label{alg:three}
    \KwData{ $x \in \mathbb{F}_{2}^{n}$ }
    \KwResult{ $\arg\min {\left\{  y \in C : |y + x|  \right\} }$ if $d(y,C) < \tau $ and False otherwise. }
    $ L \leftarrow \text{Array} \{ \} $\\
    \For { $ v \in V$} {
      $c^{\prime}_{v} \leftarrow \arg\min {\left\{  y \in C_{0} : |y + x|_{v} |  \right\} } $\\
      $ L_{v} \leftarrow c^{\prime}_{v}$
    }
    $ z \leftarrow \sum_{v \in V}{c^{\prime}_{v}} $\\
    \eIf{ $ |z| < \tau \frac{n}{f\left( n \right)} $}{
      \While{ $|z| > 0$ }{
	find $v$ and $c \in C_{0}$ such that $|z + c_{v}| < |z|$\\
	$z \leftarrow z + c_{v}$ \\
	$ L_{v} \leftarrow  L_{v} + c_{v}$
      }
    }{
      reject. 
    }
    \Return  $S(L) $

  \end{algorithm}

  \paragraph{Theorem.} Consider a Tanner Code $C = [n, n\rho, n\delta]$ and the disagreement code $C_{\oplus}$ defined by it. Suppose that for every codeword $ z \in C_{\oplus}$ in $C_{\oplus}$ such that $|z| < \tau^{\prime} n / f\left(n\right)$, there exists another codeword $y \in C_{\oplus} $ such that $|y| < |z|$, set $\tau \leftarrow \frac{\tau^{\prime} }{6 \Delta} \delta$ then, 

  \begin{enumerate}
    \item $\mathcal{D}$ corrects any error at a weight less than $\tau n / f\left(n\right)$.   
    \item $C$ is $f\left( n \right)$ testable code.
  \end{enumerate}


  \paragraph{Proof.} So it is clear from the claim above that if the condition at line (6) is satisfied, then $\mathcal{D}$  will converge into some codeword in $C$. Hence, to complete the first section, it left to show that $\mathcal{D}$ returns the closest codeword. Denote by $e$ the error, and by simple counting arguments; we have that $\mathcal{D}$ flips at most:  
  \begin{equation*}
    \begin{split}
      d_{\mathcal{D}}\left( x, C \right) & \le 2|e|\Delta + \tau \frac{n}{f\left( n \right)}\Delta
    \end{split}
  \end{equation*}
  bits. Hence, by the assumption, 
  \begin{equation*}
    \begin{split}
      d_{\mathcal{D}}\left( x, C \right) & \le 3\Delta \tau \frac{n}{f\left( n \right)} \le 3\Delta \tau\delta n < \frac{1}{2} \delta n  
    \end{split}
  \end{equation*}
  Therefore the code word returned by $\mathcal{D}$ must be the closet. Otherwise, it contradicts the fact that the relative distance of the code is $\delta$.
  To obtain the correctness of the second section, we will separate when the conditional at the line (5) holds and not. And prove that the testability inequality holds in both cases. 
  Let $x \in \mathbb{F}_{2}^{n}$ and consider the running of $\mathcal{D}$ over $x$. Assume the first case, in which the conditional at line (5) is satisfied. In that case, $\mathcal{D}$ decodes $x$ into its closest codeword in $C$. Therefore:
  \begin{equation*}
    \begin{split}
      d\left( x, C \right) \le & \ d_{D} \left( x, C \right) \le m\xi\left( x \right)\Delta +  |z|\Delta  \\ \le &  \  m\xi\left( x \right)\Delta + m\xi\left( x \right)  \Delta^{2} \\ 
      \frac{d\left( x, C \right)}{n} \le & \  \kappa_{1} \xi\left( x \right)    
    \end{split}
  \end{equation*}
  Now, consider the other case in which: $ |z| \ge \tau \frac{n}{f\left( n \right)}  $.
  \begin{equation*}
    \begin{split}
      \frac{d\left( x, C \right)}{n} & \le 1 \le \frac{|z|}{\tau n}f\left( n \right) \le \frac{m}{n} \frac{1}{\tau} \Delta \xi\left( x\right)f\left( n \right) \\ & \le \kappa_{2} \xi\left( x \right)f\left( n \right)  
    \end{split}
  \end{equation*}
  Picking $ \kappa \leftarrow \max \{ \kappa_{1}, \kappa_{2} \}$ proves $f\left( n \right)$-testability $\square$
%\end{adjustbox}
%\end{figure*}
%\end{multicols*}
\printbibliography 
\end{document}

 



