\section{Good Quantum Codes, logaritmic-check-weight.} 
In the following section we will construct a family of complexes on which we will define a pairs of Tanner Codes, evently, they will used to compose a CSS pairs of good quantum codes.  

\begin{definition}[Abelian Square Complex] \label{AbsC}
  Let $\Gamma$ be abelian group at order $|\Gamma| = n$. And consider a disjointness subsets pair $A,B \subset \Gamma$. Define the generators set $S_{\pm}  = \left\{ b^{\pm 1} a : a \in A, b \in B   \right\}$. In addition define the map $f : \left( \cdot \times \cdot \right) \rightarrow \left[ \ \frac{1}{2} |S_{\pm}| \cdot |\Gamma|  \ \right]  $. 
\begin{equation*}
  \begin{split}
    f\left( \left\{ g, ba g  \right\}  \right)= f\left( \left\{ bg, ag  \right\}  \right)
  \end{split}
\end{equation*}
\end{definition}

\begin{definition}[Abelian Square Complex Code] Let $G_{\pm}$ be an abelian square complex as defined in \ref{AbsC}. And let $C_{A},C_{B} \subset \mathbb{F}_{2}^{q\Delta}$ be a pair of samall codes. Denote by $C_{+} = \duC$ and $C_{-} = \duduC $ their dual tensor codes. 
\end{definition}

%\begin{definition}
%\end{definiition}

\begin{theorem*}[Inifinte Family Of Tanner Quantum Codes] 
Let $\delta_{0} \in \left( \frac{2}{3} ,1 \right)$ and let $\varepsilon > 0$. Consider the a pair of generator subset $A,B$ of the Abelian at order $n$ obtained by taking uniformly a $ \sqrt{ c\left( \delta_{0} + \varepsilon \right)\log n }$. And condisder the quantum Code $Q$ defined by $A,B,C_{A},C_{B}$.  Then with high probabiliy the $Q$ is a good qLDPC code.
\end{theorem*}
\begin{claim} \label{unif}
  $S_{+}$ is uniform distriuted. 
\end{claim}
\begin{proof}
  Define the random variable $X_{0}$ to be the sampled group element. We will show that for any $g \in \Gamma $ the probability that $X_{0} = g$ is $1/|\Gamma|$. By the low of total probability, we have that:     
  \begin{equation*}
    \begin{split}
      & \prb{X_{0} = g} = 1 -  \prb{X_{0} \neq  g} = 1 - \sum_{A}{ \prb{ \forall b \in A, b \in B \ \ ab = g | A } } \\ & =  \sum_{A}{ \prod_{a\in A} {\prb{ \exists b \  ba= g | a } } \prb{ A }  } \\ 
      & \ \ =  1-  \sum_{A}{  \left( 1 -   \left( \frac{1}{n} \right) \right)^{|B| \cdot |A| }   \prb{ A }  } = 1 -  \left( 1 -   \left( \frac{1}{n} \right) \right)^{|B| \cdot |A| } 
    \end{split}
  \end{equation*}
  And that is the exactly proba
\end{proof}
\begin{claim}
  Let $C_{0} = C_{A}\otimes C_{B}$ and consider the code $\testgo$ defined in \ref{testtaner}. Then $C_{x} = \left( \testgo \right)_{\oplus}$. 
\end{claim}
\begin{claim}
  The quantum code $Q = C_{x}/ C_{z}$ is the all \ireducable codewords of $C_{x}$.   
\end{claim}
\begin{proof}
  It was shown by N.Alon \cite{Noga}  that with high probability that process yield a Graph with $\delta$-algebric expansion.
  \end{proof}
