

%\newcommand*{\ACM}{}%

\ifdefined\ACM

%\documentclass[sigplan,screen]{acmart}
  \documentclass[manuscript,screen,review]{acmart}

\else
  \documentclass{article}
  \input{./usepackage}
  \addbibresource{./sample.bib} 

\fi

\begin{document}

\input{newcommands}

\title{Another reason that makes finding good qLDPC an hard task.} 
\author{David Ponarovsky}
  \maketitle
  
  \begin{claim}
    Let $C_{X}/C_{Z}^{\perp}$ be CSS a qLDPC code with non constant distance. Denote by $H_{X},H_{Z}$ their parity check matrices and by $C_{Z}^{\prime},H_{Z}^{\prime}$ the code and the parity check matrix obtaind by removing one arbitrary check form $H_{Z}$. Then $C_{X}/C_{Z}^{\perp \prime}$ is a CSS pair with constant distance.    
  \end{claim}
  \begin{proof}
    First notice that any of the rows of $H_{Z}^{\prime}$ commute with the rows of $H_{X}$, so we defently obtain a CSS code with higher rate. Seconed any codeword of the quantum code $C_{X}/C_{Z}^{\perp, \prime}$ has the form  
    \begin{equation*}
      \begin{split}
        \ket{ \mathbf{x} } = \sum_{z \in C_{Z}^{\perp, \prime}}{\ket{ x + z}}
      \end{split}
    \end{equation*}
    Using the fact that the generator matrix of the dual of any binary code is the transposed parity check matrix of it, the above become:
\begin{equation*}
      \begin{split}
        \ket{ \mathbf{x} } = \sum_{z \in \mathbb{F}_{2}^{s}}{\ket{ x + H_{Z}^{\perp, prime} z}}
      \end{split}
    \end{equation*}
Observe that because $C_{X}/C_{Z}^{\perp} \subset  C_{X}/C_{Z}^{\prime, \perp}$ we have also that the following state is in $C_{X}/C_{Z}^{\perp, \prime}$:
\begin{equation*}
  \begin{split} 
    \ket{ \mathbf{x^{\prime}} } = & \sum_{z \in \mathbb{F}_{2}^{s+1}}{\ket{ x + H_{Z}^{\perp} z}} \\
      =&  \sim_{w \in \mathbb{F}_{2}}\sum_{z \in \mathbb{F}_{2}^{s}}{\ket{ x + H_{Z}^{\perp, prime} z + h^{\prime} w  }}
  \end{split}
\end{equation*}
Where $h^{\prime}$ is the check that removed form $H_{Z}$ to obtain $C_{Z}^{\prime}$. Now let us give an quantum circuit act non-trivaliy on no more than constant qubits and with probability $\frac{1}{2}$ transform $\ket{\mathbf{x}}$ to $ \ket{\mathbf{x}^{\prime}}$. So first we prapre ancila in the $\ket{+}$ state, then controlled on it's value we add $h^{\prime}$. After that we rotate back the ancila by applaing $H$ (Hadamard) again and measuring, with probability $\frac{1}{2}$ we measure $\ket{0}$ and the remaining qubits hold the state $\ket{\mathbf{x}^{\prime}}$. As $h^{\prime}$ is also a check of the LDPC code $C_{Z}$ it has a constant weight and thus all the circuit toach a constant number of qubits. Therfore the operator which transform $\ket{\mathbf{x}}$ into $\ket{\mathbf{x}^{\prime}}$ is supported only on paulis with constanst degree.     
  \end{proof}


  \begin{claim}
Let $C_X/C_Z^{\perp}$ be a CSS qLDPC code with non-constant distance. Denote by $H_X$, $H_Z$ their parity check matrices and by $C_Z^{\prime}$, $H_Z^{\prime}$ the code and the parity check matrix obtained by removing one arbitrary check from $H_Z$. Then $C_X/C_Z^{\perp \prime}$ is a CSS pair with constant distance.
\end{claim}

\begin{proof}
First, notice that any of the rows of $H_Z^{\prime}$ commute with the rows of $H_X$, so we definitely obtain a CSS code with higher rate. Second, any codeword of the quantum code $C_X/C_Z^{\perp \prime}$ has the form  
\begin{equation*}
  \begin{split}
    \ket{\mathbf{x}} = \sum_{z \in C_Z^{\perp \prime}}{\ket{x + z}}
  \end{split}
\end{equation*}
Using the fact that the generator matrix of the dual of any binary code is the transposed parity check matrix of it, the above becomes:
\begin{equation*}
  \begin{split}
    \ket{\mathbf{x}} = \sum_{z \in \mathbb{F}_2^s}{\ket{x + H_Z^{\top \prime}z}}
  \end{split}
\end{equation*}
Observe that because $C_X/C_Z^{\perp} \subset C_X/C_Z^{\prime \perp}$, we have also that the following state is in $C_X/C_Z^{\perp \prime}$:
\begin{equation*}
  \begin{split} 
    \ket{\mathbf{x'}} = & \sum_{z \in \mathbb{F}_2^{s+1}}{\ket{x + H_Z^{\top}z}} \\
    =& \sum_{w \in \mathbb{F}_2}\sum_{z \in \mathbb{F}_2^s}{\ket{x + H_Z^{\top \prime}z + h'w  }} \\ 
    =& \frac{1}{\sqrt{2}}\left( \ket{\mathbf{x}} + \ket{\mathbf{x} + h^{\prime}} \right)
  \end{split}
\end{equation*}
Where $h'$ is the check that was removed from $H_Z$ to obtain $C_Z^{\prime}$. Now let us give a quantum circuit that acts non-trivially on no more than a constant number of qubits and with probability $\frac{1}{2}$ transforms $\ket{\mathbf{x}}$ to $\ket{\mathbf{x'}}$. So first we prepare an ancilla in the $\ket{+}$ state, then controlled on its value we add $h'$. After that, we rotate back the ancilla by applying $H$ (Hadamard) again and measuring.

With probability $\frac{1}{2}$ we measure $\ket{0}$ and the remaining qubits hold the state $\ket{\mathbf{x'}}$. As $h'$ is also a check of the LDPC code $C_Z$, it has a constant weight and thus all the circuit touches a constant number of qubits. Therefore, the operator which transforms $\ket{\mathbf{x}}$ into $\ket{\mathbf{x'}}$ is supported only on Paulis with constant degree.     
\end{proof}  

%\begin{multicols*}{2}
% \input{preamble}

\printbibliography
\end{document}





