
\inb{ Move this definition to the beginning of the paper. }
\begin{definition}
We model the qubits on the finite toric with a side length $n$ by the projection:
  \begin{equation*}
    \begin{split}
      (x_{1}, x_{2}, .., x_{d}) \mapsto (x_{1}\bmod n, x_{2}\bmod n, .., x_{d}\bmod n) 
    \end{split}
  \end{equation*}
\end{definition}

\inb{ Rewrite when we talk about the first time we have deviation clusters of size $\in (\alpha d, d)$. The reason is that having those assumptions means all the droplets in the past shrank; thus, we can use the ratio of edges to time-leaves in the big subgraph.} 

\begin{claim}
  Let $\hat{K}$ be a spanned slice, and let $\omega$ be an explanation for $\hat{K}$. Assume that:
  \begin{itemize}
    \item  The number of edges in $w$ is greater than $\beta n$.
    \item For any spanned slice $\hat{K}^{\prime} \in \omega$ such $\hat{K}^{\prime}\neq \hat{K}$ it holds that $\Size{\hat{K}^{\prime}}< \delta n$.
  \end{itemize}
Then there is a subgraph (subtree) $\omega^{\prime}$ of $\omega$ such that $\omega^{\prime}$ has less than $\frac{\beta}{2}n$ edges and at least $\frac{\beta}{4\gamma} n$ leaves.
\end{claim}


\begin{claim}
  Consider a probability space, $(\Omega, \mathbf{Pr})$, for which the atomic events are subgraphs of $G = (V = \mathbb{Z}^{d} \times \mathbb{Z}_{t}, E)$, where two vertices might be connected only if their difference in the time coordinate is at most $1$ and their Hamming distance in the space coordinate is at most $2$. We say that a vertex of such a subgraph is a time-leaf if and only if it is not connected to vertices with a lower time coordinate. Notice that an outcome $\omega \in \Omega$ does not have to be connected. Suppose that the following three conditions hold:
\begin{enumerate}
    \item There exists $n \in \mathbb{N}$ such that $\omega$ is invariant under shifting by $n \cdot \mathbf{1}_{i}$ for any $i \in [d]$. 

    \item The probability function $\mathbf{Pr}$ induces a locally stochastic noise bound over the time-leaves, which are different in their space coordination module $n$. Namely, there is $p \in (0,1)$ such that for any $S \subset V$, with a maximal subset $S^{\prime} \subset S$, such that for any $v = (v_{x},v_{t}), u = (u_{x},u_{t}) \in S^{\prime}$ it holds that $v_{x} \mod n \neq u_{x} \mod n$, the probability that $S$ are time-leaves of an outcome subgraph is less than:
    \begin{equation*}
      \begin{split}
        \prb{S \text{ are time-leaves } } \le p^{|S^{\prime}|}
      \end{split}
    \end{equation*}
  \item For any subgraph $\omega \in \Omega$, and for any $\omega^{\prime} \subset \omega$ such $\omega^\prime$ is connected. The ratio of edges to time-leaves of $\omega^{\prime}$ is at most $\gamma$. 
\end{enumerate}
Then there is $p_{c} \in (0,1)$ such that for $p < p_{c}$, the probability of sampling a subgraph with more than $\beta n$ vertices is less than:
\begin{equation*}
  \begin{split}
    t n^{d} q^{n}
  \end{split}
\end{equation*}
\begin{proof}
  Let $\omega \in \Omega$ with more than $\beta n$ vertices, observes that a spanning tree of $\omega$ has a ratio of edges to time-leaves which is at most $\omega$'s ratio, and number of edges equals to $\omega$'s vertices - 1. In addition the time-leaves of such spanning tree are just leaves. Therefore, by \cref{claim:big_subtree}, $\omega$ has a subtree with less than $\frac{\beta}{2}n$ edges and at least $\frac{\beta}{4\gamma} n$ time-leaves. 
  Now, since any two connected vertices are at a space-distance of at most $1$, it follows that all the leaves in the subtree are at a space-distance of at most $\beta n$ from each other. Thus, if $\beta < 1$, no two of them have the same space-coordinate modulo $n$. And therefore the probability to have such subtree is at most $p^{\frac{\beta}{4\gamma}n} $. 
  
Because any $\omega$ with more than $\beta n$ vertices implies the existence of a subtree with size less than $\frac{\beta}{2}n$, it's enough to bound the probability of having such a subtree. Considering that the trees are invariant to shifting by $n \cdot \mathbf{1}_{i}$, we have that it's sufficient to show that there are no such trees which are rooted in the finite cube $\mathbb{Z}_{n}^{d} \times \mathbb{Z}_{t}$. Finally, we use \cref{claim:counting_trees} to bound the number of such trees given a fixed root. Overall, we get:
  \begin{equation*}
    \begin{split}
      \prb{\text{No } \omega \text{s with more than  } \beta n \text{ vertices} } \le n^{d} t  \left( \xi^{2}  p^{\frac{\beta}{4\gamma}} \right)^{n}   
    \end{split}
  \end{equation*}
\end{proof}



\end{claim}
