

%\newcommand*{\ACM}{}%

\ifdefined\ACM

%\documentclass[sigplan,screen]{acmart}
\documentclass[manuscript,screen,review]{acmart}

\else
 \documentclass[12pt]{extarticle}
%\usepackage{libertine}
\usepackage{cuted}%\usepackage{widetext}
\input{./usepackage}
\usepackage{cancel}
\usepackage{tikz-3dplot}
\usepackage{subcaption}
\addbibresource{./sample.bib}

\fi

\begin{document}
\input{newcommands}
%\title{ $\textbf{QNC}_{1} \subset $ noisy-\textbf{BQP}}
\title{ SWEEP rule on the KD-Toric code }
%\author{Michael Ben-Or \ \ David Ponarovsky}
\maketitle

\newcommand*{\Mbas}{\mathcal{X}^\prime}
\newcommand*{\bas}{\mathcal{X}}
\newcommand*{\sMbas}{\Mbas}
\newcommand*{\QQ}{C_{X}/C_{Z}^\perp }
\newcommand*{\trig}{ Triorthogonal }
\newcommand*{\Hyp}{ Hyperproduct }
\newcommand*{\Cin}{ C_{\text{initial}} }
\newcommand*{\Ctan}{ C_{\text{Tan}} }



\newcommand*{\QACze}{\mathbf{QAC}_{0}}
\newcommand*{\QNCzef}{\mathbf{QNC}_{0,f}}
\newcommand*{\QNCze}{\mathbf{QNC}_{0}}
\newcommand*{\QNCon}{\mathbf{QNC}_{1}}
\newcommand*{\NCon}{\mathbf{NC}_{1}}
\newcommand*{\noiseQNCon}{noisy-$\QNCon$}
\newcommand*{\QNC}{\mathbf{QNC}}
\newcommand*{\QNCG}{\mathbf{QNC_G}}
\newcommand*{\NC}{\mathbf{NC}}
\newcommand*{\QNCiG}{\mathbf{QNC_{G,i}}}


% Constant depth fault tolerance construction.   
\newcommand*{\CDO} {CDFT} 
\newcommand*{\xb}{\mathbf{x}}


\section{SWEEP Rule Decoder on the Toric}
The decoder works as follows: each vertex $v$ looks for a suggestion $\hat{v}$ on $\uparrow{(v)}\cap lk_{2}$ that matches $\sigma_{v}^{+}$. If there are more than one, then pick the one which has the minimal weight.

%\tdplotsetmaincoords{70}{120}


\begin{figure}[h]
  \centering
  \begin{tikzpicture}[scale=1.5]

\fill[red!30]
  (1,1,0) -- (2,1,0) -- (2,2,0) -- (1,2,0) -- cycle;
% draw grid lines
\foreach \x in {0,1,2} {
  \foreach \y in {0,1,2} {
    \draw[gray] (\x,\y,0) -- (\x,\y,2);
  }
}

\foreach \x in {0,1,2} {
  \foreach \z in {0,1,2} {
    \draw[gray] (\x,0,\z) -- (\x,2,\z);
  }
}

\foreach \y in {0,1,2} {
  \foreach \z in {0,1,2} {
    \draw[gray] (0,\y,\z) -- (2,\y,\z);
  }
}

% draw lattice points
\foreach \x in {0,1,2} {
  \foreach \y in {0,1,2} {
    \foreach \z in {0,1,2} {
      \fill (\x,\y,\z) circle (1.5pt);
    }
  }
}

\draw (2.5,1) node { $\rightarrow$ };
\end{tikzpicture} \begin{tikzpicture}[scale=1.5]

\fill[red!30]
  (1,1,0) -- (2,1,0) -- (2,2,0) -- (1,2,0) -- cycle;
% draw grid lines
\foreach \x in {0,1,2} {
  \foreach \y in {0,1,2} {
    \draw[gray] (\x,\y,0) -- (\x,\y,2);
  }
}

\foreach \x in {0,1,2} {
  \foreach \z in {0,1,2} {
    \draw[gray] (\x,0,\z) -- (\x,2,\z);
  }
}

\foreach \y in {0,1,2} {
  \foreach \z in {0,1,2} {
    \draw[gray] (0,\y,\z) -- (2,\y,\z);
  }
}

% draw lattice points
\foreach \x in {0,1,2} {
  \foreach \y in {0,1,2} {
    \foreach \z in {0,1,2} {
      \fill (\x,\y,\z) circle (1.5pt);
    }
  }
}
\end{tikzpicture}
  \caption{SWEEP rule}
  \label{fig:sweep}
\end{figure}



\section{Span Shrinking}

Define the potentials functions $L_{i} : \mathbb{R}^{d} \rightarrow \mathbb{R}$ as follow\footnote{Notice that we use opposite signs relative to Berman and Peter Gacs, yet we agree with Perskil.}: 
\begin{equation*}
  \begin{split}
L_{i}(\xb{}) =    \begin{cases}
  \xb{}_{i} & i < d + 1 \\ 
  - \braket{\mathbf{1}, \xb{}} & i = d+1
\end{cases}
  \end{split}
\end{equation*}
The \textbf{Size} of a subset $S$ is defined as:   
\begin{equation*}
  \begin{split}
  \mathbf{Size}(S) = \sum_{i}\max_{\xb{} \in S} L_{i}(\xb{})
  \end{split}
\end{equation*}
\begin{claim}[Span Shrinking Property]
 Namely, let $e$ be an unsatisfied check at time $t$, and let $H_{e}$ be the unsatisfied checks at time $t-1$. Then there is a set $H^{\prime}_{e} \subset H_{e}$ such that:
\begin{enumerate}
  \item For any $i < d + 1$ there exists $e^{\prime} \in H^{\prime}_{e}$ such $L_{i}(e^{\prime}) \ge L_{i}(e)$. 
  \item There exists $e^{\prime} \in H^{\prime}_{e}$ such that $L_{d+1}(e^{\prime}) \le L_{d+1}(e) + 1 $. 
\end{enumerate}
\end{claim}
\begin{remark}
Numerically, we showed that the 'span shrinking property' holds for the checks on the 3D Toric (it required running over $\sim 2^{11}$ assignments of bits over the local environment of the check).
\end{remark}
\begin{proof}
  Consider a vertex $v$ which at time $t$ adjoins to an unsatisfied edge $e$, let $u,w$ be vertices which have a positive faces that adjoin to $e$. 
  \begin{enumerate}
    \item If $\hat{u}|_{e} \neq \emptyset$, then the parallel edge to $e$ going out from $u$ belongs to $H_{e}$. Denote it by $e_u$, taking $e_{u}$ satisfies at least two (three in 4D) of the first $d$ inequalities and the last $d+1$th inequality. Denote by $x \in [d]$ the index of the inequality which isn't satisfied by $e_{u}$. So it remains to prove the existence of $e^{\prime} \in H_{e}$ for which $L_x(e^{\prime}) \ge L_{x}(e)$.

Consider the assignment of bits at time $t-1$ over the complex, and consider the graph $G = \left( \mathcal{F}, E \right)$ induced by associating vertices with any face that is set to $1$ by the assignment. Two vertices are connected if their origin faces share an edge. Let $K \subset \mathcal{F}$ be a connected component of faces that contains the faces supported on $u$.

      We say that $K$ is $d$ far from $u$ if:   
      \begin{equation*}
        \begin{split}
          \max_{f \in K} | f_{x} - u_{x} | \le d
        \end{split}
      \end{equation*}
      Now, we will prove by induction on $d$ that there is a face $f \in K$ with $f_{x} \ge v_{x}$ such one of its edge is not satisfied. 
      \begin{enumerate}
        \item \textbf{Base.} The edge from $v$ which point at the $\hat{z}$ direction must not be satisfied.  

\begin{figure}[h]
  \centering
  \begin{tikzpicture}[scale=3]

\fill[red!30]
  (0,1,1) -- (0,1,0) -- (0,2,0) -- (0,2,1) -- cycle;
\fill[red!30]
  (0,1,1) -- (1,1,1) -- (1,2,1) -- (0,2,1) -- cycle;

% draw lattice points
\draw[blue] (1,1,1) -- (1,2,1);
\draw[gray] (1,1,1) -- (1,1,0);
\draw[gray] (1,1,1) -- (0,1,1);
\draw[gray] (0,1,1) -- (0,2,1);
\draw[gray] (0,1,1) -- (0,1,0);
\draw[gray] (0,1,0) -- (0,2,0);
\draw[gray] (0,2,1) -- (1,2,1);
    \draw (1,1,1) node { $v$} ;
    \draw (1,1,0.5) node { $e$} ;
\fill (1,2,1) circle (0.5pt);
    \draw (0,1,1) node { $u$ } ;
%\fill (0,1,1) circle (1.5pt);
\fill (0,1,0) circle (0.5pt);
\fill (0,2,1) circle (0.5pt);
\end{tikzpicture} 
\caption{ The induction base: In red, we have the faces on the support of $u$. The blue edge has the same $x$-coordinate as $e$. Any attempt to zero out the syndrome on the edge results in adding a face that is at least 2-far from $u$. Any configuration which is at most 1-far from $u$ has to have that local view, yet might be connected to more faces which don't adjoin the blue edge. }
  \label{fig:base}
\end{figure}
        \item \textbf{Assumption.} Assume that for any $K$ which is at most $d-1$ far from $u$ there is a face, with adjoins edge that is both has a $x$-coordinate that is greater than $u_{x}$ and is not satisfied.   
        \item \textbf{Induction Step.} Consider a connected component $K$ that is $d$-far from $u$. Notice that if by substitute a co-boundary (stabilizer) from $K$ we get $K^{\prime}$ that is at most $d^{\prime}$ far from $u$ for some $d^{\prime} < d$ then we done. That because: $\partial_{2} K^{\prime} = \partial_{2} (K + z) = \partial_{2} K$ for some $z \in \ker \partial_{2} $. 
          

          On the other hand, \ctt{Finish that.} 
      \end{enumerate}

    \item  Else, if for any $u \in \downarrow(u) \cap lk_{1}$ it holds that $\hat{u}|_{e} = \emptyset$, then it must be that $e \in H_{e}$ because $\hat{v}$ can only decrease the syndrome on $v$. Moreover, it follows that $\hat{v} = \emptyset$ (otherwise, the suggestion would zero out the syndrome on $\uparrow(v) \cap lk_{2}$). Thus, $\sigma_{v} \not\subset \uparrow(v) \cap lk_{2} \Rightarrow$ there is also an edge $e^{\prime} \in H_{e}$ where $e^{\prime} \in \downarrow(v)$. In that case, take $e \in H_{e}$ as the edge satisfies the first $d$ equalities and $e^{\prime}$ for satisfying the $d+1$th inequality.
  \end{enumerate}
\end{proof}


\section{SWEEP Rule Decoder on the Toric, version II.}

Consider the presentation of a $d$-dimensional toric by the Cayley graph of the $\left( \mathbb{Z}_{n}^{d}, + \right)$ group generated by the elements $S = \{ 1_{i} : i \in [d] \}$ (where $1_{i}$ is the vector consisting of one at the $i$th coordinate and zero elsewhere). We say that an edge $\{x, y\}$ is positive relative to a plaquette $\{v, g_{1}v, g_{2}g_{1}v, g_{2}v\}$, defined by a rooted vertex $v \in \mathbb{Z}_{n}^{d}$ and the generators $g_{1}, g_{2} \in S$, if $x = v$ and $y$ is either $g_{1}v$ or $g_{2}v$. In our code, bits are set on the plaquette, and the edges correspond to checks that restrict the parity of the bits on their support to be even.

We generalize Toom's rule in the following manner: Each plaquette asks if both of its positive edges point to a syndrome, namely unsatisfied. If so, then the bit flips itself; for convenience, we will think of the vertex at the end of the positive edges as the vertex which makes the decision and flips the plaquette.

%Consider an embedding of the $d$ Toric into $\mathbb{R}^{d}$, the coordinate of an edge is the mean of its ends.  

%We say that an edge $e$ can be the prev of $e^{\prime}$ if they both share a placket, $e$ is a positive edge relative to the placket while $e^{\prime}$ is negative relative to it. 

Let $\sigma^{(t)}$ be a domain wall at time $t$, and let $\Gamma^{t} = \{ v : \exists \{v,u\} \in \sigma^{t} \}$. We denote by $\phi^{t}$ the subsets of bits which are flipped as a result of applying the Toom's rule at time $t$, and by $\phi_{v}$ the bits which are flipped by vertex $v$. We say that $u$ is added to $\Gamma^{t+1}$ by $v$ at time $t$, if $u\in \Gamma^{t+1}$ and $u \in V(\phi_{v})$. When it clear form the context, we will omit the time, and say that $u$ is added by $v$. 


\begin{claim}
  \label{claim:toombound}
Let $v \in \Gamma^{t}$ for any $u$ that is added by $v$, and for any $x \in [d+1]$, we have $L_{x}(u) \le L_{x}(v) + 1$.
\end{claim}
\begin{proof}
By definition, any $u$ that is added by $v$ is of the form $v + \sum \alpha_{j}1_{j}$, where $\alpha_{j} \in \{0,1\}$ and $\sum \alpha_j \le 2$. Thus, for any $x \in [d]$:
  \begin{equation*}
    \begin{split}
      L_{x}(u) = \braket{1_{x}, v + \sum \alpha_{j}1_{j}} = \braket{1_{x},v} +\alpha_{x} \le L_{x}(v) + 1 
    \end{split}
  \end{equation*}
For $x = d+1$ we have: 
  \begin{equation*}
    \begin{split}
      L_{x}(u) = \braket{-\mathbf{1}, v + \sum \alpha_{j}1_{j}} = \braket{-\mathbf{1},v} - \sum_{j}\alpha_{j} \le L_{x}(v) 
    \end{split}
  \end{equation*}
\end{proof}
\begin{claim}
  \label{claim:toomb}
  Let $v \in \Gamma^{t}$ such that $L_{d+1}(v)$ is a (local) maxima in $\Gamma^{t}$ then for any $u$ which is added by $v$ we have $L_{d+1}(u) \le L_{d+1}(v) - 1$. 
\end{claim}
\begin{proof}
  We will prove that $v \notin \Gamma^{t+1}$, and then by repeating on \cref{claim:toombound} where $\sum{\alpha_{j}} \ge 1$, we get the desired result. Assume, toward contradiction, that $v \in \Gamma^{t+1}$, and denote by $w$ the vertex that adds $v$. If $w \neq v$, then there is at least one coordinate $i$ for which $w_{i} < v_{i}$, thus $L_{d+1}(w) > L_{d+1}(v)$, in contradiction to $L_{d+1}(v)$ being a maximum in $\Gamma^{t}$. In the other case, where $v$ adds itself, it follows that $\sigma_{v}$ can't be decomposed into pairs of unsatisfied checks; namely, $|\sigma_{v}|$ is odd. We show by induction that impossible,namely that $|\sigma_{v}|$ is always even. The induction is over the size of the plaquettes subset that induce the boundary $\sigma$.
  \begin{enumerate}
    \item Base. Consider a boundary that induced by a single plaquette, in that case it obvious that  $|\sigma_{v}|$ is either zero (where $v$ is not belong to the plaquette) or $2$. 
    \item Assume for any boundary that induced by at most $k$ plaquettes, and consider a boundary $\sigma$ which is induced by $k+1$ plaquettes, name this subset $F$ and observes that $F$ can be decomposed to a sum of two disjoint subsets $A$ and $B$, each with less than $k+1$ plaquettes, Now: 
      \begin{equation*}
        \begin{split}
          \sigma_{v} &= \left(\partial A \right)_{v} \cup \left(\partial B \right)_{v} \\
          \Rightarrow |\sigma_{v}| &=   | \left(\partial A \right)_{v} | + | \left(\partial B \right)_{v} | - 2 |\left(\partial A \right)_{v} \cap \left(\partial B \right)_{v}|  = \text{even} 
        \end{split}
      \end{equation*}
      Where we used the induction assumption, which tells that $| \left(\partial A \right)_{v} |$ and $| \left(\partial B \right)_{v} |$ are even numbers.
  \end{enumerate}


\end{proof}

\begin{claim}
  \label{claim:toomc}
  Let $x \in [d]$ and let $v \in \Gamma^{t}$ such that $L_{x}(v)$ is a (local) maxima in $\Gamma^{t}$ then for any $u$ which is added by $v$ we have $L_{x}(u) \le L_{x}(v)$. 
\end{claim}

\begin{proof}
  Since $L_{x}(v)$ is maximal, $v$ doesn't see edges that goes from it at the positive $x$-direction, otherwise denote it by $e$ and denote by $w$ the second vertex at the end of $e$, $w$ has an $x$-coordinate which is greater than $v$'s $x$-coordinate by $1$ and in addition $w \in \Gamma^{t}$ (since it lays on the support of $e$). Therefore $L_{x}(w) > L_{x}(v)$ in contradiction to $L_{x}(v)$ be maximal in $\Gamma^{t}$. 
Hence, any plaquette that is being flipped by $v$ lies on edges associated with $1_{j}$ such that $j \neq x$. Thus, any vertex $u$ that is added by $v$ has the form $v + \sum_{j \in [d] \setminus \{x\}} \alpha_{j}1_{j}$, where $\alpha_{j} \in \{0,1\}$ and $\sum \alpha_j \le 2$. So:
  \begin{equation*}
    \begin{split}
      L_{x}(u) = \braket{1_{x}, v + \sum_{j \in [d]/x} \alpha_{j}1_{j}} = \braket{1_{x},v} = L_{x}(v) 
    \end{split}
  \end{equation*}
\end{proof}

\begin{claim}
Let $\Gamma^{t}$ be the vertices in the support of the domain wall $\sigma^{t}$. Denote $v_i = \arg \max_{v \in \Gamma^{t}} L_{i}(v)$. Then for any $i \in [d]$, one can find $u \in \Gamma^{t-1}$ such that $u$ adds $v_i$ and $L_{i}(u) \ge L_{i}(v_{i})$. In addition, one can find $u_{d+1} \in \Gamma^{t-1}$ such that $u_{d+1}$ adds $v_{d+1}$ and $L_{d+1}(u_{d+1}) = L_{d+1}(v_{d+1}) + 1$. 
\end{claim}
\begin{proof}
Just take $u_{i}$ to be any vertex that adds $v_{i}$. By claims \cref{claim:toombound}, \cref{claim:toomb}, and \cref{claim:toomc}, we get the claim.
\end{proof}

\ctt{$V(\phi_{v})$ was not defined. $v \le w$ also not defined.} 






\newpage
\section{Investigation}

\ctt{To do: understands how the investigation should look like. Plot an example to such tree.}
The model goes as follow, at each even iteration we toss a noise, then in each odd iteration we perform a single SWEEP rule iteration. That allows to track over the history of the errors.  

We say that a check $e \in $ Error, if there is a face $f$ that adjoin to $e$ and belongs to the Error. 


\begin{definition}[Investigation]
  For any unsatisfied check $e$ at time $t$, we define $V$ (the set of checks which participated in 'misleading' of $e$), and two sets of edges on $V$, Arrows and Forks via the following algorithm: 


  

\end{definition}
\tikzset{%
  every neuron/.style={
    circle,
    draw,
    %fill=black,
    radius=0.1mm
  },
  neuron missing/.style={
    draw=none,
    scale=2,
    text height=0.25cm,
    execute at begin node=\color{black}$\vdots$
  },
}

  \begin{figure}[h]
    \centering
  \begin{algorithm}[H]
    let $V = \{e\}$, Arrows $= \emptyset$, Forks $= \emptyset$\\
    let $Q \leftarrow $ queue $\{ e \}$\\
    \While{ $Q$ is not empty  }{
      $e^{\prime} \leftarrow $ dequeue $Q$ \\
      \If { $e^{\prime} \notin $ Error }{
        $e_{1},..,e_{l} \leftarrow $ Excuse( $e^{\prime}$ ) \\
        Insert $\{e_{i}, e^{\prime} \}$ to Arrows\\
        Insert $\{e_{i}, e_{j} \}$ to Forks
      }
    }
    %\caption{Investigation}
  \end{algorithm}
\end{figure}
\begin{figure}[h]
      \begin{tikzpicture}[scale=1]%[ultra thick]
  \draw [dashed, draw=gray] (-1.8,-1.5) -- (7,-1.5);
  \draw [dashed, draw=gray] (-1.8,-3) -- (7,-3);
  \draw [dashed, draw=gray] (-1.8,-4.5) -- (7,-4.5);
  \draw [dashed, draw=gray] (-1.8,-6) -- (7,-6);
  \node (SWEEP1) at (-3, -1.5) {Sweep iteration: };
  \node (NOISE1) at (-3, -3) {Noise iteration: };
  \node (SWEEP2) at (-3, -4.5) {Sweep iteration: };
  \node (NOISE2) at (-3, -6) {Noise iteration: };
  \node (root) at (3.9, -0) { $\leftarrow$ root };
  \node (root) at (6.9, -3) { $\leftarrow$ leaf };
  \node [every  neuron ] (v-1) at ( 3 ,-0) { } ;
  \node [every  neuron ] (v-2) at ( 1 ,-1.5) { } ;
  \node [every  neuron ] (v-3) at ( 5 ,-1.5) { } ;
  \node [every  neuron ] (v-4) at ( 0 ,-3) { } ;
  \node [every  neuron ] (v-5) at ( 2 ,-3) { } ;
  \node [every  neuron ] (v-6) at ( 4 ,-3) { } ;
  \node [every  neuron ] (v-7) at ( 6 ,-3) { } ;
  \node [every  neuron ] (v-8) at ( 0.5 ,-4.5) { } ;
  \node [every  neuron ] (v-9) at ( 1.5 ,-4.5) { } ;
  \node [every  neuron ] (v-10) at ( 2.5 ,-4.5) { } ;
  \node [every  neuron ] (v-11) at ( 1.25 ,-6) { } ;
  \node [every  neuron ] (v-12) at ( 1.75 ,-6) { } ;
%  \node [every  neuron ] (v-3) at ( 6 ,-3) { } ;
%\node (v-4) at ( 0.0 ,-6) { $ \vdots $  };
%
%\node [every  neuron ] (v-6) at ( 5 ,-6) { $l$  };
%\node [every  neuron ] (v-7) at ( 7 ,-6) { $r$  };
%\node  (v-8) at ( 5 ,-7) { $\vdots$  };
%\node  (v-9) at ( 7 ,-7) { $\vdots$  };
\draw [->, draw = blue, thick] (v-1) -- (v-2);
\draw [->] (v-1) -- (v-3);
\draw [->] (v-2) -- (v-4);
\draw [->, draw = blue, thick] (v-2) -- (v-5);
\draw [->] (v-3) -- (v-6);
\draw [->] (v-3) -- (v-7);
\draw [->] (v-4) -- (v-8);
\draw [->, draw = blue, thick] (v-5) -- (v-9);
\draw [->] (v-5) -- (v-10);
\draw [->, draw = blue, thick] (v-9) -- (v-11);
\draw [->] (v-9) -- (v-12);
%%  node[right=6pt] {$y$} at
%\draw[decoration={brace,raise=6pt},decorate, thick]
%(8,-1.5) -- node[right=10pt, align=left] {  $n^{\prime}$-size binary tree, \\It's guaranteed that any node, \\beside the root, \\satisfies the heap inequality. } (8, -7.5);
%
%\draw[draw=gray, dashed] (4.5,-7.5) rectangle ++(3.5,6);
\end{tikzpicture} 
    \caption{blabla }
    \label{fig:investigation}
  \end{figure}


  \newpage 

  \section{Space-Time Graph}


  %\newcommand{\History}[1]{\mathbf{History}(#1)}
\newcommand{\History}[1]{H_{#1}}
  %\newcommand{\Time}[1]{\mathbf{Time}(#1)}
  \newcommand{\Time}[1]{T(#1)}
  \newcommand{\Excuse}[1]{\mathbf{Excuse}(#1)}
  \newcommand{\Excusei}[1]{\mathbf{Excuse}_{i}(#1)}
  \newcommand{\Size}[1]{\mathbf{Size}(#1)}
  \newcommand{\Span}[1]{\mathbf{Span}(#1)}
  \newcommand{\pre}[1]{\text{pre}(#1)}
  \newcommand{\prei}[1]{\text{pre}_{i}(#1)}

  \begin{definition}
    Consider a graph $G = (V, A, F)$, where $V$ is a set of vertices, and $A$, $F$ are sets of undirected edges. For $v \in V$, denote by $\pre{v} = \{ u \in V : \{u,v\} \in A \}$, we extend the notion for subsets of vertices $X \subset V$ by $\pre{X} = \bigcup_{v \in X} \pre{v}$. Let $ T : V \rightarrow \mathbb{N}$, We say that $(G,T)$ is a time graph iff:
\begin{enumerate}
  \item $\{x,y\} \in A \Rightarrow \Time{y} = \Time{x} \pm 1$  
  \item For $x,y \in V $  $\{x,y\} \in F $ iff there exists $z \in V $ such both $\{x,z\},\{y,z\} \in A$. 
\end{enumerate} We will call to $T$ time-function, to $A$ arrows, and to $F$ forks. Observes that from the second requirement it follows that forks can connect only vertices that have the same time value (set by $T$). 
  \end{definition}
% that since $(V,A)$ is a DAG it defines a partial order on $V$, let us denote $u \le v$ for $u,v \in V$ if there is a directed path from $u$ to  
  \begin{definition}[History, slice.]
    For a time graph $(G,T)$ and a vertex $u \in V$, let $G_{u}$ be the subgraph of $(V,A)$ induced by $\{ v \in V : \Time{v} \le \Time{u} \}$. We will denote by $\History{u}$ the 'History of $u$', which is the set of vertices that are connected to $u$ in $G_{u}$. A slice is an equivalence class of the relation $u \equiv v$ iff $\History{u} = \History{v}$. Notice that the time function has to be constant on a slice, to see this consider vertices  $x,y$ with $T(x) > T(y)$, thus $x \notin G_{y}$ and therefore $x \in \History{x}/\History{y}$ So they are belong to different classes. Thus, we can extend the time function and the history to slices and write for a slice $K$: $\Time{K}$ and $\History{K}$.
  \end{definition}

  \begin{claim} 
    \label{cref:disj}
    Consider slices $K_{1}, K_{2}$ such that $\Time{K_1} = \Time{K_2}$, then either $K_{1}=K_{2}$ or $\History{K_1}, \History{K_2}$ are disjoint.
  \end{claim}
  \begin{proof}
Assume a non-empty intersection, so there exists $z \in \History{K_{1}}\cap \History{K_{2}}$ such that for any $x \in K_{1}$ and $y \in K_{2}$, there exist arrow-paths $z \rightarrow x$ and $z \rightarrow y$. Thus, for any $w \in \History{K_{1}}$, one can concatenate a path $w \rightarrow x \rightarrow z \rightarrow y$ and conclude that $y \in \History{K_{2}}$.
  \end{proof}

  \begin{definition}[The graph of slice]
    \label{def:gslice}
    Let $K$ be a slice. The graph of $K$, denoted by $G_{K} = (V_{K}, E_{K})$, is the graph whose vertices are slices $R \subset \History{K}$ with $\Time{R} = \Time{K} - 1$. Two vertices are connected by an edge if and only if there is a fork whose ends belong to the slices associated with them. Namely, $S, R \in V_{K}$ are connected in $G_{K}$ if and only if there is $\{s, r\} = f \in F$ such that $s \in S$ and $r \in R$.
  \end{definition}

  \begin{claim}
    \label{claim:connected}
    $G_{K}$ is connected. 
  \end{claim}

  \begin{proof}
    Let $R, S \in V_{K}$ and consider $r,s \in V$ such that $r \in R, s \in S$. Recall that $R,S \subset \History{K}$ and therefore $r,s \in \History{K}$, Thus, by definition of the 'History' there exists a path, passing trough arrows only, from $r$ to $s$ in $\History{K}$. Consider such a path that is minimal in the number of points $x$ belong to it, with $\Time{x} = \Time{K}$. By induction on the number $k$ of such points we prove that $R$ and $S$ are connected in $G_{K}$. 

    \begin{enumerate}
      \item Base. $k=0$, In this case, the path from $r$ to $s$ lies within $G_{r} (= G_{s})$. Hence $\History{r} = \History{s}$, So $R = S$. 
      \item Induction step. There exists $y$ on the path from $r$ to $s$ such that $\Time{y} = \Time{K}$. Let $x$ be the point which precedes $y$ on the path, and $z$ the point that follows $y$. Since the values of $T$ at the two ends of an arrow differ by $1$, and since $y$ gets the maximal $T$ value in $\History{K}$ it follows that: 
        \begin{enumerate}
          \item $\{x,z\} \subset \pre{y} \Rightarrow \{x,z\} \in F$. 
          \item The slices of $x$ and $z$, say $K_{x}$ and $K_{z}$ has time value $\Time{K_{x}} = \Time{K_{z}} = \Time{K} -1$, Namely they are both members of $V_{K}$. 
        \end{enumerate}
        Since the path connecting $r,x$ in $\History{K}$ has $k-1$ vertices with $\Time{\cdot} = \Time{K}$, then by the induction hypothesis, $R$ and $K_{x}$ are connected in $G_{K}$, and by similar argument so are $K_{z}$ and $S$. On the other hand, $ \{x,z\} \Rightarrow \{K_{x},K_{z}\} \in E_{K}$. Thus, $R$ and $S$ are connected in $G_{K}$.
    \end{enumerate}
  \end{proof}

  \begin{definition}
Let $f : G \hookrightarrow \mathbb{R}^{d}$ be an embedding that maps each element of $V \cup A \cup F$ to a point in $\mathbb{R}^{d}$. We say that $\left( G, \mathbb{R}^{d} \right) $ is a space-time graph iff: 
\begin{enumerate}
  \item \item The point set by $f$ for an edge is the mean of its endpoints' images; that is, for $e = \{x,y\} \in A \cup F$, we have $f(e) = \frac{1}{2}\left(f(x) + f(y)\right)$.
\end{enumerate}
  \end{definition}

  \begin{definition}
    Define $\prei{v} = \arg\max_{u \in \pre{v}}L_{i}(f(u))$
  \end{definition}


  \begin{claim}
    Let $\mathbf{S} = \{ S_{1}, S_{2} , .. , S_{k} \}$ where $S_{i} \subset \mathbb{R}^{d}$, introduce an edge between $S_{i}$ and $S_{j}$ iff $S_{i} \cap S_{j} \neq \emptyset$. Assume that $\mathbf{S}$ is connected. Then $\Size{\cup^{k}_{i=1} S_{i}} \le \sum^{k}_{i=1}{\Size{S_{i}}}$. 
  \end{claim}
  \begin{proof}
    It suffices to prove that if $R_{1} \cap R_{2} \neq \emptyset$, then $\Size{R_{1} \cup R_{2}} \le \Size{R_{1}} + \Size{R_{2}}$. Let $a_{i,j} = \max_{v \in R_{j}}L_{i}(v)$. Then for any $w \in R_{1}\cap R_{2}$ we have:  
    \begin{equation*}
      \begin{split}
        \Size{R_{1} \cup R_{2}} &= \sum_{i}^{d+1}{\max{ a_{i,1},a_{i,2} } } =  \sum_{i}^{d+1}{a_{i,1} + a_{i,2} - \min{ a_{i,1},a_{i,2} } } \\
        & \le   \sum_{i}^{d+1}{a_{i,1} + a_{i,2} - L_{i}(w) } = \Size{R_{1}} + \Size{R_{2}} - \Size{w}  \\
        &  = \Size{R_{1}} + \Size{R_{2}} 
      \end{split}
    \end{equation*}
  \end{proof}

  \begin{definition}[Spanned Set]
    Consider an embedding $f : \star \hookrightarrow \mathbb{R}^{d}$, a subset of $f$'s domain $S \subset \star$, and $d+1$ points $x_{1}, \ldots, x_{d+1}$. We say that $\braket{S, x_{1}, \ldots, x_{d+1}}$ is a spanned set of $S$ if for any $i \in [d+1]$ and $s \in S$, it holds that $L(f(s)) \le L_{i}(x_{i})$ and in addition there are $v_{1},..v_{d+1} \in V$, not necessary different, that achieve the equalities $L_{i}(x_{i}) = L_{i}(f(x_{i}))$.  We name $x_{1}, \ldots, x_{d+1}$ the poles of $S$. Furthermore, we extend the notation to a spanned slice when $S$ is a slice of some time-graph. Notice that saying $\braket{S, x_{1}, \ldots, x_{d+1}}$ is a spanned set means that $\Size{S} = \Size{ \{x_{1}, \ldots, x_{d+1}\}}$.
  \end{definition}
  Observe that in the case where the subset $S$ is a slice. Each of these poles can be associated with a vertex of $G$ that gives the equality. If there are multiple vertices whose images by $f$ give equality, associate the point with one of them arbitrarily. We will use the notion of applying functions originally defined over vertices to the poles, referring to the application over the vertices associated with them. For example $\pre{x_{i}} = \pre{v}$ for the vertex $v \in S$ which satisfies $L_{i}(f(v)) = L_{i}(x_i)$ and therefore is associated with the pole $x_{i}$. 
 Another example is referring to $x_{i}$ as a vertex, so when saying 'For $x_{i} \in V_{k}$' or 'For $\{x_{i},u\} \in F$', we refer to the associated vertex or the edge connecting it to $u$.

  \begin{claim}
    \label{claim:prevslices}
    Consider a time graph $(G,T)$, an embedding $f : G \rightarrow \mathbb{R}^{d}$, such that.. , Let $K$ be a slice in $G$, and let $\hat{K} = \braket{K, x_{1}, .. x_{d+1}}$ be a spanned slice of $K$ such that $K \neq \History{K}$. Then for some integer $k$ there exist spanned slices $\hat{K}_{0} = \braket{K_{0}, \cdot}, ..,\hat{K}_{k}=\braket{K_{k}, \cdot }$ and Forks $F_{1},..,F_{k}$ such that:
    \begin{enumerate}
      \item For $i \in [d+1]$ $ \prei{x_{i}} $ belongs to the poles $\hat{K}_{0},..,\hat{K}_{k}$.  
      \item Introduce an edge between $\hat{K}_{i}$ and $\hat{K}_{j}$ if and only if one of the Forks $F_{1},..,F_{k}$ consists of a pole of $\hat{K}_{i}$ and a pole of $\hat{K}_{j}$. Then the graph formed from $\hat{K}_{0},..,\hat{K}_{k}$ is connected.  
      \item $\sum_{i=0}^{k}\Size{\hat{K}_{i}} +  \sum^{k}_{i=1}\Size{F_{i}} \ge \Size{\hat{K}} + 1 $
    \end{enumerate}
  \end{claim}
  \begin{proof}
    First Notice that $K$ doesn't contain leaves in $(V,A)$, since a leaf is connected only to itself via arrows, and therefore its 'slice' equals to its 'History'. Thus $\prei{x_{i}}$ is not empty for $i=1,..,d+1$. Next consider the graph $G_{K}= (V_{K},E_{K})$ from \cref{def:gslice}. Since $\{ x_{i}, \prei{x_{i}} \}$ is an arrow $\prei{x_{i}}$ belongs to a slice in $V_{K}$. for $i=1,..,d+1$ denote by $R_{i}$ the slice in $V_{K}$ that contains $\prei{x_i}$. 

    By \cref{claim:connected} $G_{K}$ is connected and therefore there exist a minimal collection $\{K_{0},..,K_{k}\}$ of slices form $V_{K}$ which contains $R_{1},R_{2},..R_{d+1}$, and which is connected in $G_{K}$. We pick a set of forks $\mathbf{F} = \{F_{1},..,F_{k} \}$ which realizes a spanning tree for this collection of slices. Later we will identify edges from this spanning tree with the forks from $\mathbf{F}$.  

    For $i=1,..,d+1$ we set $\prei{v_{i}}$ to be the $i$th pole of $R_{i}$, This assures (1). The set of remaining poles for $\hat{K}_0, ..,\hat{K}_{k}$ will be equal to $\cup^{k}_{i=k}F_{i}$. This will assure (ii), We will also select poles for $F_{1}, ..,F_{k}$ to form 'spanned forks' $\hat{F}_{1}, \cdots,\hat{F}_{k}$ in such way that:  
    \begin{equation*}
      \begin{split}
        \sum^{k}_{i=0}\Size{\hat{K}_{i}} + \sum^{k}_{i=1}\Size{\hat{F}_{i}} \ge \sum_{i=1}^{d+1}L_{i}\left( \prei{v_{i}} \right) \ge \Size{\hat{K}} + 1
      \end{split}
    \end{equation*}
    This will assure (3). 

    %Now we describe the selection of poles. Since we have to span..
    Let us denote by $J_{0},..,J_{2k}$ the enumerated union $K_{0},..K_{k},F_{1},..,F_{k}$. Observes that for any choice of $(d+1)(2k+1)$ elements $z_{0}^{1},z_{0}^{2}, z_{0}^{3},..,z_{0}^{d+1}..,z_{2k}^{d+1}$ in $\mathbb{R}^{d}$, such that $z_{j}^{i} \in J_{j}$ it holds that:
    \begin{equation}
      \label{equ:spanlow}
      \begin{split}
         \sum^{k}_{i=0}\Size{\hat{K}_{i}} + \sum^{k}_{i=1}\Size{\hat{F}_{i}}  \ge \sum_{j,i}L_{i}(z_{j}^{i})
      \end{split}
    \end{equation}

Later, we are going to take the points $\{z_{j}^{i}\}$ from the intersection of $J_{j}$'s. For convenience, let us assume that for the index subset $X \subset [2k]\cup\{0\}$, the intersection $\bigcap_{j \in X}J_{j}$ returns a single point. If there is more than one, then decide on the point in a way that all the chosen points simultaneously satisfy that for any index subsets $Y, X$, such that $X \cap Y$ and they both introduce a non-trivial intersection $\bigcap_{j \in Z} J_{j} : Z\in \{X,Y\}$, then:
    \begin{equation*}
      \begin{split}
        \bigcap_{j \in X} J_{j} = \bigcap_{j \in Y } J_{j} 
      \end{split}
    \end{equation*}

    Now consider a non-trivial maximal intersection $\bigcap_{j \in X} J_{j}$, the intersection is maximal in the sense that for any $j^{\prime} \notin X$ it holds that .$\bigcap_{j \in X\cup \{j^{\prime} \}} J_{j} = \emptyset$. We claim that for any $i$ and for any such $X$, there is $t \in X$ such that $J_{t}$ is the successor of $J_{j}$ on the path to $R_{i}$ for any $j \in X/\{t\}$. Assume not. Let $x, y \in X$, and denote the paths from $J_{x}, J_{y}$ to the $i$th pole by $\braket{J_{x}, J_{x_2}, \ldots, R_{i}}$, $\braket{J_{y}, J_{y_2}, \ldots, R_{i}}$, such that $J_{y} \neq J_{x_{2}}$. If $y = x_{2}$, $y_{2} = x$, or $x_{2} = y_{2} \in X$, then pick other $x, y$ (if there is no such, we get an immediate contradiction). In that case, $\braket{J_{x}, J_{y}, J_{y_{2}}, \ldots, R_{i}}$ is a path from $J_{x}$ to $R_{i}$ which is different from $\braket{J_{x}, J_{x_{2}}, \ldots, R_{i}}$. Therefore, there are at least two paths from $J_{x}$ to the $i$th pole, namely, there is a cycle in contradiction to the minimality of $K_{0}, \ldots, K_{k}$.


We will choose the $z_{j}^{i}$ by the following process. Pick a $z_{j}^{i}$ that has not been set yet. If $J_{j} = R_{i}$, then set $z_{j}^{i} \leftarrow \prei{x_{i}}$ - we call this a type-1 assignment. Otherwise, consider the path from $J_{j}$ to $R_{i}$ (by connectivity, it has to be such a one, and by minimality, there is exactly one). Let $J_{t}$ be the successor on the path, then pick $z_{j}^{i} \in J_{j} \cap J_{t}$ - similarly, we call this assignment a type-2 assignment. Since any type-2 assignment is associated with a non-trivial intersection, and any non-trivial intersection induces a type-2 assignment for all $i$'s (since for all $i$'s, one of the $J_{j}$ on its support is a successor of the rest on their path to the $i$th pole), we have that:
    \begin{equation*}
      \begin{split}
        \sum_{j,i}L_{i}(z_{j}^{i}) &= \sum_{j,i, z_{j}^{i} \in \text{type-1}}L_{i}(z_{j}^{i}) + \sum_{j,i, z_{j}^{i} \in \text{type-2}}L_{i}(z_{j}^{i}) \\
        &= \sum_{i}^{d+1}L_{i}\left( \prei{x_{i}} \right) + \sum_{X : \bigcap_{j\in X}J_{j} \neq \emptyset }\left(|X|-1\right) \sum_{i}^{d+1} L_{i}\left(\bigcap_{j\in X}J_{j} \right) \\ 
        &=\sum_{i}^{d+1}L_{i}\left( \prei{x_{i}} \right) 
      \end{split}
    \end{equation*}
    Plugging it into \cref{equ:spanlow} gives the desired.
  \end{proof}

  \section{Explantation of a Spanned Slice}

  \ctt{Here we follow the original proof, but change the triminalogy, $m$ will be the number of leaves in the explanation, then in the end we conclude that the number of faults is at least $m/\Delta$. So $|R| \le f(\frac{m}{\Delta})$. }

  \begin{definition}
    Consider a time graph $(G,T)$, an embedding $f : G \rightarrow \mathbb{R}^{d}$, such that.. Let $\beta = \frac{d+1}{\xi}$ and $\alpha = \beta \Size{\text{fork}}$. Given sets $W$ of points, $R$ of arrows and $F$ of forks, we define $U$ as the set of vertices of the graph induced by the edges of $R \cup F$. The sets $W,R$ and $F$ form an explanation of a spanned slice $\hat{K} = \braket{ K, v_{1}, .., v_{d+1}}$ if and only if: 
    \begin{enumerate}
      \item $W \cup \{v_{1} ,.., v_{d+1}\} \subset U \subset \History{K}$ and the graph $(U, R\cup F)$ is connected. 
      \item All elements of $W$ are leaves. 
      \item For $m = |W|$ and $s=\Size{K}$ we have $|R| \le \alpha (m-1) - s $ and $|F| < m -1 $. 
    \end{enumerate}
  \end{definition}

  \begin{claim}
    \label{claim:edgesin}
    Every spanned slice $K = \braket{K,v_{1},..,v_{d+1}}$ has an explanation.
  \end{claim}

  \begin{proof}
    Let $h = \Time{K} - \min_{u \in \History{K}}\Time{u}$. The proof is by induction on $h$. 
    \begin{enumerate}
      \item Base: $h=0$, namely $T$ is constant on $\History{K}$, so no arrows connect points of $\History{K}$. Thus, $\History{K}$, as well as $\mathbf{K}$, consists only of leaves. In that case, $U = W = \{u\}$, $m=1$, $s=0$, and $|R|, |F| = 0$ satisfy the requirement.
      \item Induction Step: $h \neq 0$ implies $K \neq \History{K}$. Thus, by \cref{claim:prevslices}, we know that for some $k$ there exist spanned slices $\hat{K}_{0}, .., \hat{K}_{k}$ and forks $F_{1},..,F_{k}$ that satisfy \cref{claim:prevslices}. 

        Consider $i \in 0,..,k$, denote by $s_{i} = \Size{\hat{K}_{i}}$. By the inductive hypothesis and since $\Time{K_{i}} = \Time{K} - 1$, we know that $\hat{K}_{i}$ has an explanation formed by a set of leaves $\mathbf{W}_{i}$, a set of arrows $\mathbf{R}_{i}$ and a set of forks $\mathbf{F}_{i}$. Let $m_{i} =|\mathbf{W}_{i}|$, So the sets $R_{i}$ and $F_{i}$ have at most $\alpha m_{i} - s_{i}$ and $m_{i}-1$ leaves. We define:
        \begin{enumerate}
          \item $\mathbf{W} = \cup_{i=0}^{k} \mathbf{W}_{i}$, Notice that $\mathbf{W}_{i} \subset K_{i}$ and that $\Time{K_{i}} = \Time{K_{j}}$ for all $i,j$, thus by \cref{cref:disj} $\mathbf{W}$ is a union of disjoint set, Hence $W$ contains  $m = \sum_{i=0}^{k}m_{i}$ leaves. 
          \item $\mathbf{F} = \{ F_{1},..,F_{k} \} \cup_{i = 0}^{k}\mathbf{F}_{i}$ with at most $ k + \sum_{i=0}^{k}{m_{i} -1 } = m- 1$ elements. 
          \item $\mathbf{R} = \{ \{v_{i}, \prei{v_{i}} \} \} \cup_{i=0}^{k}{ \mathbf{R}_{i} }$ with at most 
            \begin{equation*}
              \begin{split}
                & d+1 + \sum^{k}_{i=0}{\alpha (m_{i}-1)  - \beta s_{i} } \\ 
                \le & d+1 + \alpha m - \alpha(k+1) - \beta\left(s + \xi - k \cdot \Size{\text{fork}}  \right) \\
                = & \alpha \left(m - 1\right) - \beta s + \left(\alpha + d+1 - (k+1) \alpha - \beta \xi + \beta k \cdot \Size{\text{fork}} \right)
              \end{split}
            \end{equation*}
            So its enough to show that for $k\ge 0$ the term in the closure is negative, We do that by showing that the slop is negative, and then the value of the term at zero is negative: 
            \begin{equation*}
              \begin{split}
                  - \alpha  +  \beta \Size{\text{fork}} \le 0 & \Rightarrow   \Size{\text{fork}} \le \frac{\alpha}{\beta} \\ 
                 d + 1  -\beta \xi \le 0 & \Rightarrow \frac{d+1}{\beta} \le \xi
              \end{split}
            \end{equation*}
        \end{enumerate}
        And those inequalities hold for $\beta = \frac{d+1}{\xi}$ and $\alpha = \beta \Size{\text{fork}}$. Finally, by \cref{claim:prevslices}, the graphs induced by $\mathbf{R}_{i} \cup \mathbf{F}_{i}$ are connected, thus the graph induced by $\mathbf{R}\cup \mathbf{F}$ is also connected. Therefore, $\mathbf{W}, \mathbf{R}, \mathbf{F}$ form an explanation of $K$. 
    \end{enumerate}

  \end{proof}

  \section{Counting Subtrees.} 

  \begin{claim}
    Let $G = \left( V, E \right)$ be a $\Delta + 1$-regular graph, and let $k$ be an integer less than $|E|$. Fix a vertex $r \in V$. The number of subtrees rooted at $r$ is at most $\alpha^{k}$.
  \end{claim}


  \begin{proof}
    Denote by $T_{\Delta}$ and $T_{2}$ the infinity $\Delta$ and binary tress. There is an injection between the subtrees of $G$, rooted at $v$, with at most $k$ edges, to the subtrees of $T_{\Delta}$ rooted at $v$, with at most $k$ edges. Moreover, there is an injection from the subtrees of $T_{\Delta}$ rooted at $v$, with at most $k$ edges to the subtrees of $T_{2}$, rooted at $v$, with at most $k \log \Delta$ edges. 

    \ctt{In the second map, we think on replacing each of the vertex with $\Delta-1$-leaves binary tree, each leaf is associated with a outgoing edge.  }. 

    Thus, it's enough to bound the number of of subtrees in $T_{2}$ rooted at $v$, with at most $ k \log \Delta $ edges, that number is less than the number of binary tress with $k \log \Delta + 1$ leaves. For exact leaves number we get the $k \log \Delta$ Catalan number, which its limit is:   
    \begin{equation*}
      \begin{split}
          \sim \frac{4^{k \log \Delta}}{\left( k \log \Delta \right)^{\frac{3}{2}} \sqrt{\pi} } \le \frac{\Delta^{2k}}{\left( k \log \Delta \right)^{\frac{3}{2}} \sqrt{\pi} } 
      \end{split}
    \end{equation*}
    Therefore we can bound by:
    \begin{equation*}
      \begin{split}
        \sum_{j=1}^{k} \frac{\Delta^{2j}}{\left( j \log \Delta \right)^{\frac{3}{2}} \sqrt{\pi} }  \le \frac{\Delta^{2k}}{\sqrt{\pi}\log^{\frac{3}{2}} \Delta}\sum_{j=1}^{k} \frac{1}{ j^{\frac{3}{2}} }  \le \zeta (\frac{3}{2}) \cdot \frac{\Delta^{2k}}{\sqrt{\pi}\log^{\frac{3}{2}} \Delta}
      \end{split}
    \end{equation*}

  \end{proof}
  Now, from here we get an upper bound on the number of subgraphs that connected $l$ vertices at the top level. We bound it from above by counting combination of rooted subtrees, such the vertices are their root and the overall edges number is summed up to $k$. Thus: 
  \begin{equation*}
    \begin{split}
      \le \zeta (\frac{3}{2}) { k - 1 \choose l - 1 } \frac{\Delta^{2k}}{\sqrt{\pi}\log^{\frac{3}{2}} \Delta}
    \end{split}
  \end{equation*}
  \section{Tree Separator Lemma}
 For a tree $T = (V, E)$ and a vertex $v \in V$, we call the subtree obtained by taking the descendants of $v$ the subtree rooted at $v$.


  \begin{claim}
    Let $T = (V,E)$ be a tree with $m > 3$ leaves and $\tau$ edges, then it has a subtree with $m^{\prime} \in ( \frac{1}{3}m, \frac{2}{3}m)$ leaves and at most $ \frac{m^{\prime}}{m} \tau$ edges. 
  \end{claim}
  \begin{proof}
Order the vertices according to their heights. Denote by $v \in V$ the lowest vertex for which the subtree rooted at $v$ has at least $\frac{1}{3}m$ leaves. Now, denote by $T_{1}$ the subtree obtained through the following iterative process over $v$'s children:
\begin{enumerate}
  \item Initialize $T_{1}$ as the subtree rooted at $v$.
  \item For a child $u$ of $v$:
    \begin{enumerate}
      \item Check if erasing from $T_{1}$ the subtree rooted at $u$ doesn't decrease the number of leaves below $\frac{1}{3}m$. If so, then we update $T_{1}$ to be the result of the erasure.
    \end{enumerate}
\end{enumerate}
Clearly, the algorithm is defined such that $ T_{1} $ has to have at least $\frac{m}{3}$ leaves. Furthermore, since any child of $ v $ is a root of a subtree with fewer than $\frac{m}{3}$ leaves (otherwise we get a contradiction to the minimality of $ v $'s height), we have that if $ T_{1} $ would have more than $\frac{2}{3}m$ leaves, then the subtraction of any of its children would yield a tree with at least $\frac{2}{3}m - \frac{1}{3}m = \frac{1}{3}m$ leaves. Namely, $ v $ has in $ T_{1} $ a child $ u $ such that the subtraction of the subtree rooted at $ u $ from $ T_{1} $ results in a subtree with more than $\frac{1}{3}m$ leaves. But if indeed there were such a child, then the algorithm would erase it, so there is not. 


Now let $T_{2} = T/T_{1} \cup {v}$, namly the tree induced by the subtraction of $T_{1}$'s edges from $T$. Observes that since the summation of leaves in $T_{1}$ and $T_{2}$ is the leaves in $T$, and $T_{1}$ has no more than $\frac{2}{3}m$ leaves, and no less than $\frac{1}{3}$ leaves, it holds that the number of leaves in $T_{2}$ is also in the range $(\frac{1}{3}m, \frac{2}{3}m)$. We claim that at least one of the  subtrees has fewer than $\frac{m^{\prime}}{m} \tau$ edges. 

To see this, denote by $m_{1},m_{2}$ and by $ \tau_{1}, \tau_{2} $ the leaves and the edges in $T_{1},T_{2}$ respectively. Now:
\begin{equation*}
  \begin{split}
    \frac{\tau}{m} &= \frac{\tau_{1} + \tau_{2} }{m_{1} + m_{2}} =  \frac{m_{1} }{m_{1} + m_{2}} \frac{\tau_{1} }{m_{1}}  + \frac{m_{2} }{m_{1} + m_{2}} \frac{\tau_{2} }{m_{2}} 
  \end{split}
\end{equation*}
Namely, $\frac{\tau}{m}$ is a weighted average of $\frac{\tau_{1}}{m_{1}}$ and $\frac{\tau_{2}}{m_{2}}$, and therefore it is greater than their minimum. Peak the subtree with the minimal quotient.
  \end{proof}
By repeating recursively on the above construction, we get the following corollary:
  \begin{corollary}
Let $T = (V,E)$ be a tree with $m$ leaves and $\tau$ edges. Then, for any $\alpha > 0$, it has a subtree with $m^{\prime} \in \left( \frac{1}{3}\alpha m, \frac{2}{3} \alpha m \right)$ leaves and at most $\frac{m^{\prime}}{m} \tau$ edges.
  \end{corollary}

\newpage 

\section{Tanner - History Connected Equivalency}
Imagine the following process, we apply $t$ noisy iterations of the SWEEP rule, and then a single ideal (without noise) iteration. Denote by $\xi$ a deviated configuration (can be either bits or checks), and by $\xi^{\prime}$ the result of applying an ideal SWEEP rule on $\xi$. Notice that if $\xi$ is connected in the Tanner graph then $\xi^{\prime}$ is connected in the History graph \ctt{Require proof, For the classical case enumerate all the options can be done by hand}. Thus:
\begin{equation*}
  \begin{split}
    & \prb{\xi \text{ connected in Tanner}}  \le \prb{\xi^{\prime} \text{ connected in Time } | \text{ no noise at the } t+1 \text{ iteration}  }\\
    & \le \sum^{\infty}_{m} | \{ \text{ explanation to } \xi^{\prime} \text{ over } m \text{ leaves restricted to no noise at the final iteration } \} | p^{\frac{m}{\Delta}} \\ 
    & \le \sum^{\infty}_{m} | \{ \text{ explanation to } \xi^{\prime} \text{ over } m \text{ leaves } \} | p^{\frac{m}{\Delta}} \\ 
    & \le \prb{\xi^{\prime} \text{ connected in Time } \textbf{ - Upper Bound }  } \le q^{\Span{\xi^{\prime}}} \le q^{\Span{\xi} - 1 }
  \end{split}
\end{equation*}

\subsection{Another Idea.}
Reconsider the construction of the explanation. We could add at the top an imaginary layer in which all the vertices at time $t$ are connected by arrows to all the vertices (at time $t+1$) that are adjacent to them in the Tanner graph. For the last layer, we might find that the span of a slice expands instead of shrinking. Namely, \cref{claim:prevslices} for the final slices would change to:

\begin{equation*}
  \begin{split}
\sum_{i=0}^{k}\Size{\hat{K}_{i}} +  \sum^{k}_{i=1}\Size{F_{i}} \ge \Size{\hat{K}} - \xi 
  \end{split}
\end{equation*}
Thus, following the computation at the induction stage in \cref{claim:edgesin}, the number of arrows is bounded by:

\begin{equation*}
  \begin{split}
    & \alpha \left(m - 1\right) - \beta s + d+1+ \alpha + \beta \xi \\
    & \alpha \left(m - 1\right) - \beta s + O(1) 
  \end{split}
\end{equation*}

\section{Intermediate Step Lemma}

\ctt{ The idea of this step is also to bound the case that all the bits are flipped at once, So checks are satisfied (and the argue above is not applied directly). }

\begin{definition}[Connected Cluster With Span $s$]
Let $G = (B,C,E)$ be a Tanner graph of a code, and let $f : G \rightarrow \mathbb{R}^{d+1}$ be an embedding of the graph into $\mathbb{R}^{d+1}$. For $s \in \mathbb{R}$, we say that $X \subset B$ is a connected cluster of $G$ with span $s$ regarding $f$ if $X$ is connected in $G$ (where two bits are connected if there is a check that connects both of them in $E$) and $f(X) \subset \mathbb{R}^{d+1}$ has $\Size{f(X)} \le s$. When it's clear from the context which $G$ and $f$ are, we will call $X$ in brief a connected cluster with span $s$.
\end{definition}

\begin{definition}
The model, computation, and noise are tossed, and then a correction is made.
\end{definition}

\begin{claim}  
  Let $\xi$ be the event in which, at the \textbf{beginning} of time $t$, the error contains a connected cluster with a span greater than $\frac{d}{4}$, and for $i \in [t]$, let $\sigma_{i}$ be the event in which, at the \textbf{end} of time $i$, there is a connected cluster with a span of at least $\sqrt{d}$ that belongs to the error. Then:
\begin{equation*}
  \begin{split}
    & \prb{\xi} \le t\prb{ \sigma_{1} } + p^{\frac{1}{8}\sqrt{d}}  
  \end{split}
\end{equation*}
\end{claim}
\begin{proof}
 By the law of total probability it hodls: 
\begin{equation*}
  \begin{split}
    \prb{\xi} & =  \prb{\xi \cap \bigcup^{t}_{i} \sigma_{i} } +  \prb{\xi \cap \bigcap^{t}_{i} \bar{\sigma}_{i} } 
  \end{split}
\end{equation*}
First, let us bound from above the probability of the right intersection, In that case, at the \textbf{end} of time $t-1$, the erorr consists of clusters each at span less than $\sqrt{d}$. Let $m$ be the number the clusters and denote them by $X_{1},..,X_{m}$. Now since the clusters are disjoint, the sum of their $\Size{X_{i}}$ is lower than the total number of the bits, namely: 
\begin{equation*}
  \begin{split}
    & \sum_{1}^{m}\Size{X_{i} } \le n \Rightarrow m \le \frac{n}{\sqrt{d}} \\
    & p \frac{n}{\sqrt{d}}  \le \sqrt{d}
  \end{split}
\end{equation*}

, Thus, .  So denote by $\tau$ the number of bits that require to be flipped in order to merge the flipped connected component to a one with a span greater than $d/4$, So $\tau$ has to be at least:   




\begin{equation*}
  \begin{split}
    \tau\left( \sqrt{d} + 1 \right) \ge \frac{1}{4} d \Rightarrow \tau \ge \frac{1}{8} \sqrt{d}
  \end{split}
\end{equation*}
Therefore: 
\begin{equation*}
  \begin{split}
    \prb{\xi \cap \cap^{t}_{i} \bar{\sigma}_{i} } & \le \sum_{\xi^{(t-1)}} \prb{\xi | \xi^{(t-1)}}\prb{\xi^{(t-1)} \cap  \cap^{t}_{i} \bar{\sigma}_{i} }  \\ 
    & \le \sum_{\xi^{(t-1)}} p^{\frac{1}{8} \sqrt{d}} \prb{\xi^{(t-1)} \cap  \cap^{t}_{i} \bar{\sigma}_{i} } \le p^{\frac{1}{8} \sqrt{d}} 
  \end{split}
\end{equation*}


\begin{equation*}
  \begin{split}
    \prb{\xi} & =  \prb{\xi \cap \cup^{t}_{i} \sigma_{i} } +  \prb{\xi \cap \cap^{t}_{i} \bar{\sigma}_{i} } \\
    & \le t \prb{ \sigma_{1} } + p^{\frac{1}{8} \sqrt{d}}  
  \end{split}
\end{equation*}

\end{proof}
Define the bits-cluster graphs $G=(V,E)$ such that the vertices are connected bit-clusters at different times $\{A_{i}^{t}\}$, and there is an edge between $A_{i}^{t}$ and $A_{j}^{t-1}$ only if $\Pi_{x} A_{i}^{t} \cap \Pi_{x} A_{j}^{t-1} \neq \emptyset$. Given a state at time $t-1$ such that no connected component in $G$ forms a closed non-trival circle, consider $\tilde{A}_{i}^{t}$ constructed as follows: perform the application of either noise or Toom's correction in an arbitrary order and stop right before $\tilde{A}_{i}^{t}$ forms a closed non-trivial circle.


%Define $\History{A_{i}^{t}}$ to be the subgraph of $G$ consists    









\section{Configuration up to $C_{z}^\perp$ }

\section{Drafts:}

    In addition since, in a tree, the number of leavs is at least greater than the maximal degree, then we have that each $J_{j}$ intersects with at most $d+1$ elements. 


    \begin{equation*}
      \begin{split}
       & L + \Delta_{\max} + 2(n - L -1) \le \sum_{v\in V}\text{deg}(v) = 2 (n-1)\\
       \Rightarrow & L \ge \Delta_{max}
      \end{split}
    \end{equation*}

\end{document}
