

%\newcommand*{\ACM}{}%

\ifdefined\ACM

%\documentclass[sigplan,screen]{acmart}
  \documentclass[manuscript,screen,review]{acmart}

\else
  \documentclass{article}
  \input{./usepackage}
  \addbibresource{./sample.bib} 

\fi

\begin{document}
\input{newcommands}
\title{State Synthesis Using PRS.} 
\author{David Ponarovsky}
\maketitle

\begin{abstract}
  We studies the complexity of synthesis quantum states using PRS, our reasch continues the work by \cite{searchtodecision}, \cite{rosenthal2023efficient}, \cite{rosenthal2021interactive}, \cite{metger2023stateqip}, \cite{delavenne2023quantum}.
\end{abstract}

\section{Pseudorandomness.}

\begin{definition}[Pseudorandom Quantum states] Let $\mathcal{H}$, $\mathcal{K}$ be the Hilbert and the key spaces, their diminsions depeand on a security paramter $n$. A state famliy $\{\ket{\psi_{k}}\}_{k\in \mathcal{K}}$ is a pseudiorandom, if the following hold:
  \begin{enumerate}
    \item Efficient generation. There is a polynomial-time quantum algorithm $G$ that generates state $\ket{\psi_{k}}$ on input $k$. 
    \item Pseudorandomness. Any polynomially many copies of $\ket{\phi_{k}}$ with the same random $k\in K$ is computationaly indistinguishable from the same number of copies of the Haar random state. 
  \end{enumerate}
\end{definition}

\begin{definition}[Pseudorandom Unitary Operators] A famliy of unitary operators $\{ U_{k} \in U(\mathcal{H}) \}_{k \in \mathcal{K}}$ is pseudorandom, if two conditions hold: 
  \begin{enumerate}
    \item Efficient computation. There is an efficient quantum algorithm $Q$, such that for all $k$ and any $\ket{\psi} \in \mathcal{H}$ $Q(k,\ket{\psi}) = U_{k}\ket{\psi}$. 
    \item Pseudorandomness. The uniform random distribution on $U_{k}$ is computationally in distinguishable from a Haar random unitary operator. 
  \end{enumerate} 
\end{definition}

\begin{definition}[The keeping setting] Let $R^{A}\otimes R^{B}$ be a general two registers domain. We define the \textbf{keeping setting} to let one construct quntum/classical circuits\footnote{On which we think as a canidate for PRS/PRF/PRG generator.} $G : R^{A}\otimes R^{B} \rightarrow R^{A} \otimes R^{B}$ such that it is gurnted that the register $R^{B}$ cann't be acssed after the computation.   
\end{definition}

\begin{claim}
  Let $G$ be a PRS generator, than under the the keeping setting one can assume that $G$ takes as input two register, the first contains $n$ ancille qubits initiliazied to $\ket{0}$ and the seconed contain a classic string initiliezed to be the seed $k$.  
\end{claim}

\begin{proof}
  Given a PRS $G : R^{A} \rightarrow R^{A}$ define $\tilde{G} : R^{A} \otimes R^{B} \rightarrow R^{A} \otimes R^{B}$ as follow, first $\tilde{G}$ copy the calsical state in $R^{B}$ (the $k$-length seed) to $R^{A}$ and then appaly $G$ on $R^{A}$, Hence on sampled seed $k \in R^{B}$ results the output $ \ket{\psi_{k}}\otimes\ket{k}$. Under the keeping setting any polynomial distingushier-canidate $D$ has acsses only for $\ket{\psi_{k}}$, So if $D$ distinguish between the distrubition generated by $\tilde{G}$ and the Haar measure then it also distingush between $G$ and Haar measure. 
\end{proof}

\begin{claim}
  Let $G : \ket{0}^{n} \otimes \mathbb{F}_{2}^{k} \rightarrow \{ \ket{\psi_{k}} \}_{k \in \mathcal{K}}$ be a PRS generator uses $n$- ancilles and $k$ classicl bits. Then for any unitery $V: \mathcal{H}_{n} \rightarrow \mathcal{H}_{n}$ it holds that $(V \otimes I^{\otimes k} ) G$ is also a PRS.
\end{claim}
\begin{proof}
   
\end{proof}

\begin{claim}[Levis Lemma for PRS]
  Let $f : \mathcal{H} \rightarrow R$ be a \textbf{BQP}-computible fuction on the $n$-qubits hilbert space, and let $g: (0,1) \rightarrow \mathbb{R} $ a function such that:     
  \begin{equation*}
    \begin{split}
      \prbm{f\left(\ket{\psi} \right) > \varepsilon}{ \ket{\psi} \sim U} < g(\varepsilon)
    \end{split}
  \end{equation*}
  Then, a similar inequality also holds for states sampled by the PRS, when the probability for the measure $f$-value grater than $\varepsilon$ is bounded by $g(2\varepsilon)$. Namely,  
\begin{equation*}
    \begin{split}
      \prbm{f\left(\ket{\psi} \right) > \varepsilon}{ \ket{\psi} \sim \ket{\psi_{k}} } < g(2\varepsilon)
    \end{split}
  \end{equation*}
  In praticular, Levi's lemma has a version that capture consetration of states sampled by PRS generator, states the following: Assume there exsists $K$ such that for any $\ket{\psi},\ket{\phi} \in \mathcal{S}(\mathbb{C}^{d})$ $|f(\ket{\psi}) - f(\ket{\phi})| < K | \ket{\psi} - \ket{\phi}|$. Then there exsists a universal constant $C > 0$ such: 
\begin{equation*}
    \begin{split}
      \prbm{ |f\left(\ket{\psi} \right) - \exppm{f\left(\ket{\phi}\right)}{\ket{\phi} \sim U}| > \varepsilon}{ \ket{\psi} \sim \ket{\psi_{k}} } < exp\left(-\frac{Cd}{K^{2}}  4\varepsilon^{2} \right)
    \end{split}
  \end{equation*}
\end{claim}

\begin{proof}
  
\end{proof}

\begin{claim}
  Probablisitc counting argument and $\varepsilon$-net over PRS. 
\end{claim}

\begin{claim}
  exsistness of poly($n$) gates $G_{1}, G_{2} ..$ such that, any $G_{i}$ has a polynomial depth, $\braket{p(G_{i})|\tau} > a$ and $\braket{\tau^{\perp}|p(G_{j})}\braket{p(G_{i})|\tau^{\perp}} < b$ for any $i\neq j$. 
\end{claim}
\begin{proof}
  
\end{proof}
\begin{claim}
 bla bla bla 
\end{claim}

\begin{definition}
  $\varepsilon$-bised test $2$-degree for testing RPU/RPS. $f(\braket{x_{j}|G_{s}|\theta}) = 1$ For example ask if $\braket{\psi_{j^{\prime}}\tau^{\perp}}\braket{\tau^{\perp}|\psi_{j}}$ what I can say about that quantenty as polynomail?. 
\end{definition}

\section{What We Need for Synthesis.}

\begin{definition}[Pseudorandom Unitary for Synthesis] A famliy of unitary operators $\{ U_{k} \in U(\mathcal{H}) \}_{k \in \mathcal{K}}$ is pseudorandom for synthesis, if two conditions hold: 
  \begin{enumerate}
    \item Efficient computation. There is an efficient quantum algorithm $Q$, such that for all $k$ and any $\ket{\psi} \in \mathcal{H}$ $Q(k,\ket{\psi}) = U_{k}\ket{\psi}$. 
    \item Pseudorandomness for synthesis. Given a state $\ket{\tau}$ and polynomial number of samples $U_{1},U_{2}..U_{m}$. Then: 
      \begin{enumerate}
        \item $|\braket{\Phi(\tau,U_{k})|U_{k}\tau}|^{2} > a$
        \item $|\braket{\Phi(\tau,U_{k})|U_{k}\tau^{\perp}}\braket{\tau^{\perp}U^{\dagger}_{j}|\Phi(\tau,U_{j})}|^{2} < b$
      \end{enumerate}
      The uniform random distribution on $U_{k}$ is computationally in distinguishable from a Haar random unitary operator. 
  \end{enumerate} 
\end{definition}

What about, Assume that $U$ is a quantum circuit such that $\log n$ qubits are intilaized to some to some input and instead anciles, we have noisy ancilea, can we show that circuit is equavilanent to $\log n $ circuit? That will enable us to prove a quantum version for Nisan Wigerzdon PRG (BPP = P). 

\paragraph{Problem.} Let $U$ be a quntum circuit which get $\log n$ stable qubits and poly$(n)$ more random qubits obtained from the random Haar masure, can we simulate the circuit in $\log n$ time?  

approximate the absoulte value function, For example, you can consider the binomial expansion of $\sqrt{1-y}$ on $[0,1]$. Namely, setting $y=1-x^2$, we have $|x|=\sqrt{1-y}=\sum_{m=0}^{\infty}\binom{1/2}{m}(-y)^m, \quad x\in[-1,1]$. That will allow me to bound the $k$-design. 

Denote by $q_{d}(x)$ the $d$-order approximation of $|x|$, Namely 
\begin{equation*}
  \begin{split}
q_{d}(x) &= \sum_{m=0}^{d}\binom{1/2}{m}(-1)^m\left( 1 - x^{2} \right)^{m}
%&= \sum_{m=0}^{d}\sum_{n=0}^{m}\binom{1/2}{n}(-1)^n\left( 1 - x^{2} \right)^{m}\\
  \end{split}
\end{equation*}
and as the series is convergres to any $x \in (-1,1)$ we have that $|x| = q_{d}(x) + O( \binom{1/2}{d}(1-x^{2})^d )$ which by the fact that $1- x^{2} \in (-1,1)$ can be simpllified to $|x| = q_{d}(x) + O( \binom{1/2}{d}) = q_{d}(x) + O( 1/d^{1 +1/2})$.
 
% \exppm{   }{ U \sim D }
\begin{equation*}
  \begin{split}
  \exppm{ ( \braket{\Phi(\tau,U)|\Rea U\tau} )^{2}  }{ U \sim D } & =  \exppm{  \frac{1}{2^{n/2}}\sum_{x}(-1)^{\sign(\Rea \braket{x|U\tau})}\Rea \braket{x|x}\braket{x|U\tau}  }{ U \sim D } \\
& = \exppm{ \frac{1}{2^{n/2}}\sum_{x}|\Rea \braket{x|U\tau}|  }{ U \sim D } \\
& = \exppm{ \sum_{x}|\Rea \braket{x|U\tau} / 2^{n/2}|  }{ U \sim D } \\
& \ge \exppm{  \sum_{x} q_{d}\left( \Ima \braket{x|U\tau}| / 2^{n/2}  \right) - \binom{1/2}{d} \left(\frac{ | \Ima \braket{x|U\tau}| }{2^{n/2}}\right)^{d}}{ U \sim D } \\
& \ge \exppm{  \sum_{x} q_{d}\left( \Ima \braket{x|U\tau}| / 2^{n/2}  \right) - \binom{1/2}{d} \left(\frac{ | \Ima \braket{x|U\tau}| }{2^{n/2}}\right)^{d}}{ U \sim Haar } - \delta \cdot 2 ^{n} \\
& \ge \exppm{  \sum_{x} |\Rea \braket{x|U\tau} / 2^{n/2}|  - \mathbf{2} \cdot  \binom{1/2}{d} \left(\frac{ | \Ima \braket{x|U\tau}| }{2^{n/2}}\right)^{d}}{ U \sim Haar } - \delta \cdot 2 ^{n} \\
& \sim \exppm{  \sum_{x} |\Rea \braket{x|U\tau} / 2^{n/2}|}{ U \sim Haar } - \delta \cdot 2 ^{n} 
  \end{split}
\end{equation*}
\begin{equation*}
  \begin{split}
    \exppm{  \braket{\Phi(\tau,U)|U \tau^{\perp}}\braket{\tau^{\perp}U_{2}^{\dagger}|\Phi(\tau,U_{2})}  }{ U,U_{2} \sim D } & = 
  \end{split}
\end{equation*}
\begin{claim}
  fix a state $\ket{\tau}$. Let $U$ be a unitary sampled from $k$-design  distribution $D$ and denote by $\ket{s}$ the vector which $U$ sends $\ket{\tau}$ to. Now, observes that $U$ can be written as $U = \ket{s}\bra{\tau} + V$ when $V$ act on space ortogonal to $ \ket{\tau}$ denote it by $\ket{\tau^{\perp}}$. Then the distribuation over $V$ is also a $k$-design relative to the Haar mesure on $\ket{\tau^{\perp}}$. 
\end{claim}
\begin{proof}
  
\end{proof}
\printbibliography
\end{document}





