

\section{Hadamard and S Gates}


\begin{claim}
For any generator subset $S^{\prime}$ of size $d^{\prime}$, denote by $x_{S^{\prime}}$ and $z_{S^{\prime}}$ the following assignments:
\begin{equation*}
  \begin{split}
    x_{S^{\prime}}  \colonequals \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S^{\prime}} \ \ \ z_{S^{\prime}} \colonequals \sum_{u \in \expval*{S/S^{\prime}} }\rotfv{u}{S^{\prime}} 
  \end{split}
\end{equation*}
Then $x_{S^{\prime}}$ and $z_{S^{\prime}}$ are binary representations of anticommuting logical codewords of the $(d,d^{\prime})$-Toric code. In particular, $x_{S^{\prime}} \in \mathcal{C}_{X}/\mathcal{C}_{Z}^{\perp}$, $z_{S^{\prime}} \in \mathcal{C}_{Z}/\mathcal{C}_{X}^{\perp}$, and $x_{S^{\prime}} z_{S^{\prime}} = 1$. In addition, let $X_{S^{\prime}}$ and $Z_{S^{\prime}}$ be the Pauli matrices obtained by multiplying each non-trivial coordinate of them by $X$ or $Z$, respectively.
\end{claim}
\begin{proof}
  By definition $x_{S^{\prime}}$ and $z_{S^{\prime}}$ are binary assignments on the $d^{\prime}$-dimensional faces. We start by showing that $x_{S^{\prime}} \in \mathcal{C}_{X}$ and $z_{S^{\prime}}\in \mathcal{C}_{Z}$: 
\begin{equation*}
  \begin{split}
    \partial^{-} \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S^{\prime}} &=  \sum_{u \in \expval*{S^{\prime}} } \sum_{g\in S^{\prime}} \rotfv{ u}{S^{\prime}/g} +  \rotfv{gu}{S^{\prime}/g} \\
     &=  \sum_{g\in S^{\prime}} \sum_{u \in \expval*{S^{\prime}} } \rotfv{ u}{S^{\prime}/g} +  \sum_{u \in \expval*{S^{\prime}} }\rotfv{gu}{S^{\prime}/g} \\
     &=  \sum_{g\in S^{\prime}} \sum_{u \in \expval*{S^{\prime}} } \rotfv{ u}{S^{\prime}/g} +  \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S^{\prime}/g} = 0 
  \end{split}
\end{equation*}
\begin{equation*}
  \begin{split}
    \partial^{+} \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S/S^{\prime}} &=  \sum_{u \in \expval*{S^{\prime}} } \sum_{g\in S^{\prime}} \rotfv{ u}{S/S^{\prime} \cup g} +  \rotfv{g^{-1} u}{S/S^{\prime} \cup g} \\
    &=  \sum_{g\in S^{\prime}} \sum_{u \in \expval*{S^{\prime}} } \rotfv{ u}{S/S^{\prime} \cup g} +  \sum_{u \in \expval*{S^{\prime}} }\rotfv{g^{-1}u}{S/S^{\prime}\cup g} \\
     &=  \sum_{g\in S^{\prime}} \sum_{u \in \expval*{S^{\prime}} } \rotfv{ u}{S/S^{\prime}\cup g} +  \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S/S^{\prime} \cup g} = 0 
  \end{split}
\end{equation*}
Thus $x_{S^{\prime}} \in \mathcal{C}_{X}$ and $z_{S^{\prime}}\in \mathcal{C}_{Z}$, now for showing that they are not binary representations of stabiliers, it's enough to show they admit no vanishing product.  
\begin{equation*}
  \begin{split}
    x_{S^{\prime}}z_{S^{\prime}} = \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S^{\prime}} \sum_{u \in \expval*{S/S^{\prime}} }\rotfv{u}{S^{\prime}} = \rotfv{e}{S^{\prime}} \rotfv{e}{S^{\prime}} = 1
  \end{split}
\end{equation*}
\end{proof}
\begin{definition}[The Transpose Map]
Let $d, d^{\prime}$ be integers, and let $\mathcal{G}$ be a $(d, d^{\prime})$-Toric complex generated by the generator set $S$. We define the \textit{transpose map} $\phi : \mathcal{F}^{d^{\prime}} \rightarrow \mathcal{F}^{d - d^{\prime}}$ by acting on the basis elements as follows:
  \begin{equation*}
    \begin{split}
    \phi(\rotfv{v}{S^{\prime}}) \rightarrow \rotfv{v^{-1}}{S/S^{\prime}} 
    \end{split}
  \end{equation*}
Notice that for $d^{\prime} = d - d^{\prime}$, the transpose map is a permutation over the bits.
\end{definition}

\begin{definition}[ Hadamard-Type Gate $H_{\phi}$]  
For $ d' = d - d' $, we define the logical Hadamard-type gate $ H_{\phi} \colon L \rightarrow L $ as follows, for any $ S' \subset S $, of size $ d' $:
  \begin{equation*}
    \begin{split}
      H_{\phi} ( X_{S^{\prime}} )  & \rightarrow Z_{S/S^{\prime}} \\
      H_{\phi} ( Z_{S^{\prime}} )  & \rightarrow X_{S/S^{\prime}} 
    \end{split}
  \end{equation*}
\end{definition}
\begin{claim}
The Hadamard-type gate $ H_{\phi} $ has a fold-transversal implementation by, first applying $H^{n}$ over all the physical qubits, and then permuting them by the transpose map $\phi$, namely $\hat{H}_{\phi} = \phi \circ H^{n}$.
\end{claim}
\begin{proof}
  Clearly, for any subset of generators $S^{\prime} \subset S$, the map $\phi$ sends $x_{S^{\prime}}$ to $z_{S/S^{\prime}}$:
  \begin{equation*}
    \begin{split}
      \phi(x_{S^{\prime}}) = \phi(  \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S^{\prime}}   ) =  \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S/S^{\prime}} = z_{S/S^{\prime}}
    \end{split}
  \end{equation*}
Moreover, $\phi$ sends binary representations of $Z$-stabilizers to binary representations of $X$-stabilizers, and vice versa. To see this, consider a $d^{\prime}+1$ dimensional face, and consider the image of the stabilizer it defines.
  \begin{equation*}
    \begin{split}
      \phi \left( \partial^{-}  \rotfv{v}{S^{\prime}} \right) &=  \phi\left( \sum_{g\in S^{\prime}} \rotfv{v}{S^{\prime}/g} +  \rotfv{gv}{S^{\prime}/g}  \right) \\
      & = \sum_{g\in S^{\prime}} \rotfv{v^{-1}}{(S/S^{\prime})\cup g} +  \rotfv{g^{-1}v^{-1}}{(S/S^{\prime})\cup g}  \\ 
      &= \partial^{+} \rotfv{v^{-1}}{S/S^{\prime}}
    \end{split}
  \end{equation*}
And since $\phi \circ \phi = I$, we also have that $\phi\left( \partial^{+} \rotfv{v^{-1}}{S/S^{\prime}} \right)$. Thus, $H^{\otimes n} \circ \phi$ sends $Z$-stabilizers to $X$-stabilizers and vice versa, thereby preserving the code space. Combining this with the above, $H^{\otimes n} \circ \phi$ realizes the logical form $H_{\phi}$ in the $(d,d/2)$-Toric code.
\end{proof}

\begin{corollary}
For the $(d,d/2)$-Toric code, consider the gate $CZ_{S^{\prime}\rightarrow S/S^{\prime}} \colon L^{\otimes 2} \rightarrow L^{\otimes 2}$, defined to act on two encoded registers by applying $Z_{S/S^{\prime}}$ on the second register, controlled by whether the logical $X_{S^{\prime}}$ is turned on in the first register. Then $CZ_{S^{\prime}\rightarrow S/S^{\prime}}$  has a fold-transversal realization. 
\end{corollary}
\begin{proof}
Consider the following circuit, 
\begin{enumerate}
  \item Apply $H^{n}$ on the second register.  
  \item For any bit $\rotfv{v}{S^{\prime}}$, apply $CX$ from $\rotfv{v}{S^{\prime}}$ in the first register into $\phi(\rotfv{v}{S^{\prime}})$ in the second register.
  \item Again apply $H^{n}$ on the second register.  
\end{enumerate}
\end{proof}

\begin{definition}[The $\varphi$ Rotation]
Consider a permutation from p he generator set to itself $\pi \colon S \rightarrow S$. The permutation $\pi$ induces a natural isomorphism by substituting generators of the product representation with their corresponding images according to $\pi$. We define the \textit{$\varphi_{\pi}$ rotation}, $\varphi_{\pi} : \mathcal{F}^{d^{\prime}} \rightarrow \mathcal{F}^{d^{\prime}}$, to act on the $d^{\prime}$-dimensional faces as follows:
  \begin{equation*}
    \begin{split}
      \varphi_{\pi} \left(  \rotfv{v}{S^{\prime}}  \right) \colonequals \rotfv{\pi(v)}{\pi(S^{\prime})}
    \end{split}
  \end{equation*}
\end{definition}
\begin{claim}
For $d^{\prime} = d - d^{\prime}$, fix a generator subset $S^{\prime}$ of size $d^{\prime}$, and consider a permutation $\pi : S \rightarrow S$ such that $\pi(S^{\prime}) \subseteq S \setminus S^{\prime}$. Then $\varphi_{\pi}$ satisfies the following:
  \begin{enumerate}
    \item $\varphi_{\pi}$ sends the binary representation of $X$-stabilizers to themselves, and similarly for the binary representations of the $Z$-stabilizers.
    \item $\varphi_{\pi}$ sends $x_{S^{\prime}}$ to $X_{S/S^{\prime}}$ and vice versa. 
  \end{enumerate}
\end{claim}

\begin{proof}
\begin{equation*}
  \begin{split}
    \varphi_{\pi}\left( x_{S}  \right) = \varphi_{\pi}\left( \sum_{u\in \expval*{S^{\prime}}}\rotfv{u}{S^{\prime}}  \right) =  \sum_{u\in \expval*{S/S^{\prime}}}\rotfv{u}{S/S^{\prime}} = x_{S/S^{\prime}}
  \end{split}
\end{equation*}
\begin{equation*}
  \begin{split}
      \varphi \left( \partial^{-}  \rotfv{v}{J} \right) &=  \varphi\left( \sum_{g\in J} \rotfv{v}{J/g} +  \rotfv{gv}{J/g}  \right) \\
      & = \sum_{g\in J} \rotfv{\varphi(v)}{ \varphi(J / g)} +  \rotfv{\varphi(g)\varphi(v)}{\varphi(J / g) }  \\ 
      & = \sum_{g\in \varphi(J)} \rotfv{\varphi(v)}{ \varphi(J)/g} +  \rotfv{g\varphi(v)}{\varphi(J)/g }  \\ 
      &= \partial^{-} \rotfv{\varphi(v)}{\varphi(J)}
  \end{split}
\end{equation*}

\begin{equation*}
  \begin{split}
    \varphi \left( \partial^{+}  \rotfv{v}{J} \right) &=  \varphi\left( \sum_{g\in S/J} \rotfv{v}{J \cup g} +  \rotfv{g^{-1}v}{J \cup g}  \right) \\
    & = \sum_{g\in J} \rotfv{\varphi(v)}{ \varphi(J \cup g)} +  \rotfv{\varphi(g^{-1})\varphi(v)}{\varphi(J \cup g) }  \\ 
    & = \sum_{g\in S/\varphi(J)} \rotfv{\varphi(v)}{ \varphi(J)\cup g} +  \rotfv{g^{-1}\varphi(v)}{\varphi(J)\cup g }  \\ 
      &= \partial^{+} \rotfv{\varphi(v)}{\varphi(J)}
  \end{split}
\end{equation*}
\end{proof}
\begin{definition}[The Nice Encoding]
  Consider $(d,d/2)$-Toric code and fix a subset $S^{\prime} \subset S$, at size $d^{\prime}$. We define the \textit{nice encoding} to be the subsystem code, which encodes a single logical qubit as follow: 
  \begin{equation*}
    \begin{split}
      \ket{ \bar{0} } &= \ket{ \mathcal{C}_{Z}^{\perp} } \\ 
      \ket{ \bar{1} } &= \ket{ x_{S^{\prime}} + x_{S/S^{\prime}} + \mathcal{C}_{Z}^{\perp} } 
    \end{split}
  \end{equation*}
\end{definition}
\begin{claim}
  Given a resource state, the nice encoding has a fold-transversal realization of the logical $\mathbf{S}$ gate. 
\end{claim}
\begin{proof}
 Consider the resource state defined by:  
 \begin{equation*}
   \begin{split}
     \ket{\mathbf{S}} = \frac{1}{\sqrt{2}}\left(\ket{ \bar{0} } + i \ket{ \bar{0} + x_{S^{\prime}}}\right)
   \end{split}
 \end{equation*}
    \begin{figure}[h]
        \centering 
        \begin{quantikz}
          \lstick{$\ket{\psi}$} & \ctrl{1}  & \gate{Z_{S^{\prime}\rightarrow S/S^{\prime}}} &  &&&&&&&&&&&&& \\
        \lstick{$\ket{\mathbf{S}}$} & \targ{} & \meter{} \wire[u][1]{c}    \\
        \end{quantikz}
        \caption{ Simulating the $\mathbf{S}$-gate, using the $\ket{\mathbf{S}}$ magic state. }   
\label{fig:magic}
\end{figure}


\begin{equation*}
  \begin{split}
    \ket{\psi}\ket{\mathbf{S}} &=   \left(\alpha \ket{\bar{0}} + \beta \ket{\bar{0} + x_{S^{\prime}} + x_{S/S^{\prime}}} \right)  \frac{1}{\sqrt{2}}\left(\ket{ \bar{0} } + i \ket{ \bar{0} + x_{S^{\prime}}}\right) \\ 
    & \mapsto  \frac{1}{\sqrt{2}} \big( \alpha \ket{\bar{0}} \ket{\bar{0}} + i\alpha  \ket{\bar{0}} \ket{\bar{0} + x_{S^{\prime}}} \\
    & \ \ \  + \beta \ket{\bar{0} + x_{S^{\prime}} + x_{S/S^{\prime}}} \ket{\bar{0}+ x_{S^{\prime}} + x_{S/S^{\prime}}} + i\beta \ket{\bar{0} + x_{S^{\prime}} + x_{S/S^{\prime}}} \ket{ \bar{0} + x_{S/S^{\prime}}} \big)   
  \end{split}
\end{equation*}

\end{proof}


\section{Toric Encoded Circuits}

    \begin{definition}[Troic Encoded Circuit]
      Let $C$ be a quantum circuit. We say that $C$ is \textit{Toric encoded} if the following holds:
      \begin{enumerate}
          \item There is a Toric code $\mathcal{C}$ such that the qubits of $\mathcal{C}$ can be partitioned into registers $R_{1}, \ldots, R_{k}$, and each of the registers is encoded by $\mathcal{C}$.   
          \item The gates in $C$ with even time coordinates are sweep decoding gates.
        \end{enumerate} 
        For a set of faults $\mathcal{E}$ the gates in $C[\mathcal{E}]$ can be decomposed to cycles, of the following form:
        \begin{equation*}
          \begin{split}
            C =     D_{l}P_{l}\Lambda_{l},..,D_{1} P_{1} \Lambda_{1}
          \end{split}
        \end{equation*}
    \end{definition}

  \begin{definition}[Base graph $G_{o}$]
    Let $C$ be a quantum circuit, at depth $d$, with registers $R_{1}, \ldots, R_{k}$, all of which are encoded by Toric codes with the same parameters (i.e., dimension, length, etc.). Let's denote by $\mathcal{G}_{1}, .., \mathcal{G}_{k}$ the Toric complexes that induce the codes. We define the base graph of $C$, denoted by $G_{o} = (V_{o},E_{o})$ as follows: 
    \begin{enumerate}
      \item The vertices $V_{o}$ are tuples, where the first coordinates correspond to a vertex in the union over the vertices in $\mathcal{G}_{1}, \ldots, \mathcal{G}_{k}$, and the second coordinate is associated with a time. Namely:
        \begin{equation*}
          \begin{split}
            V_{o} \colonequals \bigsqcup_{i} V(\mathcal{G}_{i}) \times [d]
          \end{split}
        \end{equation*}
      \item The edges $E_{o}$ are derived from the original edges in $\mathcal{G}_{1}, \ldots, \mathcal{G}_{k}$, with the addition that any two vertices in preceding times $t$ and $t+1$ that support qubits (faces) such that $C$ acts non-trivially on those qubits at time $t$ are also connected by an edge. Namely:
        \begin{equation*}
          \begin{split}
            E_{o} & \colonequals \big\{ \{(v,t), (u,t^{\prime}) \} :  \text{ if }     \\ 
              & \text{either there exists } i \text{ such }  \{v,u\} \in \mathcal{G}_{i} \text{ and } t^{\prime} = t,t+1 \\
             & \text{or there exists } u_i = (g_{i},l_{i}) \in C \text{ such }  v,u \in l_{i,2} \text{ and } t = l_{i,1}, t^{\prime} = l_{i,1}+1  \big\} 
          \end{split}
        \end{equation*}
    \end{enumerate} 
\ctt{Here we should add that a vertex $v$ belongs to location $l$ if there is a qubit $f$ that $v$ belongs to its associated face. }

  \end{definition}




  \begin{definition}[Time Graph of $C(\mathcal{E})$]
    For a quantum circuit $C$ and set of faults $\mathcal{E}$, let us denote the base graph of $C[\mathcal{E}]$ by $G_{o}$. For each time $t$, denote the deviation induced by $\mathcal{E}$ at time $t$ by $\mathcal{D}_{t}$, so $\partial\mathcal{D}_{t}$ is the syndrome that the qubits in the deviation admit. We define the history graph $\mathcal{H} = ( V_{\mathcal{H}}, E_{\mathcal{H}})$ as follows: 
    \begin{enumerate}
      \item The vertices $V_{\mathcal{H}}$ are taken to be the vertices of $G_{o}$, namely tuples $(v,t) \in V_{o}$, that satisfy that $v$ belongs to a face associated with a check, which, at time $t$, belongs to the $\partial \mathcal{D}_{t}$. Namely:
        \begin{equation*}
          \begin{split}
            \big\{ v_{t} : v_{t}=(v,t) \in V_{o} \text{ and there exists a check } f \in C \text{ such } v \in f \in \partial \mathcal{D}_{t} \big\}
          \end{split}
        \end{equation*}
      \item The edges $E_{\mathcal{H}}$ is partitioned into two types $A_{\mathcal{H}}$ and $F_{\mathcal{H}}$, where $A_{\mathcal{H}}$ are the edges in $E_{o}$ restricted to $V_{\mathcal{H}}$ and $F_{\mathcal{H}}$ are defined to be the . Namely:
        \begin{equation*}
          \begin{split}
            A_{\mathcal{H}} &= \big\{ e = \{u,v\} \in E_{o} :  u,v \in V_{\mathcal{H}} \text{ and } \Time{v} = \Time{u}\pm 1 \big\} \\
            F_{\mathcal{H}} &= \big\{ e = \{u,v\} \in E_{o} : \text{ exists } w \in V_{\mathcal{H}} \text{ such } \{v,w\},\{u,w\} \in A_{\mathcal{H}} \big\} 
          \end{split}
        \end{equation*}
    \end{enumerate}
    By definition of the construction, $G_{\mathcal{H}}$ is a time-graph.
\end{definition}


\begin{definition}[$\Size{ }$-Function]
  Let $S$ be a subset of vertices, we define the \textit{size} of $S$ to be:
  \begin{equation*}
    \begin{split}
      \Size{S} \colonequals \sum_{i}^{d+1} \max_{v \in S} L_{i}(v) 
    \end{split}
  \end{equation*}
\end{definition}


  \begin{claim}
    Let $\mathbf{S} = \{ S_{1}, S_{2} , .. , S_{k} \}$ where $S_{i} \subset \mathbb{R}^{d}$, introduce an edge between $S_{i}$ and $S_{j}$ iff $S_{i} \cap S_{j} \neq \emptyset$. Assume that $\mathbf{S}$ is connected. Then $\Size{\cup^{k}_{i=1} S_{i}} \le \sum^{k}_{i=1}{\Size{S_{i}}}$. 
  \end{claim}
  \begin{proof}
    It suffices to prove that if $R_{1} \cap R_{2} \neq \emptyset$, then $\Size{R_{1} \cup R_{2}} \le \Size{R_{1}} + \Size{R_{2}}$. Let $a_{i,j} = \max_{v \in R_{j}}L_{i}(v)$. Then for any $w \in R_{1}\cap R_{2}$ we have:  
    \begin{equation*}
      \begin{split}
        \Size{R_{1} \cup R_{2}} &= \sum_{i}^{d+1}{\max{ a_{i,1},a_{i,2} } } =  \sum_{i}^{d+1}{a_{i,1} + a_{i,2} - \min{ a_{i,1},a_{i,2} } } \\
        & \le   \sum_{i}^{d+1}{a_{i,1} + a_{i,2} - L_{i}(w) } = \Size{R_{1}} + \Size{R_{2}} - \Size{w}  \\
        &  = \Size{R_{1}} + \Size{R_{2}} 
      \end{split}
    \end{equation*}
  \end{proof}

  \begin{definition}[Size Invariant Action]
\ctt{Here we classify both transversal gates, and rotation on the Toric. }
An action $g$ is be said size invariant action if, for any assignment $z$, it holds that $\Size{gz} = \Size{z}$. 
  \end{definition}

  \begin{claim}
    The sweep rule is Size $\xi$-shrinking.
  \end{claim}
  \begin{proof}
    
  \end{proof}

  \ctt{Eventually, we might not used the projected graph, and then we will split to history of the slices lemma for 3 parts. The first is when time $=3t$, in that we apply an invariant action so. }

