 \section{Explantation of a Spanned Slice}

  \ctt{Here we follow the original proof, but change the triminalogy, $m$ will be the number of leaves in the explanation, then in the end we conclude that the number of faults is at least $m/\Delta$. So $|R| \le f(\frac{m}{\Delta})$. }

  \begin{definition}
    Consider a time graph $(G,T)$, an embedding $f \colon G \rightarrow \mathbb{R}^{d}$, such that.. Let $\beta = \frac{d+1}{\xi}$ and $\alpha = \beta \Size{\text{fork}}$. Given sets $W$ of points, $R$ of arrows and $F$ of forks, we define $U$ as the set of vertices of the graph induced by the edges of $R \cup F$. The sets $W,R$ and $F$ form an explanation of a spanned slice $\hat{K} = \expval*{ K, v_{1}, .., v_{d+1}}$ if and only if: 
    \begin{enumerate}
      \item $W \cup \{v_{1} ,.., v_{d+1}\} \subset U \subset \History{K}$ and the graph $(U, R\cup F)$ is connected. 
      \item All elements of $W$ are leaves. 
      \item For $m = |W|$ and $s=\Size{K}$ we have $|R| \le \alpha (m-1) - s $ and $|F| < m -1 $. 
    \end{enumerate}
  \end{definition}

  \begin{claim}
    \label{claim:edgesin}
    Every spanned slice $K = \expval*{K,v_{1},..,v_{d+1}}$ has an explanation.
  \end{claim}

  \begin{proof}
    Let $h = \Time{K} - \min_{u \in \History{K}}\Time{u}$. The proof is by induction on $h$. 
    \begin{enumerate}
      \item Base: $h=0$, namely $T$ is constant on $\History{K}$, so no arrows connect points of $\History{K}$. Thus, $\History{K}$, as well as $\mathbf{K}$, consists only of leaves. In that case, $U = W = \{u\}$, $m=1$, $s=0$, and $|R|, |F| = 0$ satisfy the requirement.
      \item Induction Step: $h \neq 0$ implies $K \neq \History{K}$. Thus, by \cref{claim:prevslices}, we know that for some $k$ there exist spanned slices $\hat{K}_{0}, .., \hat{K}_{k}$ and forks $F_{1},..,F_{k}$ that satisfy \cref{claim:prevslices}. 

        Consider $i \in 0,..,k$, denote by $s_{i} = \Size{\hat{K}_{i}}$. By the inductive hypothesis and since $\Time{K_{i}} = \Time{K} - 1$, we know that $\hat{K}_{i}$ has an explanation formed by a set of leaves $\mathbf{W}_{i}$, a set of arrows $\mathbf{R}_{i}$ and a set of forks $\mathbf{F}_{i}$. Let $m_{i} =|\mathbf{W}_{i}|$, So the sets $R_{i}$ and $F_{i}$ have at most $\alpha m_{i} - s_{i}$ and $m_{i}-1$ leaves. We define:
        \begin{enumerate}
          \item $\mathbf{W} = \cup_{i=0}^{k} \mathbf{W}_{i}$, Notice that $\mathbf{W}_{i} \subset K_{i}$ and that $\Time{K_{i}} = \Time{K_{j}}$ for all $i,j$, thus by \Cref{claim:disj} $\mathbf{W}$ is a union of disjoint set, Hence $W$ contains  $m = \sum_{i=0}^{k}m_{i}$ leaves. 
          \item $\mathbf{F} = \{ F_{1},..,F_{k} \} \cup_{i = 0}^{k}\mathbf{F}_{i}$ with at most $ k + \sum_{i=0}^{k}{m_{i} -1 } = m- 1$ elements. 
          \item $\mathbf{R} = \{ \{v_{i}, \prei{v_{i}} \} \} \cup_{i=0}^{k}{ \mathbf{R}_{i} }$ with at most 
            \begin{equation*}
              \begin{split}
                & d+1 + \sum^{k}_{i=0}{\alpha (m_{i}-1)  - \beta s_{i} } \\ 
                \le & d+1 + \alpha m - \alpha(k+1) - \beta\left(s + \xi - k \cdot \Size{\text{fork}}  \right) \\
                = & \alpha \left(m - 1\right) - \beta s + \left(\alpha + d+1 - (k+1) \alpha - \beta \xi + \beta k \cdot \Size{\text{fork}} \right)
              \end{split}
            \end{equation*}
            So its enough to show that for $k\ge 0$ the term in the closure is negative, We do that by showing that the slop is negative, and then the value of the term at zero is negative: 
            \begin{equation*}
              \begin{split}
                  - \alpha  +  \beta \Size{\text{fork}} \le 0 & \Rightarrow   \Size{\text{fork}} \le \frac{\alpha}{\beta} \\ 
                 d + 1  -\beta \xi \le 0 & \Rightarrow \frac{d+1}{\beta} \le \xi
              \end{split}
            \end{equation*}
        \end{enumerate}
        And those inequalities hold for $\beta = \frac{d+1}{\xi}$ and $\alpha = \beta \Size{\text{fork}}$. Finally, by \cref{claim:prevslices}, the graphs induced by $\mathbf{R}_{i} \cup \mathbf{F}_{i}$ are connected, thus the graph induced by $\mathbf{R}\cup \mathbf{F}$ is also connected. Therefore, $\mathbf{W}, \mathbf{R}, \mathbf{F}$ form an explanation of $K$. 
    \end{enumerate}

  \end{proof}

\ctt{ 
  Consider the proof above, when we run two sequences steps, the first is not shrinking, namely $\xi = 0$, and the second is shrinking $\xi \neq 0$. Each of the proceeding slices $K_{0}, .., K_{k}$ has its own $k_i$ proceeding slices $K_{i}^{0}, .., K_{i}^{k_{i}}$. We count the number of arrows in $K$ by adding the arrows resulting in those two steps $d+1 + (k+1)\cdot(d+1)$ to the arrows in each of the explanation of the $K_{i}^{j}$ slices. So: 
            \begin{equation*}
              \begin{split}
                &  (k+2)(d+1) + \sum_{i,j=0}{\alpha (m_{i}^{j}-1)  - \beta s^{j}_{i} } \\ 
                \le & (k+2)(d+1) + \alpha m - \alpha\sum_{i=0}^{k}k_{i} - \beta\left(s + \xi - \left(k + \sum_{i=0}^{k}k_{i} - 1\right) \cdot \Size{\text{fork}}  \right) \\
                \le & \alpha \left(m - 1\right) - \beta s + \left(\alpha + (k+2)(d+1) - \alpha\sum_{i=0}^{k}k_{i} - \beta \xi + \beta\left( \sum_{i=0}^{k}k_{i} \cdot \Size{\text{fork}} \right) \right)
              \end{split}
            \end{equation*}
            Now, we want to show that the left term, the linear line, is always negative. For this we look for parameters such when $k=0, \sum k_i =0 $ it results with negative value and that the 'slope' of it is negative. For showing negative slope, we use the fact that $\sum_{i}k_{i} \ge k$.
            \begin{equation*}
              \begin{split}
                k = 0 & \Rightarrow \alpha  - \beta \xi \le 0 \Rightarrow   \xi \ge \frac{\alpha}{\beta} \\ 
                &  \alpha + (k+2)(d+1) - \beta \xi  - k \left( \alpha -  \beta\cdot \Size{\text{fork}} \right)  \\ 
                & \Rightarrow d+1 - \left( \alpha -  \beta\cdot \Size{\text{fork}} \right) \le 0 \\
                & \Rightarrow \alpha \ge \beta \Size{\text{fork}} + d+1
              \end{split}
            \end{equation*}
            That is not satisfying the inequalities, one way to try to bypass it is treating to $O(d)$ SWEEP RUlE operations as a constant depth operation, then $\xi = O(d)$. For that we need the follow property, for every subset of qubits $S$, there is subset of qubits $S^{\prime}$ at size at least $(1-\gamma)|S|$ such that for $S$ to be deviated, all the qubits in $S^{\prime}$ have to absorb fault. Now suppose that the gate is at depth at most $\Delta$, and the fanning is at most $c_{f}$, then we get: 
            \begin{equation*}
              \begin{split}
                & \prb{ S \in \mathcal{D}} \le (c_{f}^{\Delta} p)^{|S^{\prime}|} \le (c_{f}^{\Delta} p)^{(1-\gamma)|S|} \\
                \Rightarrow & p \rightarrow (c_{f}^{\Delta} p)^{1-\gamma} 
              \end{split}
            \end{equation*}
            A trivial lower bound for $1 - \gamma$ is $ \frac{1}{c_{f}^{\Delta}}$.
            \begin{equation*}
              \begin{split}
                & d+1 + \sum^{k}_{i=0}{\alpha (m_{i}-\mathcal{X}_{r-1})  - \beta s_{i} } \\ 
                \le & d+1 + \alpha m - \mathcal{X}_{r-1}\alpha(k+1) - \beta\left(s + \xi - k \cdot \Size{\text{fork}}  \right) \\
                = & \alpha \left(m - \mathcal{X}_{r}\right) - \beta s + \left( (\mathcal{X}_{r}-\mathcal{X}_{r-1}) \alpha + d+1 - \mathcal{X}_{r-1}k \alpha - \beta \xi + \beta k \cdot \Size{\text{fork}} \right)
              \end{split}
            \end{equation*}
            \begin{equation*}
              \begin{split}
                - \alpha \mathcal{X}_{r-1}  +  \beta \Size{\text{fork}} \le 0 & \Rightarrow   \Size{\text{fork}} \le \frac{\alpha}{\beta} \mathcal{X}_{r-1} \\ 
                (\mathcal{X}_{r}-\mathcal{X}_{r-1}) \alpha  + d + 1  \le 0 & \Rightarrow \mathcal{X}_{r} \le  \mathcal{X}_{r-1} - \frac{d+1}{\alpha}  \\
& \Rightarrow \frac{(\mathcal{X}_{r}-\mathcal{X}_{r-1}) \alpha  + d+1}{\beta} \le \xi \\
                 (\mathcal{X}_{r}-\mathcal{X}_{r-1}) \alpha  + d + 1  -\beta \xi \le 0 & \Rightarrow \frac{(\mathcal{X}_{r}-\mathcal{X}_{r-1}) \alpha  + d+1}{\beta} \le \xi \\
              \end{split}
            \end{equation*}
}


