

%\newcommand*{\ACM}{}%

\ifdefined\ACM

%\documentclass[sigplan,screen]{acmart}
  \documentclass[manuscript,screen,review]{acmart}

\else
  \documentclass{article}
  \input{./usepackage}
  \addbibresource{./sample.bib} 

\fi

\begin{document}

\input{newcommands}

\title{Generate States.} 
\author{David Ponarovsky}
%\author{Noa Viner, David Ponarovsky}

\ifdefined\ACM
  \affiliation{%
    \institution{The Th{\o}rv{\"a}ld Group}
    \streetaddress{1 Th{\o}rv{\"a}ld Circle}
    \city{Hekla}
  \country{Iceland}}
  \email{larst@affiliation.org}
\else
  \maketitle
\fi
%\input{abstract}
\ifdefined\ACM
  \maketitle
\fi

%\begin{multicols*}{2}
% \input{preamble}



\begin{problem} Given amplitudes $\{ a_{i} \}_{0}^{2^{n}}$ Show that there is a Quantum cuircuit that generate $\ket{\psi} = \sum_{i}{a_{i}\ket{i}}$.
\end{problem}

We will show a construction of the controlled gate. 

\section{Equivalence to Fusion-controlled gates problem.}
\subsection{Stage (1) - Fusion-controlled circuit.}

To build the required circuit, we will start by defining the fusion-controlled gate as the circuit $(U\otimes V)^{c}$, where $U$ and $V$ are two specific circuits, and $U^{c}$ and $V^{c}$ are their controlled versions. The fusion-controlled gate operates on three quantum registers - a work register of size $\Delta$ which contains the control qubit, and two input registers $U$ and $V$.

\begin{equation*}
  (U\otimes V)^{c} :\ket{0}^{\Delta}\otimes \ket{0}^{U}\otimes \ket{0}^{V}   \rightarrow 
  \begin{cases}
  \ket{0} \ket{0}^{\Delta -1} U\ket{0}^{U} \ket{0}^{V} & \Delta_{0} = 0\\
  \ket{1} \ket{0}^{\Delta -1} \ket{0}^{U} V\ket{0}^{V} & else
\end{cases} 
\end{equation*}
Assume that $S(n-1)$ and $d(n-1)$ are the maximum possible widths and depths of a circuit that generates a state in a space of dimension $n-1$. We refer to the resources required to build the fusion-controlled gate, defined by two states in dimension $n-1$, as $T_{S}[S(n-1)]$ and $T_{d}[d(n-1)]$, respectively.

%We first show that given $U^{c},V^{c}$ one can implement at the same depth cost the circuit $(U\otimes V)^{c}$

\subsection{stage (2) - Induction.}

We will now show how one can use the fusion-controlled circuit to generate an arbitrary control gate for resolving $\ket{\psi}$. 

Recall that any state in a $n$-dimisional space could be write as $\psi = \alpha_{0} \ket{0}\ket{ \psi_{0}} + \alpha_{1} \ket{1}\ket{ \psi_{1}} $. By the assumption there are $U_{\psi_{0}}^{(n-1)},U_{\psi_{1}}^{(n-1)}$ circuits each at depth at most $\log n$ generate $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ corespondly. We are going to construct a circuit that computes $\psi$ by the following: 
\begin{enumerate}
  \item Prepare $2 \times S_{n-1} + 1$ anciles. And arrange them by $S_{n-1} \ |0| \ S_{n-1}$. 
  \item Rotate the middle qubit as follow: $ 0 \mapsto \alpha_{0} 0 + \alpha_{1} 1 $.   
  \item Apply $\left(U_{\psi_{0}}^{(n-1)} \otimes U_{\psi_{1}}^{(n-1)}\right)^{c} $ to have 
    \begin{equation*}
      \alpha_{0} 0 0^{\Delta -1} U_{\psi_{0}}^{(n-1)} 0^{(n-1)} 0^{(n-1)} + \alpha_{1} 1 0^{(\Delta - 1)}0^{(n-1)}U_{\psi_{1}}^{(n-1)}0^{(n-1)}
    \end{equation*}
  \item Now apply control swap, use the $\Delta$th qubit as the control wire and swap between $S_{0}$,$S_{1}$. That yields the state: 
    \begin{equation*} 0^{\Delta -1} \left(\alpha_{0} 0 U_{\psi_{0}}^{(n-1)} 0^{(n-1)} + \alpha_{1} 1 U_{\psi_{1}}^{(n-1)}0^{(n-1)} \right)0^{(n-1)} 
    \end{equation*}
\item By induction, the above state expanse to $\psi \otimes 0^{*}$.
\end{enumerate}
So if we denote by $d(n), S(n)$ the depth and the space needed to compute a general state correspond to a given amplitude, It follows by the recursion that: 

\begin{equation*}
\begin{split} 
S(n) &= T_{S}[S(n-1)]    \\
d(n) &= T_{d}[d(n-1)] + \overbrace{1}^{ \text{rotation} } + \overbrace{n-1}^{\text{swap}} =  T_{d}[d(n-1)] + n  
\end{split} 
\end{equation*}



\section{First Soultion $\times 4$ Space.}
\begin{enumerate}
  \item Prapere $+2$ qubits.
  \item Apply $CX$ from the first qubit to the second.
  \item Apply $U^{c}$ negative-controlled by the first qubit over the first $S_{u}$ qubits, and in parallel apply $V^{c}$ controlled by the second qubit over the $S_{v}$ quibtis.   
  \item Apply $CX$ from the first qubit to the second. (reverse step 2).
\end{enumerate}
Clearly $T_{S}[S(n)] = 2 \cdot S(n) + 2$ and $T_{d}[d(n)] = 1 + d(n) + 1$ And that sumup to:

\begin{equation*}
\begin{split}
  S(n) &  = T_{S}[S(n-1)] = 2T_{S}[S(n-2)] + 2   \\
  & = 2\cdot 2^{n - 1}...+2\cdot 2^{2} +2\cdot 2 + 2  \\
  & = 2\cdot 2^{n}  \\ 
  & d(n) = T_{d}[d(n-1)] + \overbrace{1}^{ \text{rotation} } + \overbrace{n-1}^{\text{swap}} =  T_{d}[d(n-1)] + n 
\end{split} 
\end{equation*}

\section{Second Solution $\times 2$ Space. }

\subsection{Stage (1) - Fusion-controlled circuit.}

For a circuit, $U$ denotes by $U^{c}$, the controlled version of it. We first show that given $U^{c},V^{c}$ one can implement at the same depth cost the circuit $(U\otimes V)^{c}$. It's well known that $U^{c}$ could be obtained by $U$ by adding single qubits gates on $U$ wires and connecting Cnot gates from the control wire to $U$ wires. Notice that for running $(V\otimes U)^{c}$ it's sufficient to handle the Conts as each of the single qubits gates operate independently in parallel. Consider the following recipe: 

On the $i$th iteration of the circuits,
\begin{enumerate}  
  \item If there is no conflict between $U^{c}$ and $V^{c}$, meaning that either only one of them uses the control wire at that step or that neither of them, then $(U \otimes V)^{c}_{t} \leftarrow U^{c}_{t} \otimes V^{c}_{t}$
  \item Else, at the $i$ step the controlled wire flow for both of them, So denote by $ x_{c},x_{v},x_{u}$ the tree bits such at time $t$   

\end{enumerate}
  
 

\section{Third Solution T.C.S Approach.}  

\printbibliography
\end{document}





