%\section{Hadamard and S Gates}


\begin{claim}
For any generator subset $S^{\prime}$ of size $d^{\prime}$, denote by $x_{S^{\prime}}$ and $z_{S^{\prime}}$ the following assignments:
\begin{equation*}
  \begin{split}
    x_{S^{\prime}}  \colonequals \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S^{\prime}} \ \ \ z_{S^{\prime}} \colonequals \sum_{u \in \expval*{S/S^{\prime}} }\rotfv{u}{S^{\prime}} 
  \end{split}
\end{equation*}
Then $x_{S^{\prime}}$ and $z_{S^{\prime}}$ are binary representations of anticommuting logical codewords of the $(d,d^{\prime})$-Toric code. In particular, $x_{S^{\prime}} \in \mathcal{C}_{X}/\mathcal{C}_{Z}^{\perp}$, $z_{S^{\prime}} \in \mathcal{C}_{Z}/\mathcal{C}_{X}^{\perp}$, and $x_{S^{\prime}} z_{S^{\prime}} = 1$. In addition, let $X_{S^{\prime}}$ and $Z_{S^{\prime}}$ be the Pauli matrices obtained by multiplying each non-trivial coordinate of them by $X$ or $Z$, respectively.
\end{claim}
\begin{proof}
  By definition $x_{S^{\prime}}$ and $z_{S^{\prime}}$ are binary assignments on the $d^{\prime}$-dimensional faces. We start by showing that $x_{S^{\prime}} \in \mathcal{C}_{X}$ and $z_{S^{\prime}}\in \mathcal{C}_{Z}$: 
\begin{equation*}
  \begin{split}
    \partial^{-} \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S^{\prime}} &=  \sum_{u \in \expval*{S^{\prime}} } \sum_{g\in S^{\prime}} \rotfv{ u}{S^{\prime}/g} +  \rotfv{gu}{S^{\prime}/g} \\
     &=  \sum_{g\in S^{\prime}} \sum_{u \in \expval*{S^{\prime}} } \rotfv{ u}{S^{\prime}/g} +  \sum_{u \in \expval*{S^{\prime}} }\rotfv{gu}{S^{\prime}/g} \\
     &=  \sum_{g\in S^{\prime}} \sum_{u \in \expval*{S^{\prime}} } \rotfv{ u}{S^{\prime}/g} +  \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S^{\prime}/g} = 0 
  \end{split}
\end{equation*}
\begin{equation*}
  \begin{split}
    \partial^{+} \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S/S^{\prime}} &=  \sum_{u \in \expval*{S^{\prime}} } \sum_{g\in S^{\prime}} \rotfv{ u}{S/S^{\prime} \cup g} +  \rotfv{g^{-1} u}{S/S^{\prime} \cup g} \\
    &=  \sum_{g\in S^{\prime}} \sum_{u \in \expval*{S^{\prime}} } \rotfv{ u}{S/S^{\prime} \cup g} +  \sum_{u \in \expval*{S^{\prime}} }\rotfv{g^{-1}u}{S/S^{\prime}\cup g} \\
     &=  \sum_{g\in S^{\prime}} \sum_{u \in \expval*{S^{\prime}} } \rotfv{ u}{S/S^{\prime}\cup g} +  \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S/S^{\prime} \cup g} = 0 
  \end{split}
\end{equation*}
Thus $x_{S^{\prime}} \in \mathcal{C}_{X}$ and $z_{S^{\prime}}\in \mathcal{C}_{Z}$, now for showing that they are not binary representations of stabiliers, it's enough to show they admit no vanishing product.  
\begin{equation*}
  \begin{split}
    x_{S^{\prime}}z_{S^{\prime}} = \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S^{\prime}} \sum_{u \in \expval*{S/S^{\prime}} }\rotfv{u}{S^{\prime}} = \rotfv{e}{S^{\prime}} \rotfv{e}{S^{\prime}} = 1
  \end{split}
\end{equation*}
\end{proof}
\begin{definition}[The Transpose Map]
Let $d, d^{\prime}$ be integers, and let $\mathcal{G}$ be a $(d, d^{\prime})$-Toric complex generated by the generator set $S$. We define the \textit{transpose map} $\phi : \mathcal{F}^{d^{\prime}} \rightarrow \mathcal{F}^{d - d^{\prime}}$ by acting on the basis elements as follows:
  \begin{equation*}
    \begin{split}
    \phi(\rotfv{v}{S^{\prime}}) \rightarrow \rotfv{v^{-1}}{S/S^{\prime}} 
    \end{split}
  \end{equation*}
Notice that for $d^{\prime} = d - d^{\prime}$, the transpose map is a permutation over the bits.
\end{definition}

\begin{definition}[ Hadamard-Type Gate $H_{\phi}$]  
For $ d' = d - d' $, we define the logical Hadamard-type gate $ H_{\phi} \colon L \rightarrow L $ as follows, for any $ S' \subset S $, of size $ d' $:
  \begin{equation*}
    \begin{split}
      H_{\phi} ( X_{S^{\prime}} )  & \rightarrow Z_{S/S^{\prime}} \\
      H_{\phi} ( Z_{S^{\prime}} )  & \rightarrow X_{S/S^{\prime}} 
    \end{split}
  \end{equation*}
\end{definition}

\ctt{Change the definition above such that it will be about moving to the dual code $C_{X}/C_{Z}^{\perp} \rightarrow C_{Z}/C_{X}^{\perp}$. And not about the logical Hadamard. }



\begin{claim}
The Hadamard-type gate $ H_{\phi} $ has a fold-transversal implementation by, first applying $H^{n}$ over all the physical qubits, and then permuting them by the transpose map $\phi$, namely $\hat{H}_{\phi} = \phi \circ H^{n}$.
\end{claim}
\begin{proof}
  Clearly, for any subset of generators $S^{\prime} \subset S$, the map $\phi$ sends $x_{S^{\prime}}$ to $z_{S/S^{\prime}}$:
  \begin{equation*}
    \begin{split}
      \phi(x_{S^{\prime}}) = \phi(  \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S^{\prime}}   ) =  \sum_{u \in \expval*{S^{\prime}} }\rotfv{u}{S/S^{\prime}} = z_{S/S^{\prime}}
    \end{split}
  \end{equation*}
Moreover, $\phi$ sends binary representations of $Z$-stabilizers to binary representations of $X$-stabilizers, and vice versa. To see this, consider a $d^{\prime}+1$ dimensional face, and consider the image of the stabilizer it defines.
  \begin{equation*}
    \begin{split}
      \phi \left( \partial^{-}  \rotfv{v}{S^{\prime}} \right) &=  \phi\left( \sum_{g\in S^{\prime}} \rotfv{v}{S^{\prime}/g} +  \rotfv{gv}{S^{\prime}/g}  \right) \\
      & = \sum_{g\in S^{\prime}} \rotfv{v^{-1}}{(S/S^{\prime})\cup g} +  \rotfv{g^{-1}v^{-1}}{(S/S^{\prime})\cup g}  \\ 
      &= \partial^{+} \rotfv{v^{-1}}{S/S^{\prime}}
    \end{split}
  \end{equation*}
And since $\phi \circ \phi = I$, we also have that $\phi\left( \partial^{+} \rotfv{v^{-1}}{S/S^{\prime}} \right)$. Thus, $H^{\otimes n} \circ \phi$ sends $Z$-stabilizers to $X$-stabilizers and vice versa, thereby preserving the code space. Combining this with the above, $H^{\otimes n} \circ \phi$ realizes the logical form $H_{\phi}$ in the $(d,d/2)$-Toric code.
\end{proof}


\begin{definition}[The Nice Encoding]
  Consider $(d,d/2)$-Toric code and fix a subset $S^{\prime} \subset S$, at size $d^{\prime}$. We define the \textit{nice encoding} to be the subsystem code, which uses $x_{S^{\prime}}$ to encode a single logical qubit. Namely, the logical codewords are: 
  \begin{equation*}
    \begin{split}
      \ket{ \bar{0} } &= \ket{ \mathcal{C}_{Z}^{\perp} } \\ 
      \ket{ \bar{1} } &= \ket{ x_{S^{\prime}} + \mathcal{C}_{Z}^{\perp} } 
    \end{split}
  \end{equation*}
\end{definition}





